### 2015-08-05 presentations/paper/paper.tex
Add paper stuff from svn

% TODO
% - provide general advice on how to define the research problem
% - ... on how to do practical parts

\documentclass{llncs}

\usepackage{hyperref}
\usepackage{url}
\usepackage{comment}

\pagenumbering{arabic}

\begin{document}

\title{Annotated metamodel for MSR course papers}

\subtitle{Version as of 30 June 2015}

\author{Ralf L\"ammel}

\institute{Software Languages Team, CS Faculty, University of Koblenz-Landau}

\maketitle

\begin{abstract}
  This should be 100-200 words. Use present or past tense, but use it
  consistently. Prefer ``we'' over ``I'' here and throughout the
  paper. The abstract should summarize the methodology and results;
  see the corresponding sections below. Your paper is preferably
  typeset with LaTeX and it should comply with the Springer LNCS
  style. (That style is also available for word users.) 
\end{abstract}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Address these questions:

\begin{itemize}

\item What is the context of this research?

\item What is the overall challenge addressed by this research?

\item What is the overall approach adopted by the research?

\item Summarize results very briefly.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research question}

State 1-5 research questions. One question could be enough. More is
not better.

For each question, make clear why this is an interesting question. For
example, try to make clear why a scientist or a practician would
benefit from knowing the answer to the question.

Lay out some background for your research questions. That is, what
body of related work may be worth mentioning and comparing to the
research at hand. This may be related in terms of both relevant
methodology or similar research questions.

You should make sure to carry out a proper related work study. Use
DBLP on the MSR conference for 2+
years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
welcome to search other conferences and journals. Coming to the
conclusion that there is no related work is absolutely
unacceptable. Again, you need to show related work awareness so that
your research question is substantiated as being relevant and
your methodology is deeply informed by existing publications.

In many cases, you want to refine your research questions into actual
hypotheses, i.e., something that is potentially falsifiable, subject
to an appropriate approach towards measuring.

It is also common to refine research questions. That is, one starts
with a general (overall) research question and takes it appart into
several questions that are concrete enough to be researched on and to
be answered. In this manner, you may often suffice with one or two
research questions which are however refined into perhaps
several questions. Again, even without refinement, just one question may be
Ok. This depends on the nature of the project and on the kind of question.

Here are some recommended MSR papers by the Software Languages
Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
consult to see instances of the concepts discussed in this
metamodel. These papers may or may not be in an optimal form to
function as good advice. You are also advised to have a look at some
MSR papers (from the MSR conference), but again, they may also
slightly vary in terms of consistency of style. if you like to get
general advice on scientific writing, then I recommend relevant
textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
writing and by having someone with experience to provide feedback.

You should most definitely have a look at this excellent tutorial on
empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
relates. General ESE is quite often concerned with controlled
experiments and other research methods that involve subjects, whereas
MSR is more concerned with automated analysis, but the text is still
very helpful in coming to grips with research methods in software
engineering overall. Specifically, it helps with formulating research questions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Methodology}

The methodology section must give a very clear account of what sort of
procedure was executed. Here are some detailed criteria:
%
\begin{itemize}
\item The section is preferably a step-by-step procedure overall. First we did
  this. Then we did this.
\item Steps should be motivated or defended, whenever it is not
  obvious why a certain choice was made. However, one should be
  careful not to preempt the discussion of threats to validity; see
  the extra section below.
\item The text should support reproducibility. In particular, a
  reasonably knowledgeable person should be able to re-execute the
  methodology and compare the results.
\item The text should not get into low-level (implementation)
  details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
\end{itemize}

\subsection{Data extraction}

This metamodel is concerned with MSR papers. Thus, the methodology
section would be reasonably subdivided into the three major phases of
an MSR research project.

The subsection on data extraction is concerned with issues like the
following:

\begin{itemize}
\item What repository was chosen and why?
\item What sort of extraction techniques is applied?
\item What sort of extra processing (e.g., filtering) is applied?
\item What constraints were chosen to help with scalability?
\end{itemize}

\subsection{Data synthesis}

Even the simplest MSR project carries out synthesis; data analysis (see
below) may not be carried out in all the cases. The subsection on data
synthesis is concerned with issues like the following:

\begin{itemize}

\item What metrics are used?

\item What machine learning techniques are used?

\item What information retrieval techniques are used?

\end{itemize}

The typical MSR paper picks either metrics or machine learning or IR.

\subsection{Data analysis}

Data analysis would be concerned with any sort of statistical quality
analysis of the data. More specifically, the subsection on data
analysis is concerned with issues like the following:

\begin{itemize}

\item Simple statistics like median of metrics.

\item Analysis of regression or correlation or distribution.

\item Analysis of accuracy such as precision and recall.

\end{itemize}

It should be noted that the methodology section describes the `how'
(and to some extent the`why'), but it does not yet report the various
results; see the following section. For instance, the methodology may
explain why it is using a certain metric and define it and announce
that the median for the metric is going to be determined, as it would
provide a certain insight, but the actual tables or charts for the
metric and the interpretation of the findings would be deferred to the
results section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Results}

\noindent
Summarize results in terms of tables, charts, and other kinds of
figures.

Explain and interpret the results.

Get back to the research question and make sure that it is explicitly answered.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Threats to validity}

There are external and internal threats to validity. See the softlang
papers and MSR papers for examples. See this resource~\cite{Michael04}
for an explanation. Be concise and systematic about answering
questions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

This is essentially a redundant section. Try to summarize your
research from a more informed point of view. (We assume that the
reader has read the paper and is ready for some deeper conclusion.)
You could very well add some perspectives for future work, without
repeating smaller scale weakness of research, as they were already
identified in the threats to validity section.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\appendix

\section{Details}
\label{S:details}

Any sort of interesting details such as source code, extra data (extra
to the key results), extra procedural details supporting
reproducibility can be listed here.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{paper}
\bibliographystyle{abbrv}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

Generally, this seminar (series) is about ``software languages'' (SL)
and hence it combines elements of software engineering, modelling,
programming languages, linguistics, formal specification, and
programming theory; see a recent discussion of some relevant fields
and terminology~\cite{FavreGLP10}.

Each particular edition of the SL seminar focuses on a specific topic
within the broader area of SL. (For instance, an edition may focus on
programming-language usage \cite{HageK08} or natural language aspects
in programming \cite{HostO08}.) The present notes provide some general
advice on the reporting and presentation obligations of the seminar's
participants. These notes are meant to be generic with regard to the
particular theme of a specific seminar edition.

That is, the purpose of these notes is to help student participants
writing their reports and preparing their presentations. These notes
complement the meetings and consultations.

\subsection*{Road-map}

In \S\ref{S:report}, advice on the report part of the seminar is
provided.

\noindent
In \S\ref{S:presentation}, advice on the presentation part
is provided.

\noindent
These notes are summarized in \S\ref{S:concl}.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Advice on the report}
\label{S:report}

Much has been written and said about scientific writing.  A report for
this seminar is a small exercise in scientific writing. Hence,
seminar participants are \emph{strongly encouraged} to gain basic
understanding of scientific writing. For instance, seminar
participants may consult a resource such as
\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
does not plan for education on scientific writing, neither does any
other obligatory course. Hence, seminar participants are bound to
consult a designated book or online resource, and to work closely
together with the prof to get a reasonable result.\footnote{Here is
  another resource on writing and giving talks:
  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
The following notes try to get seminar participants off the ground.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Organization of the report}

As far as reports for the seminar are concerned, we assume a rather
simple organization. A report would be spending about 10-25 pages in
Springer's LNCS style to describe the research work carried out.

Reports should use close 10 pages if there are not any substantial
illustrations. Reports can use up to 25 pages, but \textbf{a higher
  page count does not imply a better grade}---potentially it may
negatively affect the grade. However, illustrations are strongly
encouraged, if they truly illustrate the subject at hand. So seminar
participants are welcome to exhaust a 25 pages limit with useful
illustrations included.

A report would have a title and an abstract. The purpose of an
abstract is to properly summarize the report: use 50-200 words,
typically 100-150 words.

A report consists of an introduction, several technical sections,
possibly a related work section, and a conclusion section. See below
for more details.

\subsection{The importance of the introduction}

A report should start with an \emph{introduction section} which
motivates the subject of the report, possibly states one or more
\emph{research questions}, typically provides some background material
(if such material is not placed in a subsequent, designated section or
an appendix), lists \emph{contributions} of the report, and describes
the organization of the rest of the report. Judgement of all submitted
work may be biased by the introduction.

If there is any ingredient that is critical to an excellent completion
of the seminar, then this is the formulation of a \emph{research
  question}. By default (for such a short report/paper that is meant
here), the research question should be identified in the introduction
section. The challenge is here to formulate a question that performs
well in all of the following dimensions: a) concise and clear; b)
informed and nontrivial; c) operationally intelligent and verifiable;
d) meaningful to the rest of the text.

\subsection{The technical sections}

After the introduction, there can be any number of \emph{technical
  sections}.  These sections constitute the core (``technical meat'')
of the report. The style of these technical sections very much depends
on the subject and the chosen sources as well as the assumed style of
presentation.

As there are many different styles, and we do not want to discuss them
here at length. The best advice may be to leverage the corpus of
consulted research papers and to try approximating the style of one of
them. The prof wants to help on this matter---during the consultations
and otherwise.

\subsection{The concluding section}

After the technical sections, the report should be concluded by a
final section. Typically, such a section contains bits of summary,
discussion, interpretations, open problems or future work, and
vision. This may be a good place for the student to show that he or
she has outgrown the view of one or two specific papers and can
usefully operate in a broader research context. Again, an excellent
student would make a serious effort to connect several research papers
and research directions in a comprehensible, informative, and
cross-indexing manner.

\subsection{Literature references}

One important element of scholarly writing is to make appropriate use
of citations. For instance, in the introduction section, one needs to
provide \emph{contextual citations} so that the overall context of the
research effort at hand is clarified. One may also quickly mention
some more technical sources as a means to prepare for the more
detailed parts of the report. Throughout the paper, one uses
\emph{technical citations} for two major purposes: (i) to give credit
to any reused content; (ii) to substantiate claims. In the conclusion
of the report, one uses \emph{visionary citations} to connect to
subjects that were not but cut be covered, or that are worth being
mentioned otherwise.

Seminar participants must prove that they use advanced means of
locating prior work. The \href{http://portal.acm.org/}{ACM Digital
  Library} and the
\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
particularly suited to search for scientific publications on topics of
the SL seminar.

Every edition of the SL seminar is unique, but here are some general
pointers for research on software languages; again, every edition of
the SL seminar may draw from additional sources, as it should be
evident from the seminar edition's design. Thus:

\begin{itemize}
\item SLE---Software Language Engineering
\item ASE---Automated Software Engineering
\item ICPC---International Conference on Program Comprehension
\item POPL---Principles of Programming Languages
\item OOPSLA---OO Programming, Systems, Languages, and Applications
\item MODELS--- Model Driven Engineering Languages and Systems
\item WCRE---Working Conference on Reverse Engineering
\item ICSM---International Conference on Software Maintenance
\item MSR---Mining Software Repositories
\item PLDI---Programm Language Design and Implementation
\item PPDP---Principles and Practice of Declarative Programming
\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
\end{itemize}

There are also various journals on similar themes that may provide
seminal and archival content for the seminar work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Abstraction is king, not page count}

There is no use in reproducing or condensing one specific paper (or a
series of strongly connected papers). Any reasonable seminar report
must exercise abstraction; it must study a subject from an individual
point of view with an original research question in mind. A reasonable
seminar report involves (3+) different pieces of scholarly work and
integrates them in the presentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Advice on the presentation}
\label{S:presentation}

This section provides another example of what should be called a
technical section. Again, in such sections, the author works out the
technical details (say, meat) of all research work. There can be any
number of such sections. One should think hard about organization
principles to make up the appropriate number of sections and
subsections.

This section briefly talks about the presentation part of the seminar.
Just as in the case of scientific writing, there exists online or
published advice on ``how to give a good talk'', perhaps even in
seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
extremely difficult, but also very rewarding. Speakers should sure to
do some amount of reflection before they go into your talk. Some rules
of thumb follow:

\begin{itemize}

\item Finalizing the slides the night before is perhaps Ok, but one
  should start thinking of the talk way ahead of time. Otherwise, the
  presentation may likely to be boring or stressful and sends the
  audience to sleep. Speakers should not waste the precious cycles of
  the audience! As an aside, the available time should be perfectly
  leveraged by the talk: not more, not less.

\item One should not confuse writing with talking. One should not
  think of the talk as a way to present the paper in a condensed
  style. Instead, one should design the talk in a way that its
  structure and style maintains the attention of the audience and
  keeps up with the audience's abilities. One should use the talk to
  get people interested in the subject. One should motivate the
  audience to read more about the subject in the report that is
  advertised by the presentation.

\item One should not waste time on outlines; they are often totally
  useless at the time they are shown. One should focus on motivation
  from the first slide on. One should make good use of illustrations
  and simplify matters. One should not try to tell every detail, but
  to select some interesting details and make clear what else could
  be discussed or is included into the paper.

\item Seminar talks should be interactive. Hence, clarifying
  questions should be admitted.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Concluding remarks}
\label{S:concl}

These notes are supposed to be useful as is, but further efforts may
be needed to convey all witness and intentions. For the time being,
the author asks the seminar participants and other readers to work
with what is available and the quoted resources. Everyone is welcome
to suggest revisions for these notes.

### 2015-08-06 presentations/paper/paper.tex
Add an abstract for the paper

@@
 \begin{abstract}
+  In 2014, the Git surpassed Subversion as the top code management tool \cite{EComSurv14}.
+With so many authors colaborating comes the need for a appropriate and standardized use of elemental actions like doing commits.
+Although the official Git documentation states very clear guidelines \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or simply ignore them.
+  This paper presents a tool that analyzes a set of commits regarding criteria composed of the official guidelines and some common mistakes, and shows a prototypical website that encourages improvements in commit-etiquette by creating a competitive score-board for a given GitHub repository.
+We also perform a machine learning powered analysis of correlations between all criteria.
+
   This should be 100-200 words. Use present or past tense, but use it

### 2015-08-06 presentations/paper/paper.tex
Remove ralle's stuff and hard wrap abstract

@@
 \begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool \cite{EComSurv14}.
-With so many authors colaborating comes the need for a appropriate and standardized use of elemental actions like doing commits.
-Although the official Git documentation states very clear guidelines \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or simply ignore them.
-  This paper presents a tool that analyzes a set of commits regarding criteria composed of the official guidelines and some common mistakes, and shows a prototypical website that encourages improvements in commit-etiquette by creating a competitive score-board for a given GitHub repository.
-We also perform a machine learning powered analysis of correlations between all criteria.
+  In 2014, the Git surpassed Subversion as the top code management tool
+  \cite{EComSurv14}. With so many authors colaborating comes the need for a
+  appropriate and standardized use of elemental actions like doing commits.
+  Although the official Git documentation states very clear guidelines
+  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
+  simply ignore them.
 
-  This should be 100-200 words. Use present or past tense, but use it
-  consistently. Prefer ``we'' over ``I'' here and throughout the
-  paper. The abstract should summarize the methodology and results;
-  see the corresponding sections below. Your paper is preferably
-  typeset with LaTeX and it should comply with the Springer LNCS
-  style. (That style is also available for word users.)
+  This paper presents a tool that analyzes a set of commits regarding criteria
+  composed of the official guidelines and some common mistakes, and shows a
+  prototypical website that encourages improvements in commit-etiquette by
+  creating a competitive score-board for a given GitHub repository. We also
+  perform a machine learning powered analysis of correlations between all
+  criteria.
 \end{abstract}

### 2015-08-06 presentations/paper/paper.tex
Fix Marco's English in abstract

--- 2015-08-05 presentations/paper/paper.tex
@@
 \begin{abstract}
-  This should be 100-200 words. Use present or past tense, but use it
-  consistently. Prefer ``we'' over ``I'' here and throughout the
-  paper. The abstract should summarize the methodology and results;
-  see the corresponding sections below. Your paper is preferably
-  typeset with LaTeX and it should comply with the Springer LNCS
-  style. (That style is also available for word users.) 
+  In 2014, Git surpassed Subversion as the top code management tool
+  \cite{EComSurv14}. With many authors collaborating comes the need for an
+  appropriate and standardized use of elemental actions, like formulating
+  commit messages. Although the official Git documentation states very clear
+  guidelines \cite{OffGuide} on how this should be done, maby of users are not
+  aware of them or simply ignore them.
+
+  This paper presents a tool that analyzes a set of commit messages regarding
+  criteria composed of the official guidelines and some common mistakes, and
+  shows a prototypical website that encourages improvements in commit message
+  style by creating a competitive score-board for a given GitHub repository. We
+  also perform a machine-learning-powered analysis of correlations between the
+  criteria, which can help improve the selection of criteria in the future.
 \end{abstract}

### 2015-08-06 presentations/paper/paper.tex
Fix my own English in abstract

@@
   commit messages. Although the official Git documentation states very clear
-  guidelines \cite{OffGuide} on how this should be done, maby of users are not
-  aware of them or simply ignore them.
+  guidelines \cite{OffGuide} on how this should be done, many users are either
+  unaware or simply ignore them.
 

### 2015-08-24 presentations/paper/abstract.tex
Move sections into separate files

\begin{abstract}
  In 2014, the Git surpassed Subversion as the top code management tool
  \cite{EComSurv14}. With so many authors colaborating comes the need for a
  appropriate and standardized use of elemental actions like doing commits.
  Although the official Git documentation states very clear guidelines
  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
  simply ignore them.

  This paper presents a tool that analyzes a set of commits regarding criteria
  composed of the official guidelines and some common mistakes, and shows a
  prototypical website that encourages improvements in commit-etiquette by
  creating a competitive score-board for a given GitHub repository. We also
  perform a machine learning powered analysis of correlations between all
  criteria.
\end{abstract}

### 2015-08-24 presentations/paper/conclusion.tex
Move sections into separate files

--- 2015-08-06 presentations/paper/paper.tex
@@
-% TODO
-% - provide general advice on how to define the research problem
-% - ... on how to do practical parts
-
-\documentclass{llncs}
-
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{comment}
-
-\pagenumbering{arabic}
-
-\begin{document}
-
-\title{Annotated metamodel for MSR course papers}
-
-\subtitle{Version as of 30 June 2015}
-
-\author{Ralf L\"ammel}
-
-\institute{Software Languages Team, CS Faculty, University of Koblenz-Landau}
-
-\maketitle
-
-\begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool
-  \cite{EComSurv14}. With so many authors colaborating comes the need for a
-  appropriate and standardized use of elemental actions like doing commits.
-  Although the official Git documentation states very clear guidelines
-  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
-  simply ignore them.
-
-  This paper presents a tool that analyzes a set of commits regarding criteria
-  composed of the official guidelines and some common mistakes, and shows a
-  prototypical website that encourages improvements in commit-etiquette by
-  creating a competitive score-board for a given GitHub repository. We also
-  perform a machine learning powered analysis of correlations between all
-  criteria.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Address these questions:
-
-\begin{itemize}
-
-\item What is the context of this research?
-
-\item What is the overall challenge addressed by this research?
-
-\item What is the overall approach adopted by the research?
-
-\item Summarize results very briefly.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Research question}
-
-State 1-5 research questions. One question could be enough. More is
-not better.
-
-For each question, make clear why this is an interesting question. For
-example, try to make clear why a scientist or a practician would
-benefit from knowing the answer to the question.
-
-Lay out some background for your research questions. That is, what
-body of related work may be worth mentioning and comparing to the
-research at hand. This may be related in terms of both relevant
-methodology or similar research questions.
-
-You should make sure to carry out a proper related work study. Use
-DBLP on the MSR conference for 2+
-years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
-welcome to search other conferences and journals. Coming to the
-conclusion that there is no related work is absolutely
-unacceptable. Again, you need to show related work awareness so that
-your research question is substantiated as being relevant and
-your methodology is deeply informed by existing publications.
-
-In many cases, you want to refine your research questions into actual
-hypotheses, i.e., something that is potentially falsifiable, subject
-to an appropriate approach towards measuring.
-
-It is also common to refine research questions. That is, one starts
-with a general (overall) research question and takes it appart into
-several questions that are concrete enough to be researched on and to
-be answered. In this manner, you may often suffice with one or two
-research questions which are however refined into perhaps
-several questions. Again, even without refinement, just one question may be
-Ok. This depends on the nature of the project and on the kind of question.
-
-Here are some recommended MSR papers by the Software Languages
-Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
-consult to see instances of the concepts discussed in this
-metamodel. These papers may or may not be in an optimal form to
-function as good advice. You are also advised to have a look at some
-MSR papers (from the MSR conference), but again, they may also
-slightly vary in terms of consistency of style. if you like to get
-general advice on scientific writing, then I recommend relevant
-textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
-writing and by having someone with experience to provide feedback.
-
-You should most definitely have a look at this excellent tutorial on
-empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
-relates. General ESE is quite often concerned with controlled
-experiments and other research methods that involve subjects, whereas
-MSR is more concerned with automated analysis, but the text is still
-very helpful in coming to grips with research methods in software
-engineering overall. Specifically, it helps with formulating research questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-The methodology section must give a very clear account of what sort of
-procedure was executed. Here are some detailed criteria:
-%
-\begin{itemize}
-\item The section is preferably a step-by-step procedure overall. First we did
-  this. Then we did this.
-\item Steps should be motivated or defended, whenever it is not
-  obvious why a certain choice was made. However, one should be
-  careful not to preempt the discussion of threats to validity; see
-  the extra section below.
-\item The text should support reproducibility. In particular, a
-  reasonably knowledgeable person should be able to re-execute the
-  methodology and compare the results.
-\item The text should not get into low-level (implementation)
-  details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
-\end{itemize}
-
-\subsection{Data extraction}
-
-This metamodel is concerned with MSR papers. Thus, the methodology
-section would be reasonably subdivided into the three major phases of
-an MSR research project.
-
-The subsection on data extraction is concerned with issues like the
-following:
-
-\begin{itemize}
-\item What repository was chosen and why?
-\item What sort of extraction techniques is applied?
-\item What sort of extra processing (e.g., filtering) is applied?
-\item What constraints were chosen to help with scalability?
-\end{itemize}
-
-\subsection{Data synthesis}
-
-Even the simplest MSR project carries out synthesis; data analysis (see
-below) may not be carried out in all the cases. The subsection on data
-synthesis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item What metrics are used?
-
-\item What machine learning techniques are used?
-
-\item What information retrieval techniques are used?
-
-\end{itemize}
-
-The typical MSR paper picks either metrics or machine learning or IR.
-
-\subsection{Data analysis}
-
-Data analysis would be concerned with any sort of statistical quality
-analysis of the data. More specifically, the subsection on data
-analysis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item Simple statistics like median of metrics.
-
-\item Analysis of regression or correlation or distribution.
-
-\item Analysis of accuracy such as precision and recall.
-
-\end{itemize}
-
-It should be noted that the methodology section describes the `how'
-(and to some extent the`why'), but it does not yet report the various
-results; see the following section. For instance, the methodology may
-explain why it is using a certain metric and define it and announce
-that the median for the metric is going to be determined, as it would
-provide a certain insight, but the actual tables or charts for the
-metric and the interpretation of the findings would be deferred to the
-results section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-
-\noindent
-Summarize results in terms of tables, charts, and other kinds of
-figures.
-
-Explain and interpret the results.
-
-Get back to the research question and make sure that it is explicitly answered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Threats to validity}
-
-There are external and internal threats to validity. See the softlang
-papers and MSR papers for examples. See this resource~\cite{Michael04}
-for an explanation. Be concise and systematic about answering
-questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Conclusion}
@@
 identified in the threats to validity section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Details}
-\label{S:details}
-
-Any sort of interesting details such as source code, extra data (extra
-to the key results), extra procedural details supporting
-reproducibility can be listed here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{paper}
-\bibliographystyle{abbrv}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Generally, this seminar (series) is about ``software languages'' (SL)
-and hence it combines elements of software engineering, modelling,
-programming languages, linguistics, formal specification, and
-programming theory; see a recent discussion of some relevant fields
-and terminology~\cite{FavreGLP10}.
-
-Each particular edition of the SL seminar focuses on a specific topic
-within the broader area of SL. (For instance, an edition may focus on
-programming-language usage \cite{HageK08} or natural language aspects
-in programming \cite{HostO08}.) The present notes provide some general
-advice on the reporting and presentation obligations of the seminar's
-participants. These notes are meant to be generic with regard to the
-particular theme of a specific seminar edition.
-
-That is, the purpose of these notes is to help student participants
-writing their reports and preparing their presentations. These notes
-complement the meetings and consultations.
-
-\subsection*{Road-map}
-
-In \S\ref{S:report}, advice on the report part of the seminar is
-provided.
-
-\noindent
-In \S\ref{S:presentation}, advice on the presentation part
-is provided.
-
-\noindent
-These notes are summarized in \S\ref{S:concl}.
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the report}
-\label{S:report}
-
-Much has been written and said about scientific writing.  A report for
-this seminar is a small exercise in scientific writing. Hence,
-seminar participants are \emph{strongly encouraged} to gain basic
-understanding of scientific writing. For instance, seminar
-participants may consult a resource such as
-\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
-does not plan for education on scientific writing, neither does any
-other obligatory course. Hence, seminar participants are bound to
-consult a designated book or online resource, and to work closely
-together with the prof to get a reasonable result.\footnote{Here is
-  another resource on writing and giving talks:
-  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
-The following notes try to get seminar participants off the ground.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Organization of the report}
-
-As far as reports for the seminar are concerned, we assume a rather
-simple organization. A report would be spending about 10-25 pages in
-Springer's LNCS style to describe the research work carried out.
-
-Reports should use close 10 pages if there are not any substantial
-illustrations. Reports can use up to 25 pages, but \textbf{a higher
-  page count does not imply a better grade}---potentially it may
-negatively affect the grade. However, illustrations are strongly
-encouraged, if they truly illustrate the subject at hand. So seminar
-participants are welcome to exhaust a 25 pages limit with useful
-illustrations included.
-
-A report would have a title and an abstract. The purpose of an
-abstract is to properly summarize the report: use 50-200 words,
-typically 100-150 words.
-
-A report consists of an introduction, several technical sections,
-possibly a related work section, and a conclusion section. See below
-for more details.
-
-\subsection{The importance of the introduction}
-
-A report should start with an \emph{introduction section} which
-motivates the subject of the report, possibly states one or more
-\emph{research questions}, typically provides some background material
-(if such material is not placed in a subsequent, designated section or
-an appendix), lists \emph{contributions} of the report, and describes
-the organization of the rest of the report. Judgement of all submitted
-work may be biased by the introduction.
-
-If there is any ingredient that is critical to an excellent completion
-of the seminar, then this is the formulation of a \emph{research
-  question}. By default (for such a short report/paper that is meant
-here), the research question should be identified in the introduction
-section. The challenge is here to formulate a question that performs
-well in all of the following dimensions: a) concise and clear; b)
-informed and nontrivial; c) operationally intelligent and verifiable;
-d) meaningful to the rest of the text.
-
-\subsection{The technical sections}
-
-After the introduction, there can be any number of \emph{technical
-  sections}.  These sections constitute the core (``technical meat'')
-of the report. The style of these technical sections very much depends
-on the subject and the chosen sources as well as the assumed style of
-presentation.
-
-As there are many different styles, and we do not want to discuss them
-here at length. The best advice may be to leverage the corpus of
-consulted research papers and to try approximating the style of one of
-them. The prof wants to help on this matter---during the consultations
-and otherwise.
-
-\subsection{The concluding section}
-
-After the technical sections, the report should be concluded by a
-final section. Typically, such a section contains bits of summary,
-discussion, interpretations, open problems or future work, and
-vision. This may be a good place for the student to show that he or
-she has outgrown the view of one or two specific papers and can
-usefully operate in a broader research context. Again, an excellent
-student would make a serious effort to connect several research papers
-and research directions in a comprehensible, informative, and
-cross-indexing manner.
-
-\subsection{Literature references}
-
-One important element of scholarly writing is to make appropriate use
-of citations. For instance, in the introduction section, one needs to
-provide \emph{contextual citations} so that the overall context of the
-research effort at hand is clarified. One may also quickly mention
-some more technical sources as a means to prepare for the more
-detailed parts of the report. Throughout the paper, one uses
-\emph{technical citations} for two major purposes: (i) to give credit
-to any reused content; (ii) to substantiate claims. In the conclusion
-of the report, one uses \emph{visionary citations} to connect to
-subjects that were not but cut be covered, or that are worth being
-mentioned otherwise.
-
-Seminar participants must prove that they use advanced means of
-locating prior work. The \href{http://portal.acm.org/}{ACM Digital
-  Library} and the
-\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
-particularly suited to search for scientific publications on topics of
-the SL seminar.
-
-Every edition of the SL seminar is unique, but here are some general
-pointers for research on software languages; again, every edition of
-the SL seminar may draw from additional sources, as it should be
-evident from the seminar edition's design. Thus:
-
-\begin{itemize}
-\item SLE---Software Language Engineering
-\item ASE---Automated Software Engineering
-\item ICPC---International Conference on Program Comprehension
-\item POPL---Principles of Programming Languages
-\item OOPSLA---OO Programming, Systems, Languages, and Applications
-\item MODELS--- Model Driven Engineering Languages and Systems
-\item WCRE---Working Conference on Reverse Engineering
-\item ICSM---International Conference on Software Maintenance
-\item MSR---Mining Software Repositories
-\item PLDI---Programm Language Design and Implementation
-\item PPDP---Principles and Practice of Declarative Programming
-\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
-\end{itemize}
-
-There are also various journals on similar themes that may provide
-seminal and archival content for the seminar work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Abstraction is king, not page count}
-
-There is no use in reproducing or condensing one specific paper (or a
-series of strongly connected papers). Any reasonable seminar report
-must exercise abstraction; it must study a subject from an individual
-point of view with an original research question in mind. A reasonable
-seminar report involves (3+) different pieces of scholarly work and
-integrates them in the presentation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the presentation}
-\label{S:presentation}
-
-This section provides another example of what should be called a
-technical section. Again, in such sections, the author works out the
-technical details (say, meat) of all research work. There can be any
-number of such sections. One should think hard about organization
-principles to make up the appropriate number of sections and
-subsections.
-
-This section briefly talks about the presentation part of the seminar.
-Just as in the case of scientific writing, there exists online or
-published advice on ``how to give a good talk'', perhaps even in
-seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
-extremely difficult, but also very rewarding. Speakers should sure to
-do some amount of reflection before they go into your talk. Some rules
-of thumb follow:
-
-\begin{itemize}
-
-\item Finalizing the slides the night before is perhaps Ok, but one
-  should start thinking of the talk way ahead of time. Otherwise, the
-  presentation may likely to be boring or stressful and sends the
-  audience to sleep. Speakers should not waste the precious cycles of
-  the audience! As an aside, the available time should be perfectly
-  leveraged by the talk: not more, not less.
-
-\item One should not confuse writing with talking. One should not
-  think of the talk as a way to present the paper in a condensed
-  style. Instead, one should design the talk in a way that its
-  structure and style maintains the attention of the audience and
-  keeps up with the audience's abilities. One should use the talk to
-  get people interested in the subject. One should motivate the
-  audience to read more about the subject in the report that is
-  advertised by the presentation.
-
-\item One should not waste time on outlines; they are often totally
-  useless at the time they are shown. One should focus on motivation
-  from the first slide on. One should make good use of illustrations
-  and simplify matters. One should not try to tell every detail, but
-  to select some interesting details and make clear what else could
-  be discussed or is included into the paper.
-
-\item Seminar talks should be interactive. Hence, clarifying
-  questions should be admitted.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Concluding remarks}
-\label{S:concl}
-
-These notes are supposed to be useful as is, but further efforts may
-be needed to convey all witness and intentions. For the time being,
-the author asks the seminar participants and other readers to work
-with what is available and the quoted resources. Everyone is welcome
-to suggest revisions for these notes.

### 2015-08-24 presentations/paper/details.tex
Move sections into separate files

--- 2015-08-06 presentations/paper/paper.tex
@@
-% TODO
-% - provide general advice on how to define the research problem
-% - ... on how to do practical parts
-
-\documentclass{llncs}
-
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{comment}
-
-\pagenumbering{arabic}
-
-\begin{document}
-
-\title{Annotated metamodel for MSR course papers}
-
-\subtitle{Version as of 30 June 2015}
-
-\author{Ralf L\"ammel}
-
-\institute{Software Languages Team, CS Faculty, University of Koblenz-Landau}
-
-\maketitle
-
-\begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool
-  \cite{EComSurv14}. With so many authors colaborating comes the need for a
-  appropriate and standardized use of elemental actions like doing commits.
-  Although the official Git documentation states very clear guidelines
-  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
-  simply ignore them.
-
-  This paper presents a tool that analyzes a set of commits regarding criteria
-  composed of the official guidelines and some common mistakes, and shows a
-  prototypical website that encourages improvements in commit-etiquette by
-  creating a competitive score-board for a given GitHub repository. We also
-  perform a machine learning powered analysis of correlations between all
-  criteria.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Address these questions:
-
-\begin{itemize}
-
-\item What is the context of this research?
-
-\item What is the overall challenge addressed by this research?
-
-\item What is the overall approach adopted by the research?
-
-\item Summarize results very briefly.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Research question}
-
-State 1-5 research questions. One question could be enough. More is
-not better.
-
-For each question, make clear why this is an interesting question. For
-example, try to make clear why a scientist or a practician would
-benefit from knowing the answer to the question.
-
-Lay out some background for your research questions. That is, what
-body of related work may be worth mentioning and comparing to the
-research at hand. This may be related in terms of both relevant
-methodology or similar research questions.
-
-You should make sure to carry out a proper related work study. Use
-DBLP on the MSR conference for 2+
-years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
-welcome to search other conferences and journals. Coming to the
-conclusion that there is no related work is absolutely
-unacceptable. Again, you need to show related work awareness so that
-your research question is substantiated as being relevant and
-your methodology is deeply informed by existing publications.
-
-In many cases, you want to refine your research questions into actual
-hypotheses, i.e., something that is potentially falsifiable, subject
-to an appropriate approach towards measuring.
-
-It is also common to refine research questions. That is, one starts
-with a general (overall) research question and takes it appart into
-several questions that are concrete enough to be researched on and to
-be answered. In this manner, you may often suffice with one or two
-research questions which are however refined into perhaps
-several questions. Again, even without refinement, just one question may be
-Ok. This depends on the nature of the project and on the kind of question.
-
-Here are some recommended MSR papers by the Software Languages
-Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
-consult to see instances of the concepts discussed in this
-metamodel. These papers may or may not be in an optimal form to
-function as good advice. You are also advised to have a look at some
-MSR papers (from the MSR conference), but again, they may also
-slightly vary in terms of consistency of style. if you like to get
-general advice on scientific writing, then I recommend relevant
-textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
-writing and by having someone with experience to provide feedback.
-
-You should most definitely have a look at this excellent tutorial on
-empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
-relates. General ESE is quite often concerned with controlled
-experiments and other research methods that involve subjects, whereas
-MSR is more concerned with automated analysis, but the text is still
-very helpful in coming to grips with research methods in software
-engineering overall. Specifically, it helps with formulating research questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-The methodology section must give a very clear account of what sort of
-procedure was executed. Here are some detailed criteria:
-%
-\begin{itemize}
-\item The section is preferably a step-by-step procedure overall. First we did
-  this. Then we did this.
-\item Steps should be motivated or defended, whenever it is not
-  obvious why a certain choice was made. However, one should be
-  careful not to preempt the discussion of threats to validity; see
-  the extra section below.
-\item The text should support reproducibility. In particular, a
-  reasonably knowledgeable person should be able to re-execute the
-  methodology and compare the results.
-\item The text should not get into low-level (implementation)
-  details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
-\end{itemize}
-
-\subsection{Data extraction}
-
-This metamodel is concerned with MSR papers. Thus, the methodology
-section would be reasonably subdivided into the three major phases of
-an MSR research project.
-
-The subsection on data extraction is concerned with issues like the
-following:
-
-\begin{itemize}
-\item What repository was chosen and why?
-\item What sort of extraction techniques is applied?
-\item What sort of extra processing (e.g., filtering) is applied?
-\item What constraints were chosen to help with scalability?
-\end{itemize}
-
-\subsection{Data synthesis}
-
-Even the simplest MSR project carries out synthesis; data analysis (see
-below) may not be carried out in all the cases. The subsection on data
-synthesis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item What metrics are used?
-
-\item What machine learning techniques are used?
-
-\item What information retrieval techniques are used?
-
-\end{itemize}
-
-The typical MSR paper picks either metrics or machine learning or IR.
-
-\subsection{Data analysis}
-
-Data analysis would be concerned with any sort of statistical quality
-analysis of the data. More specifically, the subsection on data
-analysis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item Simple statistics like median of metrics.
-
-\item Analysis of regression or correlation or distribution.
-
-\item Analysis of accuracy such as precision and recall.
-
-\end{itemize}
-
-It should be noted that the methodology section describes the `how'
-(and to some extent the`why'), but it does not yet report the various
-results; see the following section. For instance, the methodology may
-explain why it is using a certain metric and define it and announce
-that the median for the metric is going to be determined, as it would
-provide a certain insight, but the actual tables or charts for the
-metric and the interpretation of the findings would be deferred to the
-results section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-
-\noindent
-Summarize results in terms of tables, charts, and other kinds of
-figures.
-
-Explain and interpret the results.
-
-Get back to the research question and make sure that it is explicitly answered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Threats to validity}
-
-There are external and internal threats to validity. See the softlang
-papers and MSR papers for examples. See this resource~\cite{Michael04}
-for an explanation. Be concise and systematic about answering
-questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-This is essentially a redundant section. Try to summarize your
-research from a more informed point of view. (We assume that the
-reader has read the paper and is ready for some deeper conclusion.)
-You could very well add some perspectives for future work, without
-repeating smaller scale weakness of research, as they were already
-identified in the threats to validity section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
 \section{Details}
@@
 reproducibility can be listed here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{paper}
-\bibliographystyle{abbrv}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Generally, this seminar (series) is about ``software languages'' (SL)
-and hence it combines elements of software engineering, modelling,
-programming languages, linguistics, formal specification, and
-programming theory; see a recent discussion of some relevant fields
-and terminology~\cite{FavreGLP10}.
-
-Each particular edition of the SL seminar focuses on a specific topic
-within the broader area of SL. (For instance, an edition may focus on
-programming-language usage \cite{HageK08} or natural language aspects
-in programming \cite{HostO08}.) The present notes provide some general
-advice on the reporting and presentation obligations of the seminar's
-participants. These notes are meant to be generic with regard to the
-particular theme of a specific seminar edition.
-
-That is, the purpose of these notes is to help student participants
-writing their reports and preparing their presentations. These notes
-complement the meetings and consultations.
-
-\subsection*{Road-map}
-
-In \S\ref{S:report}, advice on the report part of the seminar is
-provided.
-
-\noindent
-In \S\ref{S:presentation}, advice on the presentation part
-is provided.
-
-\noindent
-These notes are summarized in \S\ref{S:concl}.
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the report}
-\label{S:report}
-
-Much has been written and said about scientific writing.  A report for
-this seminar is a small exercise in scientific writing. Hence,
-seminar participants are \emph{strongly encouraged} to gain basic
-understanding of scientific writing. For instance, seminar
-participants may consult a resource such as
-\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
-does not plan for education on scientific writing, neither does any
-other obligatory course. Hence, seminar participants are bound to
-consult a designated book or online resource, and to work closely
-together with the prof to get a reasonable result.\footnote{Here is
-  another resource on writing and giving talks:
-  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
-The following notes try to get seminar participants off the ground.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Organization of the report}
-
-As far as reports for the seminar are concerned, we assume a rather
-simple organization. A report would be spending about 10-25 pages in
-Springer's LNCS style to describe the research work carried out.
-
-Reports should use close 10 pages if there are not any substantial
-illustrations. Reports can use up to 25 pages, but \textbf{a higher
-  page count does not imply a better grade}---potentially it may
-negatively affect the grade. However, illustrations are strongly
-encouraged, if they truly illustrate the subject at hand. So seminar
-participants are welcome to exhaust a 25 pages limit with useful
-illustrations included.
-
-A report would have a title and an abstract. The purpose of an
-abstract is to properly summarize the report: use 50-200 words,
-typically 100-150 words.
-
-A report consists of an introduction, several technical sections,
-possibly a related work section, and a conclusion section. See below
-for more details.
-
-\subsection{The importance of the introduction}
-
-A report should start with an \emph{introduction section} which
-motivates the subject of the report, possibly states one or more
-\emph{research questions}, typically provides some background material
-(if such material is not placed in a subsequent, designated section or
-an appendix), lists \emph{contributions} of the report, and describes
-the organization of the rest of the report. Judgement of all submitted
-work may be biased by the introduction.
-
-If there is any ingredient that is critical to an excellent completion
-of the seminar, then this is the formulation of a \emph{research
-  question}. By default (for such a short report/paper that is meant
-here), the research question should be identified in the introduction
-section. The challenge is here to formulate a question that performs
-well in all of the following dimensions: a) concise and clear; b)
-informed and nontrivial; c) operationally intelligent and verifiable;
-d) meaningful to the rest of the text.
-
-\subsection{The technical sections}
-
-After the introduction, there can be any number of \emph{technical
-  sections}.  These sections constitute the core (``technical meat'')
-of the report. The style of these technical sections very much depends
-on the subject and the chosen sources as well as the assumed style of
-presentation.
-
-As there are many different styles, and we do not want to discuss them
-here at length. The best advice may be to leverage the corpus of
-consulted research papers and to try approximating the style of one of
-them. The prof wants to help on this matter---during the consultations
-and otherwise.
-
-\subsection{The concluding section}
-
-After the technical sections, the report should be concluded by a
-final section. Typically, such a section contains bits of summary,
-discussion, interpretations, open problems or future work, and
-vision. This may be a good place for the student to show that he or
-she has outgrown the view of one or two specific papers and can
-usefully operate in a broader research context. Again, an excellent
-student would make a serious effort to connect several research papers
-and research directions in a comprehensible, informative, and
-cross-indexing manner.
-
-\subsection{Literature references}
-
-One important element of scholarly writing is to make appropriate use
-of citations. For instance, in the introduction section, one needs to
-provide \emph{contextual citations} so that the overall context of the
-research effort at hand is clarified. One may also quickly mention
-some more technical sources as a means to prepare for the more
-detailed parts of the report. Throughout the paper, one uses
-\emph{technical citations} for two major purposes: (i) to give credit
-to any reused content; (ii) to substantiate claims. In the conclusion
-of the report, one uses \emph{visionary citations} to connect to
-subjects that were not but cut be covered, or that are worth being
-mentioned otherwise.
-
-Seminar participants must prove that they use advanced means of
-locating prior work. The \href{http://portal.acm.org/}{ACM Digital
-  Library} and the
-\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
-particularly suited to search for scientific publications on topics of
-the SL seminar.
-
-Every edition of the SL seminar is unique, but here are some general
-pointers for research on software languages; again, every edition of
-the SL seminar may draw from additional sources, as it should be
-evident from the seminar edition's design. Thus:
-
-\begin{itemize}
-\item SLE---Software Language Engineering
-\item ASE---Automated Software Engineering
-\item ICPC---International Conference on Program Comprehension
-\item POPL---Principles of Programming Languages
-\item OOPSLA---OO Programming, Systems, Languages, and Applications
-\item MODELS--- Model Driven Engineering Languages and Systems
-\item WCRE---Working Conference on Reverse Engineering
-\item ICSM---International Conference on Software Maintenance
-\item MSR---Mining Software Repositories
-\item PLDI---Programm Language Design and Implementation
-\item PPDP---Principles and Practice of Declarative Programming
-\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
-\end{itemize}
-
-There are also various journals on similar themes that may provide
-seminal and archival content for the seminar work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Abstraction is king, not page count}
-
-There is no use in reproducing or condensing one specific paper (or a
-series of strongly connected papers). Any reasonable seminar report
-must exercise abstraction; it must study a subject from an individual
-point of view with an original research question in mind. A reasonable
-seminar report involves (3+) different pieces of scholarly work and
-integrates them in the presentation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the presentation}
-\label{S:presentation}
-
-This section provides another example of what should be called a
-technical section. Again, in such sections, the author works out the
-technical details (say, meat) of all research work. There can be any
-number of such sections. One should think hard about organization
-principles to make up the appropriate number of sections and
-subsections.
-
-This section briefly talks about the presentation part of the seminar.
-Just as in the case of scientific writing, there exists online or
-published advice on ``how to give a good talk'', perhaps even in
-seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
-extremely difficult, but also very rewarding. Speakers should sure to
-do some amount of reflection before they go into your talk. Some rules
-of thumb follow:
-
-\begin{itemize}
-
-\item Finalizing the slides the night before is perhaps Ok, but one
-  should start thinking of the talk way ahead of time. Otherwise, the
-  presentation may likely to be boring or stressful and sends the
-  audience to sleep. Speakers should not waste the precious cycles of
-  the audience! As an aside, the available time should be perfectly
-  leveraged by the talk: not more, not less.
-
-\item One should not confuse writing with talking. One should not
-  think of the talk as a way to present the paper in a condensed
-  style. Instead, one should design the talk in a way that its
-  structure and style maintains the attention of the audience and
-  keeps up with the audience's abilities. One should use the talk to
-  get people interested in the subject. One should motivate the
-  audience to read more about the subject in the report that is
-  advertised by the presentation.
-
-\item One should not waste time on outlines; they are often totally
-  useless at the time they are shown. One should focus on motivation
-  from the first slide on. One should make good use of illustrations
-  and simplify matters. One should not try to tell every detail, but
-  to select some interesting details and make clear what else could
-  be discussed or is included into the paper.
-
-\item Seminar talks should be interactive. Hence, clarifying
-  questions should be admitted.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Concluding remarks}
-\label{S:concl}
-
-These notes are supposed to be useful as is, but further efforts may
-be needed to convey all witness and intentions. For the time being,
-the author asks the seminar participants and other readers to work
-with what is available and the quoted resources. Everyone is welcome
-to suggest revisions for these notes.

### 2015-08-24 presentations/paper/introduction.tex
Move sections into separate files

--- 2015-08-06 presentations/paper/paper.tex
@@
-% TODO
-% - provide general advice on how to define the research problem
-% - ... on how to do practical parts
-
-\documentclass{llncs}
-
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{comment}
-
-\pagenumbering{arabic}
-
-\begin{document}
-
-\title{Annotated metamodel for MSR course papers}
-
-\subtitle{Version as of 30 June 2015}
-
-\author{Ralf L\"ammel}
-
-\institute{Software Languages Team, CS Faculty, University of Koblenz-Landau}
-
-\maketitle
-
-\begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool
-  \cite{EComSurv14}. With so many authors colaborating comes the need for a
-  appropriate and standardized use of elemental actions like doing commits.
-  Although the official Git documentation states very clear guidelines
-  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
-  simply ignore them.
-
-  This paper presents a tool that analyzes a set of commits regarding criteria
-  composed of the official guidelines and some common mistakes, and shows a
-  prototypical website that encourages improvements in commit-etiquette by
-  creating a competitive score-board for a given GitHub repository. We also
-  perform a machine learning powered analysis of correlations between all
-  criteria.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Introduction}
@@
 \end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Research question}
-
-State 1-5 research questions. One question could be enough. More is
-not better.
-
-For each question, make clear why this is an interesting question. For
-example, try to make clear why a scientist or a practician would
-benefit from knowing the answer to the question.
-
-Lay out some background for your research questions. That is, what
-body of related work may be worth mentioning and comparing to the
-research at hand. This may be related in terms of both relevant
-methodology or similar research questions.
-
-You should make sure to carry out a proper related work study. Use
-DBLP on the MSR conference for 2+
-years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
-welcome to search other conferences and journals. Coming to the
-conclusion that there is no related work is absolutely
-unacceptable. Again, you need to show related work awareness so that
-your research question is substantiated as being relevant and
-your methodology is deeply informed by existing publications.
-
-In many cases, you want to refine your research questions into actual
-hypotheses, i.e., something that is potentially falsifiable, subject
-to an appropriate approach towards measuring.
-
-It is also common to refine research questions. That is, one starts
-with a general (overall) research question and takes it appart into
-several questions that are concrete enough to be researched on and to
-be answered. In this manner, you may often suffice with one or two
-research questions which are however refined into perhaps
-several questions. Again, even without refinement, just one question may be
-Ok. This depends on the nature of the project and on the kind of question.
-
-Here are some recommended MSR papers by the Software Languages
-Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
-consult to see instances of the concepts discussed in this
-metamodel. These papers may or may not be in an optimal form to
-function as good advice. You are also advised to have a look at some
-MSR papers (from the MSR conference), but again, they may also
-slightly vary in terms of consistency of style. if you like to get
-general advice on scientific writing, then I recommend relevant
-textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
-writing and by having someone with experience to provide feedback.
-
-You should most definitely have a look at this excellent tutorial on
-empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
-relates. General ESE is quite often concerned with controlled
-experiments and other research methods that involve subjects, whereas
-MSR is more concerned with automated analysis, but the text is still
-very helpful in coming to grips with research methods in software
-engineering overall. Specifically, it helps with formulating research questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-The methodology section must give a very clear account of what sort of
-procedure was executed. Here are some detailed criteria:
-%
-\begin{itemize}
-\item The section is preferably a step-by-step procedure overall. First we did
-  this. Then we did this.
-\item Steps should be motivated or defended, whenever it is not
-  obvious why a certain choice was made. However, one should be
-  careful not to preempt the discussion of threats to validity; see
-  the extra section below.
-\item The text should support reproducibility. In particular, a
-  reasonably knowledgeable person should be able to re-execute the
-  methodology and compare the results.
-\item The text should not get into low-level (implementation)
-  details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
-\end{itemize}
-
-\subsection{Data extraction}
-
-This metamodel is concerned with MSR papers. Thus, the methodology
-section would be reasonably subdivided into the three major phases of
-an MSR research project.
-
-The subsection on data extraction is concerned with issues like the
-following:
-
-\begin{itemize}
-\item What repository was chosen and why?
-\item What sort of extraction techniques is applied?
-\item What sort of extra processing (e.g., filtering) is applied?
-\item What constraints were chosen to help with scalability?
-\end{itemize}
-
-\subsection{Data synthesis}
-
-Even the simplest MSR project carries out synthesis; data analysis (see
-below) may not be carried out in all the cases. The subsection on data
-synthesis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item What metrics are used?
-
-\item What machine learning techniques are used?
-
-\item What information retrieval techniques are used?
-
-\end{itemize}
-
-The typical MSR paper picks either metrics or machine learning or IR.
-
-\subsection{Data analysis}
-
-Data analysis would be concerned with any sort of statistical quality
-analysis of the data. More specifically, the subsection on data
-analysis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item Simple statistics like median of metrics.
-
-\item Analysis of regression or correlation or distribution.
-
-\item Analysis of accuracy such as precision and recall.
-
-\end{itemize}
-
-It should be noted that the methodology section describes the `how'
-(and to some extent the`why'), but it does not yet report the various
-results; see the following section. For instance, the methodology may
-explain why it is using a certain metric and define it and announce
-that the median for the metric is going to be determined, as it would
-provide a certain insight, but the actual tables or charts for the
-metric and the interpretation of the findings would be deferred to the
-results section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-
-\noindent
-Summarize results in terms of tables, charts, and other kinds of
-figures.
-
-Explain and interpret the results.
-
-Get back to the research question and make sure that it is explicitly answered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Threats to validity}
-
-There are external and internal threats to validity. See the softlang
-papers and MSR papers for examples. See this resource~\cite{Michael04}
-for an explanation. Be concise and systematic about answering
-questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-This is essentially a redundant section. Try to summarize your
-research from a more informed point of view. (We assume that the
-reader has read the paper and is ready for some deeper conclusion.)
-You could very well add some perspectives for future work, without
-repeating smaller scale weakness of research, as they were already
-identified in the threats to validity section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Details}
-\label{S:details}
-
-Any sort of interesting details such as source code, extra data (extra
-to the key results), extra procedural details supporting
-reproducibility can be listed here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{paper}
-\bibliographystyle{abbrv}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Generally, this seminar (series) is about ``software languages'' (SL)
-and hence it combines elements of software engineering, modelling,
-programming languages, linguistics, formal specification, and
-programming theory; see a recent discussion of some relevant fields
-and terminology~\cite{FavreGLP10}.
-
-Each particular edition of the SL seminar focuses on a specific topic
-within the broader area of SL. (For instance, an edition may focus on
-programming-language usage \cite{HageK08} or natural language aspects
-in programming \cite{HostO08}.) The present notes provide some general
-advice on the reporting and presentation obligations of the seminar's
-participants. These notes are meant to be generic with regard to the
-particular theme of a specific seminar edition.
-
-That is, the purpose of these notes is to help student participants
-writing their reports and preparing their presentations. These notes
-complement the meetings and consultations.
-
-\subsection*{Road-map}
-
-In \S\ref{S:report}, advice on the report part of the seminar is
-provided.
-
-\noindent
-In \S\ref{S:presentation}, advice on the presentation part
-is provided.
-
-\noindent
-These notes are summarized in \S\ref{S:concl}.
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the report}
-\label{S:report}
-
-Much has been written and said about scientific writing.  A report for
-this seminar is a small exercise in scientific writing. Hence,
-seminar participants are \emph{strongly encouraged} to gain basic
-understanding of scientific writing. For instance, seminar
-participants may consult a resource such as
-\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
-does not plan for education on scientific writing, neither does any
-other obligatory course. Hence, seminar participants are bound to
-consult a designated book or online resource, and to work closely
-together with the prof to get a reasonable result.\footnote{Here is
-  another resource on writing and giving talks:
-  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
-The following notes try to get seminar participants off the ground.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Organization of the report}
-
-As far as reports for the seminar are concerned, we assume a rather
-simple organization. A report would be spending about 10-25 pages in
-Springer's LNCS style to describe the research work carried out.
-
-Reports should use close 10 pages if there are not any substantial
-illustrations. Reports can use up to 25 pages, but \textbf{a higher
-  page count does not imply a better grade}---potentially it may
-negatively affect the grade. However, illustrations are strongly
-encouraged, if they truly illustrate the subject at hand. So seminar
-participants are welcome to exhaust a 25 pages limit with useful
-illustrations included.
-
-A report would have a title and an abstract. The purpose of an
-abstract is to properly summarize the report: use 50-200 words,
-typically 100-150 words.
-
-A report consists of an introduction, several technical sections,
-possibly a related work section, and a conclusion section. See below
-for more details.
-
-\subsection{The importance of the introduction}
-
-A report should start with an \emph{introduction section} which
-motivates the subject of the report, possibly states one or more
-\emph{research questions}, typically provides some background material
-(if such material is not placed in a subsequent, designated section or
-an appendix), lists \emph{contributions} of the report, and describes
-the organization of the rest of the report. Judgement of all submitted
-work may be biased by the introduction.
-
-If there is any ingredient that is critical to an excellent completion
-of the seminar, then this is the formulation of a \emph{research
-  question}. By default (for such a short report/paper that is meant
-here), the research question should be identified in the introduction
-section. The challenge is here to formulate a question that performs
-well in all of the following dimensions: a) concise and clear; b)
-informed and nontrivial; c) operationally intelligent and verifiable;
-d) meaningful to the rest of the text.
-
-\subsection{The technical sections}
-
-After the introduction, there can be any number of \emph{technical
-  sections}.  These sections constitute the core (``technical meat'')
-of the report. The style of these technical sections very much depends
-on the subject and the chosen sources as well as the assumed style of
-presentation.
-
-As there are many different styles, and we do not want to discuss them
-here at length. The best advice may be to leverage the corpus of
-consulted research papers and to try approximating the style of one of
-them. The prof wants to help on this matter---during the consultations
-and otherwise.
-
-\subsection{The concluding section}
-
-After the technical sections, the report should be concluded by a
-final section. Typically, such a section contains bits of summary,
-discussion, interpretations, open problems or future work, and
-vision. This may be a good place for the student to show that he or
-she has outgrown the view of one or two specific papers and can
-usefully operate in a broader research context. Again, an excellent
-student would make a serious effort to connect several research papers
-and research directions in a comprehensible, informative, and
-cross-indexing manner.
-
-\subsection{Literature references}
-
-One important element of scholarly writing is to make appropriate use
-of citations. For instance, in the introduction section, one needs to
-provide \emph{contextual citations} so that the overall context of the
-research effort at hand is clarified. One may also quickly mention
-some more technical sources as a means to prepare for the more
-detailed parts of the report. Throughout the paper, one uses
-\emph{technical citations} for two major purposes: (i) to give credit
-to any reused content; (ii) to substantiate claims. In the conclusion
-of the report, one uses \emph{visionary citations} to connect to
-subjects that were not but cut be covered, or that are worth being
-mentioned otherwise.
-
-Seminar participants must prove that they use advanced means of
-locating prior work. The \href{http://portal.acm.org/}{ACM Digital
-  Library} and the
-\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
-particularly suited to search for scientific publications on topics of
-the SL seminar.
-
-Every edition of the SL seminar is unique, but here are some general
-pointers for research on software languages; again, every edition of
-the SL seminar may draw from additional sources, as it should be
-evident from the seminar edition's design. Thus:
-
-\begin{itemize}
-\item SLE---Software Language Engineering
-\item ASE---Automated Software Engineering
-\item ICPC---International Conference on Program Comprehension
-\item POPL---Principles of Programming Languages
-\item OOPSLA---OO Programming, Systems, Languages, and Applications
-\item MODELS--- Model Driven Engineering Languages and Systems
-\item WCRE---Working Conference on Reverse Engineering
-\item ICSM---International Conference on Software Maintenance
-\item MSR---Mining Software Repositories
-\item PLDI---Programm Language Design and Implementation
-\item PPDP---Principles and Practice of Declarative Programming
-\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
-\end{itemize}
-
-There are also various journals on similar themes that may provide
-seminal and archival content for the seminar work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Abstraction is king, not page count}
-
-There is no use in reproducing or condensing one specific paper (or a
-series of strongly connected papers). Any reasonable seminar report
-must exercise abstraction; it must study a subject from an individual
-point of view with an original research question in mind. A reasonable
-seminar report involves (3+) different pieces of scholarly work and
-integrates them in the presentation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the presentation}
-\label{S:presentation}
-
-This section provides another example of what should be called a
-technical section. Again, in such sections, the author works out the
-technical details (say, meat) of all research work. There can be any
-number of such sections. One should think hard about organization
-principles to make up the appropriate number of sections and
-subsections.
-
-This section briefly talks about the presentation part of the seminar.
-Just as in the case of scientific writing, there exists online or
-published advice on ``how to give a good talk'', perhaps even in
-seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
-extremely difficult, but also very rewarding. Speakers should sure to
-do some amount of reflection before they go into your talk. Some rules
-of thumb follow:
-
-\begin{itemize}
-
-\item Finalizing the slides the night before is perhaps Ok, but one
-  should start thinking of the talk way ahead of time. Otherwise, the
-  presentation may likely to be boring or stressful and sends the
-  audience to sleep. Speakers should not waste the precious cycles of
-  the audience! As an aside, the available time should be perfectly
-  leveraged by the talk: not more, not less.
-
-\item One should not confuse writing with talking. One should not
-  think of the talk as a way to present the paper in a condensed
-  style. Instead, one should design the talk in a way that its
-  structure and style maintains the attention of the audience and
-  keeps up with the audience's abilities. One should use the talk to
-  get people interested in the subject. One should motivate the
-  audience to read more about the subject in the report that is
-  advertised by the presentation.
-
-\item One should not waste time on outlines; they are often totally
-  useless at the time they are shown. One should focus on motivation
-  from the first slide on. One should make good use of illustrations
-  and simplify matters. One should not try to tell every detail, but
-  to select some interesting details and make clear what else could
-  be discussed or is included into the paper.
-
-\item Seminar talks should be interactive. Hence, clarifying
-  questions should be admitted.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Concluding remarks}
-\label{S:concl}
-
-These notes are supposed to be useful as is, but further efforts may
-be needed to convey all witness and intentions. For the time being,
-the author asks the seminar participants and other readers to work
-with what is available and the quoted resources. Everyone is welcome
-to suggest revisions for these notes.

### 2015-08-24 presentations/paper/methodology.tex
Move sections into separate files

--- 2015-08-06 presentations/paper/paper.tex
@@
-% TODO
-% - provide general advice on how to define the research problem
-% - ... on how to do practical parts
-
-\documentclass{llncs}
-
-\usepackage{hyperref}
-\usepackage{url}
-\usepackage{comment}
-
-\pagenumbering{arabic}
-
-\begin{document}
-
-\title{Annotated metamodel for MSR course papers}
-
-\subtitle{Version as of 30 June 2015}
-
-\author{Ralf L\"ammel}
-
-\institute{Software Languages Team, CS Faculty, University of Koblenz-Landau}
-
-\maketitle
-
-\begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool
-  \cite{EComSurv14}. With so many authors colaborating comes the need for a
-  appropriate and standardized use of elemental actions like doing commits.
-  Although the official Git documentation states very clear guidelines
-  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
-  simply ignore them.
-
-  This paper presents a tool that analyzes a set of commits regarding criteria
-  composed of the official guidelines and some common mistakes, and shows a
-  prototypical website that encourages improvements in commit-etiquette by
-  creating a competitive score-board for a given GitHub repository. We also
-  perform a machine learning powered analysis of correlations between all
-  criteria.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Address these questions:
-
-\begin{itemize}
-
-\item What is the context of this research?
-
-\item What is the overall challenge addressed by this research?
-
-\item What is the overall approach adopted by the research?
-
-\item Summarize results very briefly.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Research question}
-
-State 1-5 research questions. One question could be enough. More is
-not better.
-
-For each question, make clear why this is an interesting question. For
-example, try to make clear why a scientist or a practician would
-benefit from knowing the answer to the question.
-
-Lay out some background for your research questions. That is, what
-body of related work may be worth mentioning and comparing to the
-research at hand. This may be related in terms of both relevant
-methodology or similar research questions.
-
-You should make sure to carry out a proper related work study. Use
-DBLP on the MSR conference for 2+
-years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
-welcome to search other conferences and journals. Coming to the
-conclusion that there is no related work is absolutely
-unacceptable. Again, you need to show related work awareness so that
-your research question is substantiated as being relevant and
-your methodology is deeply informed by existing publications.
-
-In many cases, you want to refine your research questions into actual
-hypotheses, i.e., something that is potentially falsifiable, subject
-to an appropriate approach towards measuring.
-
-It is also common to refine research questions. That is, one starts
-with a general (overall) research question and takes it appart into
-several questions that are concrete enough to be researched on and to
-be answered. In this manner, you may often suffice with one or two
-research questions which are however refined into perhaps
-several questions. Again, even without refinement, just one question may be
-Ok. This depends on the nature of the project and on the kind of question.
-
-Here are some recommended MSR papers by the Software Languages
-Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
-consult to see instances of the concepts discussed in this
-metamodel. These papers may or may not be in an optimal form to
-function as good advice. You are also advised to have a look at some
-MSR papers (from the MSR conference), but again, they may also
-slightly vary in terms of consistency of style. if you like to get
-general advice on scientific writing, then I recommend relevant
-textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
-writing and by having someone with experience to provide feedback.
-
-You should most definitely have a look at this excellent tutorial on
-empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
-relates. General ESE is quite often concerned with controlled
-experiments and other research methods that involve subjects, whereas
-MSR is more concerned with automated analysis, but the text is still
-very helpful in coming to grips with research methods in software
-engineering overall. Specifically, it helps with formulating research questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \section{Methodology}
@@
 results section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-
-\noindent
-Summarize results in terms of tables, charts, and other kinds of
-figures.
-
-Explain and interpret the results.
-
-Get back to the research question and make sure that it is explicitly answered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Threats to validity}
-
-There are external and internal threats to validity. See the softlang
-papers and MSR papers for examples. See this resource~\cite{Michael04}
-for an explanation. Be concise and systematic about answering
-questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-This is essentially a redundant section. Try to summarize your
-research from a more informed point of view. (We assume that the
-reader has read the paper and is ready for some deeper conclusion.)
-You could very well add some perspectives for future work, without
-repeating smaller scale weakness of research, as they were already
-identified in the threats to validity section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\appendix
-
-\section{Details}
-\label{S:details}
-
-Any sort of interesting details such as source code, extra data (extra
-to the key results), extra procedural details supporting
-reproducibility can be listed here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\bibliography{paper}
-\bibliographystyle{abbrv}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\end{document}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Generally, this seminar (series) is about ``software languages'' (SL)
-and hence it combines elements of software engineering, modelling,
-programming languages, linguistics, formal specification, and
-programming theory; see a recent discussion of some relevant fields
-and terminology~\cite{FavreGLP10}.
-
-Each particular edition of the SL seminar focuses on a specific topic
-within the broader area of SL. (For instance, an edition may focus on
-programming-language usage \cite{HageK08} or natural language aspects
-in programming \cite{HostO08}.) The present notes provide some general
-advice on the reporting and presentation obligations of the seminar's
-participants. These notes are meant to be generic with regard to the
-particular theme of a specific seminar edition.
-
-That is, the purpose of these notes is to help student participants
-writing their reports and preparing their presentations. These notes
-complement the meetings and consultations.
-
-\subsection*{Road-map}
-
-In \S\ref{S:report}, advice on the report part of the seminar is
-provided.
-
-\noindent
-In \S\ref{S:presentation}, advice on the presentation part
-is provided.
-
-\noindent
-These notes are summarized in \S\ref{S:concl}.
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the report}
-\label{S:report}
-
-Much has been written and said about scientific writing.  A report for
-this seminar is a small exercise in scientific writing. Hence,
-seminar participants are \emph{strongly encouraged} to gain basic
-understanding of scientific writing. For instance, seminar
-participants may consult a resource such as
-\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
-does not plan for education on scientific writing, neither does any
-other obligatory course. Hence, seminar participants are bound to
-consult a designated book or online resource, and to work closely
-together with the prof to get a reasonable result.\footnote{Here is
-  another resource on writing and giving talks:
-  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
-The following notes try to get seminar participants off the ground.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Organization of the report}
-
-As far as reports for the seminar are concerned, we assume a rather
-simple organization. A report would be spending about 10-25 pages in
-Springer's LNCS style to describe the research work carried out.
-
-Reports should use close 10 pages if there are not any substantial
-illustrations. Reports can use up to 25 pages, but \textbf{a higher
-  page count does not imply a better grade}---potentially it may
-negatively affect the grade. However, illustrations are strongly
-encouraged, if they truly illustrate the subject at hand. So seminar
-participants are welcome to exhaust a 25 pages limit with useful
-illustrations included.
-
-A report would have a title and an abstract. The purpose of an
-abstract is to properly summarize the report: use 50-200 words,
-typically 100-150 words.
-
-A report consists of an introduction, several technical sections,
-possibly a related work section, and a conclusion section. See below
-for more details.
-
-\subsection{The importance of the introduction}
-
-A report should start with an \emph{introduction section} which
-motivates the subject of the report, possibly states one or more
-\emph{research questions}, typically provides some background material
-(if such material is not placed in a subsequent, designated section or
-an appendix), lists \emph{contributions} of the report, and describes
-the organization of the rest of the report. Judgement of all submitted
-work may be biased by the introduction.
-
-If there is any ingredient that is critical to an excellent completion
-of the seminar, then this is the formulation of a \emph{research
-  question}. By default (for such a short report/paper that is meant
-here), the research question should be identified in the introduction
-section. The challenge is here to formulate a question that performs
-well in all of the following dimensions: a) concise and clear; b)
-informed and nontrivial; c) operationally intelligent and verifiable;
-d) meaningful to the rest of the text.
-
-\subsection{The technical sections}
-
-After the introduction, there can be any number of \emph{technical
-  sections}.  These sections constitute the core (``technical meat'')
-of the report. The style of these technical sections very much depends
-on the subject and the chosen sources as well as the assumed style of
-presentation.
-
-As there are many different styles, and we do not want to discuss them
-here at length. The best advice may be to leverage the corpus of
-consulted research papers and to try approximating the style of one of
-them. The prof wants to help on this matter---during the consultations
-and otherwise.
-
-\subsection{The concluding section}
-
-After the technical sections, the report should be concluded by a
-final section. Typically, such a section contains bits of summary,
-discussion, interpretations, open problems or future work, and
-vision. This may be a good place for the student to show that he or
-she has outgrown the view of one or two specific papers and can
-usefully operate in a broader research context. Again, an excellent
-student would make a serious effort to connect several research papers
-and research directions in a comprehensible, informative, and
-cross-indexing manner.
-
-\subsection{Literature references}
-
-One important element of scholarly writing is to make appropriate use
-of citations. For instance, in the introduction section, one needs to
-provide \emph{contextual citations} so that the overall context of the
-research effort at hand is clarified. One may also quickly mention
-some more technical sources as a means to prepare for the more
-detailed parts of the report. Throughout the paper, one uses
-\emph{technical citations} for two major purposes: (i) to give credit
-to any reused content; (ii) to substantiate claims. In the conclusion
-of the report, one uses \emph{visionary citations} to connect to
-subjects that were not but cut be covered, or that are worth being
-mentioned otherwise.
-
-Seminar participants must prove that they use advanced means of
-locating prior work. The \href{http://portal.acm.org/}{ACM Digital
-  Library} and the
-\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
-particularly suited to search for scientific publications on topics of
-the SL seminar.
-
-Every edition of the SL seminar is unique, but here are some general
-pointers for research on software languages; again, every edition of
-the SL seminar may draw from additional sources, as it should be
-evident from the seminar edition's design. Thus:
-
-\begin{itemize}
-\item SLE---Software Language Engineering
-\item ASE---Automated Software Engineering
-\item ICPC---International Conference on Program Comprehension
-\item POPL---Principles of Programming Languages
-\item OOPSLA---OO Programming, Systems, Languages, and Applications
-\item MODELS--- Model Driven Engineering Languages and Systems
-\item WCRE---Working Conference on Reverse Engineering
-\item ICSM---International Conference on Software Maintenance
-\item MSR---Mining Software Repositories
-\item PLDI---Programm Language Design and Implementation
-\item PPDP---Principles and Practice of Declarative Programming
-\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
-\end{itemize}
-
-There are also various journals on similar themes that may provide
-seminal and archival content for the seminar work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Abstraction is king, not page count}
-
-There is no use in reproducing or condensing one specific paper (or a
-series of strongly connected papers). Any reasonable seminar report
-must exercise abstraction; it must study a subject from an individual
-point of view with an original research question in mind. A reasonable
-seminar report involves (3+) different pieces of scholarly work and
-integrates them in the presentation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the presentation}
-\label{S:presentation}
-
-This section provides another example of what should be called a
-technical section. Again, in such sections, the author works out the
-technical details (say, meat) of all research work. There can be any
-number of such sections. One should think hard about organization
-principles to make up the appropriate number of sections and
-subsections.
-
-This section briefly talks about the presentation part of the seminar.
-Just as in the case of scientific writing, there exists online or
-published advice on ``how to give a good talk'', perhaps even in
-seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
-extremely difficult, but also very rewarding. Speakers should sure to
-do some amount of reflection before they go into your talk. Some rules
-of thumb follow:
-
-\begin{itemize}
-
-\item Finalizing the slides the night before is perhaps Ok, but one
-  should start thinking of the talk way ahead of time. Otherwise, the
-  presentation may likely to be boring or stressful and sends the
-  audience to sleep. Speakers should not waste the precious cycles of
-  the audience! As an aside, the available time should be perfectly
-  leveraged by the talk: not more, not less.
-
-\item One should not confuse writing with talking. One should not
-  think of the talk as a way to present the paper in a condensed
-  style. Instead, one should design the talk in a way that its
-  structure and style maintains the attention of the audience and
-  keeps up with the audience's abilities. One should use the talk to
-  get people interested in the subject. One should motivate the
-  audience to read more about the subject in the report that is
-  advertised by the presentation.
-
-\item One should not waste time on outlines; they are often totally
-  useless at the time they are shown. One should focus on motivation
-  from the first slide on. One should make good use of illustrations
-  and simplify matters. One should not try to tell every detail, but
-  to select some interesting details and make clear what else could
-  be discussed or is included into the paper.
-
-\item Seminar talks should be interactive. Hence, clarifying
-  questions should be admitted.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Concluding remarks}
-\label{S:concl}
-
-These notes are supposed to be useful as is, but further efforts may
-be needed to convey all witness and intentions. For the time being,
-the author asks the seminar participants and other readers to work
-with what is available and the quoted resources. Everyone is welcome
-to suggest revisions for these notes.

### 2015-08-24 presentations/paper/paper.tex
Move sections into separate files

--- 2015-08-06 presentations/paper/paper.tex
@@
-% TODO
-% - provide general advice on how to define the research problem
-% - ... on how to do practical parts
-
 \documentclass{llncs}
@@
 \begin{document}
-
 \title{Annotated metamodel for MSR course papers}
-
 \subtitle{Version as of 30 June 2015}
-
 \author{Ralf L\"ammel}
-
 \institute{Software Languages Team, CS Faculty, University of Koblenz-Landau}
@@
 
-\begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool
-  \cite{EComSurv14}. With so many authors colaborating comes the need for a
-  appropriate and standardized use of elemental actions like doing commits.
-  Although the official Git documentation states very clear guidelines
-  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
-  simply ignore them.
-
-  This paper presents a tool that analyzes a set of commits regarding criteria
-  composed of the official guidelines and some common mistakes, and shows a
-  prototypical website that encourages improvements in commit-etiquette by
-  creating a competitive score-board for a given GitHub repository. We also
-  perform a machine learning powered analysis of correlations between all
-  criteria.
-\end{abstract}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Address these questions:
-
-\begin{itemize}
-
-\item What is the context of this research?
-
-\item What is the overall challenge addressed by this research?
-
-\item What is the overall approach adopted by the research?
-
-\item Summarize results very briefly.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Research question}
-
-State 1-5 research questions. One question could be enough. More is
-not better.
-
-For each question, make clear why this is an interesting question. For
-example, try to make clear why a scientist or a practician would
-benefit from knowing the answer to the question.
-
-Lay out some background for your research questions. That is, what
-body of related work may be worth mentioning and comparing to the
-research at hand. This may be related in terms of both relevant
-methodology or similar research questions.
-
-You should make sure to carry out a proper related work study. Use
-DBLP on the MSR conference for 2+
-years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
-welcome to search other conferences and journals. Coming to the
-conclusion that there is no related work is absolutely
-unacceptable. Again, you need to show related work awareness so that
-your research question is substantiated as being relevant and
-your methodology is deeply informed by existing publications.
-
-In many cases, you want to refine your research questions into actual
-hypotheses, i.e., something that is potentially falsifiable, subject
-to an appropriate approach towards measuring.
-
-It is also common to refine research questions. That is, one starts
-with a general (overall) research question and takes it appart into
-several questions that are concrete enough to be researched on and to
-be answered. In this manner, you may often suffice with one or two
-research questions which are however refined into perhaps
-several questions. Again, even without refinement, just one question may be
-Ok. This depends on the nature of the project and on the kind of question.
-
-Here are some recommended MSR papers by the Software Languages
-Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
-consult to see instances of the concepts discussed in this
-metamodel. These papers may or may not be in an optimal form to
-function as good advice. You are also advised to have a look at some
-MSR papers (from the MSR conference), but again, they may also
-slightly vary in terms of consistency of style. if you like to get
-general advice on scientific writing, then I recommend relevant
-textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
-writing and by having someone with experience to provide feedback.
-
-You should most definitely have a look at this excellent tutorial on
-empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
-relates. General ESE is quite often concerned with controlled
-experiments and other research methods that involve subjects, whereas
-MSR is more concerned with automated analysis, but the text is still
-very helpful in coming to grips with research methods in software
-engineering overall. Specifically, it helps with formulating research questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Methodology}
-
-The methodology section must give a very clear account of what sort of
-procedure was executed. Here are some detailed criteria:
-%
-\begin{itemize}
-\item The section is preferably a step-by-step procedure overall. First we did
-  this. Then we did this.
-\item Steps should be motivated or defended, whenever it is not
-  obvious why a certain choice was made. However, one should be
-  careful not to preempt the discussion of threats to validity; see
-  the extra section below.
-\item The text should support reproducibility. In particular, a
-  reasonably knowledgeable person should be able to re-execute the
-  methodology and compare the results.
-\item The text should not get into low-level (implementation)
-  details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
-\end{itemize}
-
-\subsection{Data extraction}
-
-This metamodel is concerned with MSR papers. Thus, the methodology
-section would be reasonably subdivided into the three major phases of
-an MSR research project.
-
-The subsection on data extraction is concerned with issues like the
-following:
-
-\begin{itemize}
-\item What repository was chosen and why?
-\item What sort of extraction techniques is applied?
-\item What sort of extra processing (e.g., filtering) is applied?
-\item What constraints were chosen to help with scalability?
-\end{itemize}
-
-\subsection{Data synthesis}
-
-Even the simplest MSR project carries out synthesis; data analysis (see
-below) may not be carried out in all the cases. The subsection on data
-synthesis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item What metrics are used?
-
-\item What machine learning techniques are used?
-
-\item What information retrieval techniques are used?
-
-\end{itemize}
-
-The typical MSR paper picks either metrics or machine learning or IR.
-
-\subsection{Data analysis}
-
-Data analysis would be concerned with any sort of statistical quality
-analysis of the data. More specifically, the subsection on data
-analysis is concerned with issues like the following:
-
-\begin{itemize}
-
-\item Simple statistics like median of metrics.
-
-\item Analysis of regression or correlation or distribution.
-
-\item Analysis of accuracy such as precision and recall.
-
-\end{itemize}
-
-It should be noted that the methodology section describes the `how'
-(and to some extent the`why'), but it does not yet report the various
-results; see the following section. For instance, the methodology may
-explain why it is using a certain metric and define it and announce
-that the median for the metric is going to be determined, as it would
-provide a certain insight, but the actual tables or charts for the
-metric and the interpretation of the findings would be deferred to the
-results section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Results}
-
-\noindent
-Summarize results in terms of tables, charts, and other kinds of
-figures.
-
-Explain and interpret the results.
-
-Get back to the research question and make sure that it is explicitly answered.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Threats to validity}
-
-There are external and internal threats to validity. See the softlang
-papers and MSR papers for examples. See this resource~\cite{Michael04}
-for an explanation. Be concise and systematic about answering
-questions.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-This is essentially a redundant section. Try to summarize your
-research from a more informed point of view. (We assume that the
-reader has read the paper and is ready for some deeper conclusion.)
-You could very well add some perspectives for future work, without
-repeating smaller scale weakness of research, as they were already
-identified in the threats to validity section.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\include{abstract}
+\include{introduction}
+\include{research_question}
+\include{methodology}
+\include{results}
+\include{threads}
+\include{conclusion}
 
 \appendix
-
-\section{Details}
-\label{S:details}
-
-Any sort of interesting details such as source code, extra data (extra
-to the key results), extra procedural details supporting
-reproducibility can be listed here.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\include{details}
 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \end{document}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Introduction}
-
-Generally, this seminar (series) is about ``software languages'' (SL)
-and hence it combines elements of software engineering, modelling,
-programming languages, linguistics, formal specification, and
-programming theory; see a recent discussion of some relevant fields
-and terminology~\cite{FavreGLP10}.
-
-Each particular edition of the SL seminar focuses on a specific topic
-within the broader area of SL. (For instance, an edition may focus on
-programming-language usage \cite{HageK08} or natural language aspects
-in programming \cite{HostO08}.) The present notes provide some general
-advice on the reporting and presentation obligations of the seminar's
-participants. These notes are meant to be generic with regard to the
-particular theme of a specific seminar edition.
-
-That is, the purpose of these notes is to help student participants
-writing their reports and preparing their presentations. These notes
-complement the meetings and consultations.
-
-\subsection*{Road-map}
-
-In \S\ref{S:report}, advice on the report part of the seminar is
-provided.
-
-\noindent
-In \S\ref{S:presentation}, advice on the presentation part
-is provided.
-
-\noindent
-These notes are summarized in \S\ref{S:concl}.
-
-\pagebreak
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the report}
-\label{S:report}
-
-Much has been written and said about scientific writing.  A report for
-this seminar is a small exercise in scientific writing. Hence,
-seminar participants are \emph{strongly encouraged} to gain basic
-understanding of scientific writing. For instance, seminar
-participants may consult a resource such as
-\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
-does not plan for education on scientific writing, neither does any
-other obligatory course. Hence, seminar participants are bound to
-consult a designated book or online resource, and to work closely
-together with the prof to get a reasonable result.\footnote{Here is
-  another resource on writing and giving talks:
-  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
-The following notes try to get seminar participants off the ground.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Organization of the report}
-
-As far as reports for the seminar are concerned, we assume a rather
-simple organization. A report would be spending about 10-25 pages in
-Springer's LNCS style to describe the research work carried out.
-
-Reports should use close 10 pages if there are not any substantial
-illustrations. Reports can use up to 25 pages, but \textbf{a higher
-  page count does not imply a better grade}---potentially it may
-negatively affect the grade. However, illustrations are strongly
-encouraged, if they truly illustrate the subject at hand. So seminar
-participants are welcome to exhaust a 25 pages limit with useful
-illustrations included.
-
-A report would have a title and an abstract. The purpose of an
-abstract is to properly summarize the report: use 50-200 words,
-typically 100-150 words.
-
-A report consists of an introduction, several technical sections,
-possibly a related work section, and a conclusion section. See below
-for more details.
-
-\subsection{The importance of the introduction}
-
-A report should start with an \emph{introduction section} which
-motivates the subject of the report, possibly states one or more
-\emph{research questions}, typically provides some background material
-(if such material is not placed in a subsequent, designated section or
-an appendix), lists \emph{contributions} of the report, and describes
-the organization of the rest of the report. Judgement of all submitted
-work may be biased by the introduction.
-
-If there is any ingredient that is critical to an excellent completion
-of the seminar, then this is the formulation of a \emph{research
-  question}. By default (for such a short report/paper that is meant
-here), the research question should be identified in the introduction
-section. The challenge is here to formulate a question that performs
-well in all of the following dimensions: a) concise and clear; b)
-informed and nontrivial; c) operationally intelligent and verifiable;
-d) meaningful to the rest of the text.
-
-\subsection{The technical sections}
-
-After the introduction, there can be any number of \emph{technical
-  sections}.  These sections constitute the core (``technical meat'')
-of the report. The style of these technical sections very much depends
-on the subject and the chosen sources as well as the assumed style of
-presentation.
-
-As there are many different styles, and we do not want to discuss them
-here at length. The best advice may be to leverage the corpus of
-consulted research papers and to try approximating the style of one of
-them. The prof wants to help on this matter---during the consultations
-and otherwise.
-
-\subsection{The concluding section}
-
-After the technical sections, the report should be concluded by a
-final section. Typically, such a section contains bits of summary,
-discussion, interpretations, open problems or future work, and
-vision. This may be a good place for the student to show that he or
-she has outgrown the view of one or two specific papers and can
-usefully operate in a broader research context. Again, an excellent
-student would make a serious effort to connect several research papers
-and research directions in a comprehensible, informative, and
-cross-indexing manner.
-
-\subsection{Literature references}
-
-One important element of scholarly writing is to make appropriate use
-of citations. For instance, in the introduction section, one needs to
-provide \emph{contextual citations} so that the overall context of the
-research effort at hand is clarified. One may also quickly mention
-some more technical sources as a means to prepare for the more
-detailed parts of the report. Throughout the paper, one uses
-\emph{technical citations} for two major purposes: (i) to give credit
-to any reused content; (ii) to substantiate claims. In the conclusion
-of the report, one uses \emph{visionary citations} to connect to
-subjects that were not but cut be covered, or that are worth being
-mentioned otherwise.
-
-Seminar participants must prove that they use advanced means of
-locating prior work. The \href{http://portal.acm.org/}{ACM Digital
-  Library} and the
-\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
-particularly suited to search for scientific publications on topics of
-the SL seminar.
-
-Every edition of the SL seminar is unique, but here are some general
-pointers for research on software languages; again, every edition of
-the SL seminar may draw from additional sources, as it should be
-evident from the seminar edition's design. Thus:
-
-\begin{itemize}
-\item SLE---Software Language Engineering
-\item ASE---Automated Software Engineering
-\item ICPC---International Conference on Program Comprehension
-\item POPL---Principles of Programming Languages
-\item OOPSLA---OO Programming, Systems, Languages, and Applications
-\item MODELS--- Model Driven Engineering Languages and Systems
-\item WCRE---Working Conference on Reverse Engineering
-\item ICSM---International Conference on Software Maintenance
-\item MSR---Mining Software Repositories
-\item PLDI---Programm Language Design and Implementation
-\item PPDP---Principles and Practice of Declarative Programming
-\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
-\end{itemize}
-
-There are also various journals on similar themes that may provide
-seminal and archival content for the seminar work.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\subsection{Abstraction is king, not page count}
-
-There is no use in reproducing or condensing one specific paper (or a
-series of strongly connected papers). Any reasonable seminar report
-must exercise abstraction; it must study a subject from an individual
-point of view with an original research question in mind. A reasonable
-seminar report involves (3+) different pieces of scholarly work and
-integrates them in the presentation.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Advice on the presentation}
-\label{S:presentation}
-
-This section provides another example of what should be called a
-technical section. Again, in such sections, the author works out the
-technical details (say, meat) of all research work. There can be any
-number of such sections. One should think hard about organization
-principles to make up the appropriate number of sections and
-subsections.
-
-This section briefly talks about the presentation part of the seminar.
-Just as in the case of scientific writing, there exists online or
-published advice on ``how to give a good talk'', perhaps even in
-seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
-extremely difficult, but also very rewarding. Speakers should sure to
-do some amount of reflection before they go into your talk. Some rules
-of thumb follow:
-
-\begin{itemize}
-
-\item Finalizing the slides the night before is perhaps Ok, but one
-  should start thinking of the talk way ahead of time. Otherwise, the
-  presentation may likely to be boring or stressful and sends the
-  audience to sleep. Speakers should not waste the precious cycles of
-  the audience! As an aside, the available time should be perfectly
-  leveraged by the talk: not more, not less.
-
-\item One should not confuse writing with talking. One should not
-  think of the talk as a way to present the paper in a condensed
-  style. Instead, one should design the talk in a way that its
-  structure and style maintains the attention of the audience and
-  keeps up with the audience's abilities. One should use the talk to
-  get people interested in the subject. One should motivate the
-  audience to read more about the subject in the report that is
-  advertised by the presentation.
-
-\item One should not waste time on outlines; they are often totally
-  useless at the time they are shown. One should focus on motivation
-  from the first slide on. One should make good use of illustrations
-  and simplify matters. One should not try to tell every detail, but
-  to select some interesting details and make clear what else could
-  be discussed or is included into the paper.
-
-\item Seminar talks should be interactive. Hence, clarifying
-  questions should be admitted.
-
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Concluding remarks}
-\label{S:concl}
-
-These notes are supposed to be useful as is, but further efforts may
-be needed to convey all witness and intentions. For the time being,
-the author asks the seminar participants and other readers to work
-with what is available and the quoted resources. Everyone is welcome
-to suggest revisions for these notes.
+\include{notes}

### 2015-08-24 presentations/paper/research_question.tex
Move sections into separate files

\section{Research question}

State 1-5 research questions. One question could be enough. More is
not better.

For each question, make clear why this is an interesting question. For
example, try to make clear why a scientist or a practician would
benefit from knowing the answer to the question.

Lay out some background for your research questions. That is, what
body of related work may be worth mentioning and comparing to the
research at hand. This may be related in terms of both relevant
methodology or similar research questions.

You should make sure to carry out a proper related work study. Use
DBLP on the MSR conference for 2+
years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
welcome to search other conferences and journals. Coming to the
conclusion that there is no related work is absolutely
unacceptable. Again, you need to show related work awareness so that
your research question is substantiated as being relevant and
your methodology is deeply informed by existing publications.

In many cases, you want to refine your research questions into actual
hypotheses, i.e., something that is potentially falsifiable, subject
to an appropriate approach towards measuring.

It is also common to refine research questions. That is, one starts
with a general (overall) research question and takes it appart into
several questions that are concrete enough to be researched on and to
be answered. In this manner, you may often suffice with one or two
research questions which are however refined into perhaps
several questions. Again, even without refinement, just one question may be
Ok. This depends on the nature of the project and on the kind of question.

Here are some recommended MSR papers by the Software Languages
Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
consult to see instances of the concepts discussed in this
metamodel. These papers may or may not be in an optimal form to
function as good advice. You are also advised to have a look at some
MSR papers (from the MSR conference), but again, they may also
slightly vary in terms of consistency of style. if you like to get
general advice on scientific writing, then I recommend relevant
textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
writing and by having someone with experience to provide feedback.

You should most definitely have a look at this excellent tutorial on
empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
relates. General ESE is quite often concerned with controlled
experiments and other research methods that involve subjects, whereas
MSR is more concerned with automated analysis, but the text is still
very helpful in coming to grips with research methods in software
engineering overall. Specifically, it helps with formulating research questions.

### 2015-08-24 presentations/paper/results.tex
Move sections into separate files

\section{Results}

\noindent
Summarize results in terms of tables, charts, and other kinds of
figures.

Explain and interpret the results.

Get back to the research question and make sure that it is explicitly answered.

### 2015-08-24 presentations/paper/methodology.tex
Add methodology section intro

@@
 \section{Methodology}
+% The methodology section must give a very clear account of what sort of
+% procedure was executed. Here are some detailed criteria:
 
-The methodology section must give a very clear account of what sort of
-procedure was executed. Here are some detailed criteria:
-%
+Our methodology is divided into the three typical phases of a MSR research project:
+
+% \begin{itemize}
+% \item The section is preferably a step-by-step procedure overall. First we did
+%   this. Then we did this.
+% \item Steps should be motivated or defended, whenever it is not
+%   obvious why a certain choice was made. However, one should be
+%   careful not to preempt the discussion of threats to validity; see
+%   the extra section below.
+% \item The text should support reproducibility. In particular, a
+%   reasonably knowledgeable person should be able to re-execute the
+%   methodology and compare the results.
+% \item The text should not get into low-level (implementation)
+%   details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
+% \end{itemize}
+
 \begin{itemize}
-\item The section is preferably a step-by-step procedure overall. First we did
-  this. Then we did this.
-\item Steps should be motivated or defended, whenever it is not
-  obvious why a certain choice was made. However, one should be
-  careful not to preempt the discussion of threats to validity; see
-  the extra section below.
-\item The text should support reproducibility. In particular, a
-  reasonably knowledgeable person should be able to re-execute the
-  methodology and compare the results.
-\item The text should not get into low-level (implementation)
-  details. These can be deferred to separate documentation; see Appendix~\ref{S:details}.
+  \item Data Extraction.
+Since we wanted to be able to compare arbitrary Git repositories, we decided to \texttt{git clone} repos directly, instead of accessing commits via a proprietary API like GitHub's.
+  \item Data Synthesis.
+This includes checking commits against our criteria, which will be detailed below.
+The synthesized metrics are counts of met or unmet criteria grouped by the commit author email.
+  \item Data Analysis. We use a set of repositories and analyse our synthesis results for interesting statistics and relations between criteria.
 \end{itemize}

### 2015-08-24 presentations/paper/methodology.tex
Add TODOs to Data Analysis

@@
 
-\subsection{Data extraction}
+\subsection{Data Extraction}
 
-This metamodel is concerned with MSR papers. Thus, the methodology
-section would be reasonably subdivided into the three major phases of
-an MSR research project.
+% This metamodel is concerned with MSR papers. Thus, the methodology
+% section would be reasonably subdivided into the three major phases of
+% an MSR research project.
+%
+% The subsection on data extraction is concerned with issues like the
+% following:
+%
+% \begin{itemize}
+% \item What repository was chosen and why?
+% \item What sort of extraction techniques is applied?
+% \item What sort of extra processing (e.g., filtering) is applied?
+% \item What constraints were chosen to help with scalability?
+% \end{itemize}
 
-The subsection on data extraction is concerned with issues like the
-following:
+% TODO: Describe extraction process
+% TODO: Describe preprocessing and output
+% TODO: Mention commit-limit
+% TODO: Introduce example repos
 
-\begin{itemize}
-\item What repository was chosen and why?
-\item What sort of extraction techniques is applied?
-\item What sort of extra processing (e.g., filtering) is applied?
-\item What constraints were chosen to help with scalability?
-\end{itemize}
+\subsection{Data Synthesis}
 
-\subsection{Data synthesis}
+% Even the simplest MSR project carries out synthesis; data analysis (see
+% below) may not be carried out in all the cases. The subsection on data
+% synthesis is concerned with issues like the following:
+%
+% \begin{itemize}
+%
+% \item What metrics are used?
+%
+% \item What machine learning techniques are used?
+%
+% \item What information retrieval techniques are used?
+%
+% \end{itemize}
+%
+% The typical MSR paper picks either metrics or machine learning or IR.
 
-Even the simplest MSR project carries out synthesis; data analysis (see
-below) may not be carried out in all the cases. The subsection on data
-synthesis is concerned with issues like the following:
+% TODO: Describe general synthesis process, focusing on input and output
+% TODO: List all criteria with details
+% TODO: Try to express criteria as metrics
+% TODO: Put special focus on those Natural Language Processing
+% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation
 
-\begin{itemize}
-
-\item What metrics are used?
-
-\item What machine learning techniques are used?
-
-\item What information retrieval techniques are used?
-
-\end{itemize}
-
-The typical MSR paper picks either metrics or machine learning or IR.
-
-\subsection{Data analysis}
+\subsection{Data Analysis}
 

### 2015-08-24 presentations/paper/methodology.tex
Add TODOs to Data ExtractionÂ

--- 2015-08-24 presentations/paper/methodology.tex
@@
 
-This metamodel is concerned with MSR papers. Thus, the methodology
-section would be reasonably subdivided into the three major phases of
-an MSR research project.
+% This metamodel is concerned with MSR papers. Thus, the methodology
+% section would be reasonably subdivided into the three major phases of
+% an MSR research project.
+%
+% The subsection on data extraction is concerned with issues like the
+% following:
+%
+% \begin{itemize}
+% \item What repository was chosen and why?
+% \item What sort of extraction techniques is applied?
+% \item What sort of extra processing (e.g., filtering) is applied?
+% \item What constraints were chosen to help with scalability?
+% \end{itemize}
 
-The subsection on data extraction is concerned with issues like the
-following:
-
-\begin{itemize}
-\item What repository was chosen and why?
-\item What sort of extraction techniques is applied?
-\item What sort of extra processing (e.g., filtering) is applied?
-\item What constraints were chosen to help with scalability?
-\end{itemize}
+% TODO: Describe extraction process
+% TODO: Describe preprocessing and output
+% TODO: Mention commit-limit
+% TODO: Introduce example repos
 

### 2015-08-24 presentations/paper/methodology.tex
Add TODOs to Data Analysis

--- 2015-08-24 presentations/paper/methodology.tex
@@
 % TODO: List all criteria with details
-% TODO: Try to express criteria as metrics
+% TODO: Try to express criteria as metrics. I guess we count how many of an author's commits meet each criterion, and that count is our metric.
 % TODO: Put special focus on those Natural Language Processing
@@
 
-Data analysis would be concerned with any sort of statistical quality
-analysis of the data. More specifically, the subsection on data
-analysis is concerned with issues like the following:
+% Data analysis would be concerned with any sort of statistical quality
+% analysis of the data. More specifically, the subsection on data
+% analysis is concerned with issues like the following:
+%
+% \begin{itemize}
+%
+% \item Simple statistics like median of metrics.
+%
+% \item Analysis of regression or correlation or distribution.
+%
+% \item Analysis of accuracy such as precision and recall.
+%
+% \end{itemize}
+%
+% It should be noted that the methodology section describes the `how'
+% (and to some extent the`why'), but it does not yet report the various
+% results; see the following section. For instance, the methodology may
+% explain why it is using a certain metric and define it and announce
+% that the median for the metric is going to be determined, as it would
+% provide a certain insight, but the actual tables or charts for the
+% metric and the interpretation of the findings would be deferred to the
+% results section.
 
-\begin{itemize}
-
-\item Simple statistics like median of metrics.
-
-\item Analysis of regression or correlation or distribution.
-
-\item Analysis of accuracy such as precision and recall.
-
-\end{itemize}
-
-It should be noted that the methodology section describes the `how'
-(and to some extent the`why'), but it does not yet report the various
-results; see the following section. For instance, the methodology may
-explain why it is using a certain metric and define it and announce
-that the median for the metric is going to be determined, as it would
-provide a certain insight, but the actual tables or charts for the
-metric and the interpretation of the findings would be deferred to the
-results section.
+% TODO: Decide on analysis tools
+% * Weka
+% * Some Boxplots including averages for all metrics
+% TODO: Introduce the analysis tools we used

### 2015-08-24 presentations/paper/methodology.tex
Add stubs for criteria descriptions

@@
 
+Each commit of an author has been testet against the following criteria.
+While most tests either \emph{fail} or \emph{pass}, some criteria may not be appliccable in some situations, e.g.
+a commit message's body cannot be tested for a per-line character limit, if there is no body at all.
+In those cases, the criterion-test will count as \emph{undefined}.
+
+\subsubsection{subject_limit}
+\label{subs:subject_limit}
+
+\subsubsection{capitalize_subject}
+\label{subs:capitalize_subject}
+
+\subsubsection{no_period_subject}
+\label{subs:no_period_subject}
+
+\subsubsection{imperative_subject}
+\label{subs:imperative_subject}
+
+\subsubsection{body_used}
+\label{subs:body_used}
+
+\subsubsection{body_limit}
+\label{subs:body_limit}
+
+\subsubsection{empty_second_line}
+\label{subs:empty_second_line}
+
+\subsubsection{no_short_message}
+\label{subs:no_short_message}
+
+\subsubsection{no_long_message}
+\label{subs:no_long_message}
+
+\subsubsection{no_bulk_change}
+\label{subs:no_bulk_change}
+
+\subsubsection{no_vulgarity}
+\label{subs:no_vulgarity}
+
+\subsubsection{no_misspelling}
+\label{subs:no_misspelling}
+
+\subsubsection{no_duplicate}
+\label{subs:no_duplicate}
+
 \subsection{Data Analysis}

### 2015-08-24 presentations/paper/methodology.tex
Describe our synthesis without detailing criteria

@@
 
-% TODO: Describe general synthesis process, focusing on input and output
-% TODO: List all criteria with details
-% TODO: Try to express criteria as metrics. I guess we count how many of an author's commits meet each criterion, and that count is our metric.
 % TODO: Put special focus on those Natural Language Processing
@@
 
-Each commit of an author has been testet against the following criteria.
-While most tests either \emph{fail} or \emph{pass}, some criteria may not be appliccable in some situations, e.g.
+Each commit of an author is testet against the criteria below.
+While most tests either \emph{fail} or \emph{pass}, some criteria may not be appliccable in certain situations, e.g.
 a commit message's body cannot be tested for a per-line character limit, if there is no body at all.
 In those cases, the criterion-test will count as \emph{undefined}.
+
+The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion for each author. This triples will be used as a metric for the analysis in \ref{sub:analysis}.
+
+Almost all of the criteria below relate to the commit message.
+Only one of them states a very superficial rule about the changes in the commit.
+None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language.
+By keeping our criteria language-independent, they remain appliccable to all Git Repositories.
+
+In general, commit messages should consist of a subject line and a body \cite{OffGuide}.
+\cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post.
+Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message.
+Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}).
+
+The remaining 6 criteria have been chosen by the authors.
+Since there are no other sources to back our claim that failing to meet them makes a commit ``worse'', we will explain our reasoning behind the choices.
+Additionally, our criteria can be proven as valid, if there is a correlation between them and the criteria taken from credible sources.
+%TODO: THIS IS A WILD FUCKING GUESS AND WE BETTER FINALLY USE WEKA AND GET SOME RESULTS
+
+% TODO: List all criteria with details
 
@@
 \subsection{Data Analysis}
+\label{sub:analysis}
 

### 2015-08-24 presentations/paper/methodology.tex
Escape underscores in subsubsection titles
Explain subject_limit

@@
 \label{subs:subject_limit}
+The subject line, i.e.
+the first line of a commit message, should be limited to 50 characters.
+This rule seems to have originated from a blog post by Tim Pope \cite{TP}, which is referenced by the Git manual \cite{OffGuide}.
+The reasoning behind it is, that the subject line is used by various tools and user interfaces to describe a commit in limited space.
+
+Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does.
+Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without much language-specific effort.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain capitalize_subject

@@
 \label{subs:capitalize_subject}
+The first letter of the subject line should be capitalized.
+Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the english language start with a capital letter.
+This rule is only mentioned by \cite{CB}.
+It may not be as important as other rules, but fullfilling it requires little effort and makes reading the message a nicer.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain imperative-subject

@@
 \label{subs:no_period_subject}
+The subject line should have no trailing period.
+It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{empty_second_line}) and omitting it helps with the 50 character limit.
+Again, the only explicit mention of this rule is \cite{CB}, although the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both seem to agree on this.
 
@@
 \label{subs:imperative_subject}
+The subject line should be written in imperative present, e.g.
+``Add a function that...'' (as mentioned in \cite{OffGuide}).
+There are a lot of opinions on this rule and many authors seem to prefer regular present tense (e.g.
+``Adds a function that...'') or past tense (e.g.
+``Added a function that...''), which both have their own justification.
+The most important reason to use the imperative is consistency with git itself, which usually generates messages this way, the most prominent example being messages of automatic merges (e.g.
+``Merge branch \'master\' of https://github.com/hartenfels/Commit-Rater'').
+\cite{CB} gives a very nice explanation on how to write messages in the imperative.
+
+This criterion requires natural language processing of the commit
+message.
+For this purpose we use a perl module \footnote{http://search.cpan.org/dist/Lingua-EN-Tagger/Tagger.pm} and use it to get a list of the forms of the words in the subject line.
+If the list contains a verb in base present form, the criterion is passed.
+This is of course a very heuristic approach, but it successfully fails regular present tense or past tense subjet lines and furthermore ensures that there is a verb, so that nonsense messages like ``Some changes'' are failed too.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain body_used

@@
 \label{subs:body_used}
+Additionally to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}).
+The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines.
+It is also acceptable to use bullet points.
+This criterion only checks if there is a body.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain body_limit
Explain empty_second_line

@@
 \label{subs:body_limit}
+The lines of the body should be limited to 72 characters (originally stated in \cite{TP}).
+As with the subject line limit, this ensures proper display of the (full) commit message with limited space available.
+The test on this criterion will be undefined if no body is used.
 
@@
 \label{subs:empty_second_line}
+The subject line and the body should be separated by an empty line (\cite{TP}).
+This is how programs (including git itself) parsing the commit message which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial.
+If no body is used, the test on this criterion will be undefined.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain no_short_message

@@
 
+The following six criteria have been chosen by the authors. Some state the obvious and most should be easy to meet, but failing to meet them should be a strong indicator of a bad commit.
+
 \subsubsection{no_short_message}
 \label{subs:no_short_message}
+The subject line should consist of more than 2 words, since no useful information can be conveyed with less words, for example messages like ``Bug'', ``Fix'' and ``Add comment'' are useless.
+Of course, there are situations where two words are appropriate, but we estimate that these are rare enough to be insignificant.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain no_long_message

@@
 \label{subs:no_long_message}
+The subject line should be limited to less than 10 words.
+This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words.
+The reasoning behind this criterion again is, that many words hint at more than one logical changeset in one commit.
+Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less time.
+If there is need for longer explanations, the body should be used.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain no_long_message

@@
 
-\subsubsection{subject_limit}
+\subsubsection{subject\_limit}
 \label{subs:subject_limit}
@@
 
-\subsubsection{capitalize_subject}
+\subsubsection{capitalize\_subject}
 \label{subs:capitalize_subject}
@@
 
-\subsubsection{no_period_subject}
+\subsubsection{no\_period\_subject}
 \label{subs:no_period_subject}
@@
 
-\subsubsection{imperative_subject}
+\subsubsection{imperative\_subject}
 \label{subs:imperative_subject}
@@
 
-\subsubsection{body_used}
+\subsubsection{body\_used}
 \label{subs:body_used}
@@
 
-\subsubsection{body_limit}
+\subsubsection{body\_limit}
 \label{subs:body_limit}
@@
 
-\subsubsection{empty_second_line}
+\subsubsection{empty\_second\_line}
 \label{subs:empty_second_line}
@@
 
-\subsubsection{no_short_message}
+\subsubsection{no\_short\_message}
 \label{subs:no_short_message}
@@
 
-\subsubsection{no_long_message}
+\subsubsection{no\_long\_message}
 \label{subs:no_long_message}
@@
 
-\subsubsection{no_bulk_change}
+It should be noted that the 10 words limit was arbitrarily chosen and might not yield ideal results.
+
+\subsubsection{no\_bulk\_change}
 \label{subs:no_bulk_change}
+Large changesets hint at a commit with more than one logical changeset.
+If 10 or more files are changed by a commit, chances are that that commit should have been separated multiple commits.
+Furthermore, even a commit with 10 or more changes only contains one logical changeset, this hints at bad software architecture, altough this should maybe not be reflected in the evaluation of commits.
 
-\subsubsection{no_vulgarity}
+One big problem with this criterion is, that there may very well be reasonable logical changes that have to touch 10 or more files, such as the refactoring of a classname.
+Also, as with the no_bulk_change-criterum in \ref{subs:no_long_message}, the chosen limit is only our best guess.
+
+\subsubsection{no\_vulgarity}
 \label{subs:no_vulgarity}
 
-\subsubsection{no_misspelling}
+\subsubsection{no\_misspelling}
 \label{subs:no_misspelling}
 
-\subsubsection{no_duplicate}
+\subsubsection{no\_duplicate}
 \label{subs:no_duplicate}

### 2015-08-24 presentations/paper/methodology.tex
Explain no_vulgarity

@@
 \label{subs:no_vulgarity}
+A commit message should obviously not contain any vulgarity for many reasons, but it should suffice to say that such things are unprofessional and will rarely make the commit any better.
+
+Checking for vulgarity is done with a perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words.
+The test for the criterion is passed if none of the words are found in the commit message.
+
+This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}
 

### 2015-08-24 presentations/paper/methodology.tex
Explain no_misspelling

@@
 \label{subs:no_misspelling}
+Of course, spelling is important. Correct or at least consistant spelling makes commit messages easier to read and scan, and makes them searchable.
+
+This criterion is hugely proplematic.
+In principle, spell checking is easily done with one of many libraries \footnote{We use http://search.cpan.org/~hank/Text-Aspell/Aspell.pm}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to less than 2.
+This will of course sometimes hide real errors.
+Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.
 

### 2015-08-24 presentations/paper/methodology.tex
Explain no_duplicate

@@
 \label{subs:no_duplicate}
+There should rarely be duplicate commit messages (except for automatic messages like merges).
+A duplicate commit message hints at a duplicate change to the code and makes reading git logs more difficult (for humans).
+
+If a commit has the same commit message as a commit that has been processed before, this test fails.
 

### 2015-08-24 presentations/paper/methodology.tex
Spell check data synthesis

@@
 
-% TODO: Put special focus on those Natural Language Processing
 % TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation
@@
 None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language.
-By keeping our criteria language-independent, they remain appliccable to all Git Repositories.
+By keeping our criteria language-independent, they remain appliccable to all Git repositories.
 
-In general, commit messages should consist of a subject line and a body \cite{OffGuide}.
+In general, commit messages should consist of a subject line and a body \footnote{See \cite{OffGuide} for an exhaustive explanation and an example}.
 \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post.
 Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message.
-Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}).
+Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}) that we found missing in the list.
 
@@
 %TODO: THIS IS A WILD FUCKING GUESS AND WE BETTER FINALLY USE WEKA AND GET SOME RESULTS
-
-% TODO: List all criteria with details
 
@@
 Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does.
-Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without much language-specific effort.
+Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without great language-specific effort.
 
@@
 This rule is only mentioned by \cite{CB}.
-It may not be as important as other rules, but fullfilling it requires little effort and makes reading the message a nicer.
+It may not be as important as other rules, but fulfilling it requires little effort and makes reading the message nicer.
 
@@
 It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{empty_second_line}) and omitting it helps with the 50 character limit.
-Again, the only explicit mention of this rule is \cite{CB}, although the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both seem to agree on this.
+Again, the only explicit mention of this rule is \cite{CB}, although the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both seem to adhere to it.
 
@@
 \label{subs:imperative_subject}
-The subject line should be written in imperative present, e.g.
+The subject line should be written in imperative present tense, e.g.
 ``Add a function that...'' (as mentioned in \cite{OffGuide}).
-There are a lot of opinions on this rule and many authors seem to prefer regular present tense (e.g.
+There are a lot of opinions on this rule and some authors seem to prefer regular present tense (e.g.
 ``Adds a function that...'') or past tense (e.g.
 ``Added a function that...''), which both have their own justification.
-The most important reason to use the imperative is consistency with git itself, which usually generates messages this way, the most prominent example being messages of automatic merges (e.g.
+In the authors opinion, the most important reason to use the imperative is consistency with git itself, which usually generates messages this way, the most prominent example being messages of automatic merges (e.g.
 ``Merge branch \'master\' of https://github.com/hartenfels/Commit-Rater'').
-\cite{CB} gives a very nice explanation on how to write messages in the imperative.
+\cite{CB} gives very nice instructions on how and why to write messages in the imperative.
 
@@
 message.
-For this purpose we use a perl module \footnote{http://search.cpan.org/dist/Lingua-EN-Tagger/Tagger.pm} and use it to get a list of the forms of the words in the subject line.
+For this purpose we use a Perl module \footnote{http://search.cpan.org/dist/Lingua-EN-Tagger/Tagger.pm} and use it to get a list of the forms of the words in the subject line.
 If the list contains a verb in base present form, the criterion is passed.
@@
 \label{subs:body_used}
-Additionally to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}).
+In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}).
 The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines.
@@
 This criterion only checks if there is a body.
+
+As the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} seem to disagree on this, we decided to make the useage of the body mandatory.
 
@@
 The subject line and the body should be separated by an empty line (\cite{TP}).
-This is how programs (including git itself) parsing the commit message which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial.
+This is how programs (including git itself) parsing the commit message know, which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial.
 If no body is used, the test on this criterion will be undefined.
@@
 This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words.
-The reasoning behind this criterion again is, that many words hint at more than one logical changeset in one commit.
-Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less time.
-If there is need for longer explanations, the body should be used.
+The reasoning behind this criterion is agein, that many words hint at more than one logical changeset in one commit.
+Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less effort.
+If there is need for longer explanations, they should be moved to the body.
 
@@
 Large changesets hint at a commit with more than one logical changeset.
-If 10 or more files are changed by a commit, chances are that that commit should have been separated multiple commits.
+If 10 or more files are changed by a commit, chances are that that commit should have been divided into multiple commits.
 Furthermore, even a commit with 10 or more changes only contains one logical changeset, this hints at bad software architecture, altough this should maybe not be reflected in the evaluation of commits.
@@
 \subsubsection{no\_vulgarity}
+\footnote{This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}}
 \label{subs:no_vulgarity}
@@
 
-Checking for vulgarity is done with a perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words.
+Checking for vulgarity is done with a Perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words.
 The test for the criterion is passed if none of the words are found in the commit message.
-
-This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}
 
@@
 \label{subs:no_misspelling}
-Of course, spelling is important. Correct or at least consistant spelling makes commit messages easier to read and scan, and makes them searchable.
+Of course, spelling is important. Correct or at least consistent spelling makes commit messages easier to read and scan, and makes them searchable.
 
-This criterion is hugely proplematic.
-In principle, spell checking is easily done with one of many libraries \footnote{We use http://search.cpan.org/~hank/Text-Aspell/Aspell.pm}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to less than 2.
+This criterion is hugely problematic.
+In principle, spell checking is easily done with one of many libraries \footnote{We use http://search.cpan.org/~hank/Text-Aspell/Aspell.pm}, but such libraries will report technical terms as errors and since we cannot manualy whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2.
 This will of course sometimes hide real errors.

### 2015-08-25 presentations/paper/methodology.tex
Escape some underscores in criterion names
Start description of Data Extraction

@@
 \subsection{Data Extraction}
+
+Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:TODO}.
+Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings accross them.
+
+\begin{description}
+    \item[101worker]\footnote{\url{https://github.com/101companies/101worker}}: A relatively small repository of barely over $2,000$ commits, done by the Software Languages Team of the University of Koblenz-Landau.
+Most of the commits in this repository do not adhere to the commit guidelines.
+    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit/}}: % TODO why?
+    \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60,000$ commits, partially adhering the commit guidelines.
+    \item[Linux Kernel]\footnote{\url{https://github.com/torvalds/linux}}: A massive repository of over half a million commits.
+Used for stress-testing our implementation and finding reasonable constraints on the amount of commits analyzed.
+Most commit messages adhere to the commit guidelines, for the sake of managing such a large volume of them.
+\end{description}
+
+To extract commit messages of a GitHub repository, the first and obvious attempt would be to use GitHub's API\footnote{\url{https://developer.github.com/v3/}}, which provides seemingly ideal REST resources for doing exactly that\footnote{\url{https://developer.github.com/v3/git/commits/\#get-a-commit}}.
+However, there is a heavy rate limit on calls to the API\footnote{\url{https://developer.github.com/v3/\#rate-limiting}}, which at the time of writing was at most 5000 requests per hour.
+Such a limit is only enough to analyze small repositories and is not suitable for a web application performing the rating of commits (see section\ref{sec:TODO}).
+
+Instead, the choice was made to simply clone the repositories and use \texttt{git log} to extract commit messages from them.
+While it requires time to clone the repository and disk space to store its data, it is much less limited and can be used for any Git repository, even outside of GitHub.
+
+During processing, each message is attributed to an author by their e-mail address and split into subject line and zero or more body lines following it.
+Additionally, a list of changed files is gathered from the log, for the use in data synthesis.
+
+\begin{table}
+    \begin{tabularx}{\textwidth}{|X|X|}\hline
+        \textbf{Repository} & \textbf{Time to Rate} \\\hline
+        101worker & ? \\\hline
+        BadgeKit & ? \\\hline
+        perl & ? \\\hline
+        Linux Kernel & ?\\\hline
+    \end{tabularx}
+    \caption{Time taken to rate commits of repositories}
+    \label{tab:time}
+\end{table}
+
+Since the entirety of repository commit messages can be listed by a single call to \texttt{git log} and commits can be extracted by a single regular expression, the commit rating process is fast and scales well.
+Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs.
 
@@
 One big problem with this criterion is, that there may very well be reasonable logical changes that have to touch 10 or more files, such as the refactoring of a classname.
-Also, as with the no_bulk_change-criterum in \ref{subs:no_long_message}, the chosen limit is only our best guess.
+Also, as with the no\_bulk\_change-criterum in \ref{subs:no_long_message}, the chosen limit is only our best guess.
 

### 2015-08-25 presentations/paper/methodology.tex
Finish data extraction aside from the time table

@@
 However, there is a heavy rate limit on calls to the API\footnote{\url{https://developer.github.com/v3/\#rate-limiting}}, which at the time of writing was at most 5000 requests per hour.
-Such a limit is only enough to analyze small repositories and is not suitable for a web application performing the rating of commits (see section\ref{sec:TODO}).
+Such a limit is only enough to analyze small repositories and is not suitable for a web application performing the rating of commits (see section \ref{sec:TODO}).
 
@@
 
-\begin{table}
-    \begin{tabularx}{\textwidth}{|X|X|}\hline
+\begin{table}[t]
+    \begin{tabularx}{\textwidth}{@{}|Y|Y|@{}}\hline
         \textbf{Repository} & \textbf{Time to Rate} \\\hline
-        101worker & ? \\\hline
-        BadgeKit & ? \\\hline
+        101worker & 10 seconds \\\hline
+        BadgeKit & 4 seconds \\\hline
         perl & ? \\\hline
@@
     \end{tabularx}
-    \caption{Time taken to rate commits of repositories}
+    \caption{Time taken to clone repositories and rate their commits}
     \label{tab:time}
@@
 Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs.
+The actual time taken to rate these repositories on the server the application is running on are found in table \ref{tab:time}.
+
+However, to keep the prototype website usable for multiple users at once, we decided to limit the number of commits analyzed to the latest $10,000$ commits.
+However, this practical limit may be increased by allowing more worker processes to rate repositories at once, reducing the chance of the entire commit rater being blocked for a long time by large repositories.
 
@@
 % \end{itemize}
-
-% TODO: Describe extraction process
-% TODO: Describe preprocessing and output
-% TODO: Mention commit-limit
-% TODO: Introduce example repos
 

### 2015-08-25 presentations/paper/methodology.tex
Fix Marco's English and links in Data Synthesis

@@
 
-Each commit of an author is testet against the criteria below.
+Each commit of an author is tested against the criteria below.
 While most tests either \emph{fail} or \emph{pass}, some criteria may not be appliccable in certain situations, e.g.
-a commit message's body cannot be tested for a per-line character limit, if there is no body at all.
+a commit message's body cannot be tested for a per-line character limit if there is no body at all.
 In those cases, the criterion-test will count as \emph{undefined}.
 
-The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion for each author. This triples will be used as a metric for the analysis in \ref{sub:analysis}.
+The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author. These triples will be used as a metric for the analysis in \ref{sub:analysis}.
 
-Almost all of the criteria below relate to the commit message.
-Only one of them states a very superficial rule about the changes in the commit.
+Almost all of the criteria below relate to the commit message, only one of them states a very superficial rule about the changes in the commit.
 None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language.
-By keeping our criteria language-independent, they remain appliccable to all Git repositories.
+By keeping our criteria language-independent, they remain applicable to all Git repositories.
 
@@
 Since there are no other sources to back our claim that failing to meet them makes a commit ``worse'', we will explain our reasoning behind the choices.
-Additionally, our criteria can be proven as valid, if there is a correlation between them and the criteria taken from credible sources.
+Additionally, our criteria can be validated if there is a correlation between them and the criteria taken from credible sources (see section \ref{sec:TODO}).
 %TODO: THIS IS A WILD FUCKING GUESS AND WE BETTER FINALLY USE WEKA AND GET SOME RESULTS
@@
 The first letter of the subject line should be capitalized.
-Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the english language start with a capital letter.
+Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the English language start with a capital letter.
 This rule is only mentioned by \cite{CB}.
-It may not be as important as other rules, but fulfilling it requires little effort and makes reading the message nicer.
 
@@
 It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{empty_second_line}) and omitting it helps with the 50 character limit.
-Again, the only explicit mention of this rule is \cite{CB}, although the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both seem to adhere to it.
+Again, the only explicit mention of this rule is \cite{CB}, however the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both implicitly adhere to it.
 
@@
 ``Add a function that...'' (as mentioned in \cite{OffGuide}).
-There are a lot of opinions on this rule and some authors seem to prefer regular present tense (e.g.
-``Adds a function that...'') or past tense (e.g.
-``Added a function that...''), which both have their own justification.
-In the authors opinion, the most important reason to use the imperative is consistency with git itself, which usually generates messages this way, the most prominent example being messages of automatic merges (e.g.
-``Merge branch \'master\' of https://github.com/hartenfels/Commit-Rater'').
-\cite{CB} gives very nice instructions on how and why to write messages in the imperative.
+This also adds consistency with Git itself, which generates messages this way, the most prominent example being messages of automatic merges (e.g.
+``Merge branch 'master' of https://github.com/hartenfels/Commit-Rater'').
+\cite{CB} gives very nice instructions on how and why to write messages in imperative form.
 
-This criterion requires natural language processing of the commit
-message.
-For this purpose we use a Perl module \footnote{http://search.cpan.org/dist/Lingua-EN-Tagger/Tagger.pm} and use it to get a list of the forms of the words in the subject line.
+This criterion requires natural language processing of the commit message.
+For this purpose we use a part-of-speech tagger\footnote{\url{https://metacpan.org/pod/Lingua::EN::Tagger}} and generate a list of the forms of the words in the subject line.
 If the list contains a verb in base present form, the criterion is passed.
-This is of course a very heuristic approach, but it successfully fails regular present tense or past tense subjet lines and furthermore ensures that there is a verb, so that nonsense messages like ``Some changes'' are failed too.
+This is of course a very heuristic approach, but it successfully fails regular present tense, past tense or subject lines with no verb at all.
 
@@
 
-As the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} seem to disagree on this, we decided to make the useage of the body mandatory.
+As the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} seem to disagree on this, we decided to make the usage of the body mandatory.
 
@@
 
+\par\bigskip
 The following six criteria have been chosen by the authors. Some state the obvious and most should be easy to meet, but failing to meet them should be a strong indicator of a bad commit.
@@
 
-One big problem with this criterion is, that there may very well be reasonable logical changes that have to touch 10 or more files, such as the refactoring of a classname.
-Also, as with the no\_bulk\_change-criterum in \ref{subs:no_long_message}, the chosen limit is only our best guess.
+One big problem with this criterion is, that there may very well be reasonable logical changes that have to touch 10 or more files, such as the refactoring of a class name.
+Also, as with the no\_long\_message-criterion in \ref{subs:no_long_message}, the chosen limit is only our best guess.
 
@@
 
-Checking for vulgarity is done with a Perl module \footnote{http://search.cpan.org/~abigail/Regexp-Common-2013031301/lib/Regexp/Common/profanity.pm} that contains a list of offensive words.
-The test for the criterion is passed if none of the words are found in the commit message.
+Checking for vulgarity is done with a Perl module that matches offensive words\footnote{\url{https://metacpan.org/pod/Regexp::Common::profanity}}.
+The test for the criterion passes if none of the words are found in the commit message.
 
@@
 This criterion is hugely problematic.
-In principle, spell checking is easily done with one of many libraries \footnote{We use http://search.cpan.org/~hank/Text-Aspell/Aspell.pm}, but such libraries will report technical terms as errors and since we cannot manualy whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2.
+In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manualy whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2.
 This will of course sometimes hide real errors.

### 2015-08-25 presentations/paper/threats.tex
Renamed threads to threats

\section{Threats to validity}
\label{sec:threats-to-validity}

There are external and internal threats to validity. See the softlang
papers and MSR papers for examples. See this resource~\cite{Michael04}
for an explanation. Be concise and systematic about answering
questions.

### 2015-08-25 presentations/paper/methodology.tex
Add \labels to all \sections
Fill in all times now that they're timed
Remove comma separators from numbers

@@
 \section{Methodology}
+\label{sec:methodology}
 % The methodology section must give a very clear account of what sort of
@@
 \begin{description}
-    \item[101worker]\footnote{\url{https://github.com/101companies/101worker}}: A relatively small repository of barely over $2,000$ commits, done by the Software Languages Team of the University of Koblenz-Landau.
+    \item[101worker]\footnote{\url{https://github.com/101companies/101worker}}: A relatively small repository of barely over $2000$ commits, done by the Software Languages Team of the University of Koblenz-Landau.
 Most of the commits in this repository do not adhere to the commit guidelines.
     \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit/}}: % TODO why?
-    \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60,000$ commits, partially adhering the commit guidelines.
+    \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60000$ commits, partially adhering the commit guidelines.
     \item[Linux Kernel]\footnote{\url{https://github.com/torvalds/linux}}: A massive repository of over half a million commits.
@@
         BadgeKit & 4 seconds \\\hline
-        perl & ? \\\hline
-        Linux Kernel & ?\\\hline
+        perl & 3 minutes \\\hline
+        Linux Kernel & 16 minutes\\\hline
     \end{tabularx}
@@
 
-However, to keep the prototype website usable for multiple users at once, we decided to limit the number of commits analyzed to the latest $10,000$ commits.
+However, to keep the prototype website usable for multiple users at once, we decided to limit the number of commits analyzed to the latest $10000$ commits.
 However, this practical limit may be increased by allowing more worker processes to rate repositories at once, reducing the chance of the entire commit rater being blocked for a long time by large repositories.

### 2015-08-25 presentations/paper/methodology.tex
Order and add commits to time table

@@
 \begin{table}[t]
-    \begin{tabularx}{\textwidth}{@{}|Y|Y|@{}}\hline
-        \textbf{Repository} & \textbf{Time to Rate} \\\hline
-        101worker & 10 seconds \\\hline
-        BadgeKit & 4 seconds \\\hline
-        perl & 3 minutes \\\hline
-        Linux Kernel & 16 minutes\\\hline
+    \begin{tabularx}{\textwidth}{@{}|Y|Y|Y|@{}}\hline
+        \textbf{Repository} & \textbf{Commits} & \textbf{Time to Rate} \\\hline
+        BadgeKit            & $723$            & $4$ seconds           \\\hline
+        101worker           & $2073$           & $10$ seconds          \\\hline
+        perl                & $60898$          & $3$ minutes           \\\hline
+        Linux Kernel        & $543964$         & $16$ minutes          \\\hline
     \end{tabularx}

### 2015-08-25 presentations/paper/research_question.tex
Add \labels to all \sections
Add related work section for referencing
Comment out instructions in Related Work

@@
 \section{Research question}
+\label{sec:research-question}
 
-State 1-5 research questions. One question could be enough. More is
-not better.
+\subsection{Related Work}
+\label{sec:related-work}
 
-For each question, make clear why this is an interesting question. For
-example, try to make clear why a scientist or a practician would
-benefit from knowing the answer to the question.
-
-Lay out some background for your research questions. That is, what
-body of related work may be worth mentioning and comparing to the
-research at hand. This may be related in terms of both relevant
-methodology or similar research questions.
-
-You should make sure to carry out a proper related work study. Use
-DBLP on the MSR conference for 2+
-years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
-welcome to search other conferences and journals. Coming to the
-conclusion that there is no related work is absolutely
-unacceptable. Again, you need to show related work awareness so that
-your research question is substantiated as being relevant and
-your methodology is deeply informed by existing publications.
-
-In many cases, you want to refine your research questions into actual
-hypotheses, i.e., something that is potentially falsifiable, subject
-to an appropriate approach towards measuring.
-
-It is also common to refine research questions. That is, one starts
-with a general (overall) research question and takes it appart into
-several questions that are concrete enough to be researched on and to
-be answered. In this manner, you may often suffice with one or two
-research questions which are however refined into perhaps
-several questions. Again, even without refinement, just one question may be
-Ok. This depends on the nature of the project and on the kind of question.
-
-Here are some recommended MSR papers by the Software Languages
-Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
-consult to see instances of the concepts discussed in this
-metamodel. These papers may or may not be in an optimal form to
-function as good advice. You are also advised to have a look at some
-MSR papers (from the MSR conference), but again, they may also
-slightly vary in terms of consistency of style. if you like to get
-general advice on scientific writing, then I recommend relevant
-textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
-writing and by having someone with experience to provide feedback.
-
-You should most definitely have a look at this excellent tutorial on
-empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
-relates. General ESE is quite often concerned with controlled
-experiments and other research methods that involve subjects, whereas
-MSR is more concerned with automated analysis, but the text is still
-very helpful in coming to grips with research methods in software
-engineering overall. Specifically, it helps with formulating research questions.
+%State 1-5 research questions. One question could be enough. More is
+%not better.
+%
+%For each question, make clear why this is an interesting question. For
+%example, try to make clear why a scientist or a practician would
+%benefit from knowing the answer to the question.
+%
+%Lay out some background for your research questions. That is, what
+%body of related work may be worth mentioning and comparing to the
+%research at hand. This may be related in terms of both relevant
+%methodology or similar research questions.
+%
+%You should make sure to carry out a proper related work study. Use
+%DBLP on the MSR conference for 2+
+%years.\footnote{\url{http://dblp.uni-trier.de/db/conf/msr/}} You are
+%welcome to search other conferences and journals. Coming to the
+%conclusion that there is no related work is absolutely
+%unacceptable. Again, you need to show related work awareness so that
+%your research question is substantiated as being relevant and
+%your methodology is deeply informed by existing publications.
+%
+%In many cases, you want to refine your research questions into actual
+%hypotheses, i.e., something that is potentially falsifiable, subject
+%to an appropriate approach towards measuring.
+%
+%It is also common to refine research questions. That is, one starts
+%with a general (overall) research question and takes it appart into
+%several questions that are concrete enough to be researched on and to
+%be answered. In this manner, you may often suffice with one or two
+%research questions which are however refined into perhaps
+%several questions. Again, even without refinement, just one question may be
+%Ok. This depends on the nature of the project and on the kind of question.
+%
+%Here are some recommended MSR papers by the Software Languages
+%Team~\cite{LaemmelLPV11,LaemmelP13,SchmorleizL15} which you could
+%consult to see instances of the concepts discussed in this
+%metamodel. These papers may or may not be in an optimal form to
+%function as good advice. You are also advised to have a look at some
+%MSR papers (from the MSR conference), but again, they may also
+%slightly vary in terms of consistency of style. if you like to get
+%general advice on scientific writing, then I recommend relevant
+%textbooks~\cite{Day98,Zobel09}. The best way to learn writing is by
+%writing and by having someone with experience to provide feedback.
+%
+%You should most definitely have a look at this excellent tutorial on
+%empirical software engineering (ESE)~\cite{Easterbrook07} to which MSR
+%relates. General ESE is quite often concerned with controlled
+%experiments and other research methods that involve subjects, whereas
+%MSR is more concerned with automated analysis, but the text is still
+%very helpful in coming to grips with research methods in software
+%engineering overall. Specifically, it helps with formulating research questions.

### 2015-08-25 analyzer.rb
Add rating and weighted rating to analyzer

@@ -3,4 +3,34 @@
 require 'json'
 require 'pp'
 
-pp JSON.parse(STDIN.read)
+def getAuthorPassRates(resultTriples)
+  passRates = Hash.new
+  resultTriples.each do |criterionName, resultTriple|
+    passRates[criterionName] = resultTriple['pass'].to_f \
+                             / (resultTriple['pass'] + resultTriple['fail'])
+  end
+  return passRates
+end
+
+def getAuthorPassRateWeights(resultTriples)
+  passRateWeights = Hash.new
+  resultTriples.each do |criterionName, resultTriple|
+    passRateWeights[criterionName] = (resultTriple['pass'].to_f + resultTriple['fail']) \
+                                   / (resultTriple['pass'] + resultTriple['fail'] + resultTriple['undef'])
+  end
+  return passRateWeights
+end
+
+authors = JSON.parse(STDIN.read)
+result = Hash.new
+authors.each do |authorEmail, resultTriples|
+  result[authorEmail] = Hash.new
+  result[authorEmail]['passRates'] = getAuthorPassRates(resultTriples)
+  result[authorEmail]['passRateWeights'] = getAuthorPassRateWeights(resultTriples)
+  result[authorEmail]['average'] = result[authorEmail]['passRates'].values.inject(:+) \
+                                 / result[authorEmail]['passRates'].length
+  result[authorEmail]['weightedAverage'] = result[authorEmail]['passRates'].values.zip(result[authorEmail]['passRateWeights'].values).map{|a,b| a * b}.inject(:+)\
+                                         / result[authorEmail]['passRateWeights'].values.inject(:+)
+end
+
+pp result

### 2015-08-25 presentations/paper/introduction.tex
Comment out introduction info
Add \labels to all \sections

@@
 \section{Introduction}
+\label{sec:introduction}
 
-Address these questions:
+%Address these questions:
+%
+%\begin{itemize}
+%
+%\item What is the context of this research?
+%
+%\item What is the overall challenge addressed by this research?
+%
+%\item What is the overall approach adopted by the research?
+%
+%\item Summarize results very briefly.
+%
+%\end{itemize}
 
-\begin{itemize}
+Revision control systems are a tool most software developers use every day, and of course performing commits is a frequent task in these systems.
+Each of these commits is associated with a message, so that the reasons for specific changes can be ascertained in the future\TODO{cite that this is true}.
+To achieve consistent and useful commit messages, best practices have been established\cite{OffGuide,CB,TP,SR}.
 
-\item What is the context of this research?
+While there has been research in the field of Mining Software Repositories about emotional content of commit messages (see section \ref{sec:related-work}), none of them have dealt with the actual quality of commits and their relation to the aformentioned best practices.
+In this paper, we present our approach to this topic.
 
-\item What is the overall challenge addressed by this research?
+We have built an application called ``Commit Rater''\footnote{\url{https://github.com/hartenfels/Commit-Rater}}, which extracts commit message data of any Git repository (see section \ref{sec:data-extraction}) and synthesizes the quantitative adherance to commit criteria (see section \ref{sec:data-synthesis}).
+For the sake of easy use and graphical visualization of the ratings, we have also built a web application\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}} around the tool, which, at the time of writing, is available for public use at \TODO{trollarena.de, really?}.
 
-\item What is the overall approach adopted by the research?
-
-\item Summarize results very briefly.
-
-\end{itemize}
+Finally, we also performed machine learning \TODO{actually do machine learning and finish this}

### 2015-08-25 presentations/paper/research_question.tex
Capitalize section titles

@@
-\section{Research question}
-\label{sec:research-question}
+\section{Research Questions}
+\label{sec:research-questions}
+
+Our research and development regarding the Commit Rater was lead by the goal of providing useful data to developers, such as ourselves, regarding their commits to help them learn and improve.
+The following two research questions (RQs) emerged from this objective.
+
+\subsection{RQ1: Can ``Good'' Commits be Recognized?}
+\label{sec:rq1}
+
+Telling ``good'' from ``bad'' commits would allow us to provide feedback to developers on how to improve and educate them about best practices.
+A set of criteria needs to be chosen and applied to the commit data, to allow for a quantifiable rating of each commit.
+
+\subsection{RQ2: Is Our Personally Chosen Criteria Valid?}
+\label{sec:rq2}
+
+Due to the lack of availability, the criteria necessary in RQ1 cannot all come from reputable sources and instead needs to be chosen through common sense.
+To validate these baseless rules, we want to find correlations between them and the official criteria.
+Through this, new criteria could be established and bad ones removed, allowing for a more accurate and detailed report to developers.
 

### 2015-08-25 analyzer.rb
Generate JSON as output

@@ -33,4 +33,4 @@ authors.each do |authorEmail, resultTriples|
                                          / result[authorEmail]['passRateWeights'].values.inject(:+)
 end
 
-pp result
+puts JSON.pretty_generate(result)

### 2015-08-25 analyzer.rb
Read input from samples directory
... Instead of stdin

@@ -21,16 +21,18 @@ def getAuthorPassRateWeights(resultTriples)
   return passRateWeights
 end
 
-authors = JSON.parse(STDIN.read)
 result = Hash.new
-authors.each do |authorEmail, resultTriples|
-  result[authorEmail] = Hash.new
-  result[authorEmail]['passRates'] = getAuthorPassRates(resultTriples)
-  result[authorEmail]['passRateWeights'] = getAuthorPassRateWeights(resultTriples)
-  result[authorEmail]['average'] = result[authorEmail]['passRates'].values.inject(:+) \
-                                 / result[authorEmail]['passRates'].length
-  result[authorEmail]['weightedAverage'] = result[authorEmail]['passRates'].values.zip(result[authorEmail]['passRateWeights'].values).map{|a,b| a * b}.inject(:+)\
-                                         / result[authorEmail]['passRateWeights'].values.inject(:+)
+Dir.glob('samples/*.json') do |sample|
+  authors = JSON.parse(File.read(sample))
+  authors.each do |authorEmail, resultTriples|
+    result[authorEmail] = Hash.new
+    result[authorEmail]['passRates'] = getAuthorPassRates(resultTriples)
+    result[authorEmail]['passRateWeights'] = getAuthorPassRateWeights(resultTriples)
+    result[authorEmail]['average'] = result[authorEmail]['passRates'].values.inject(:+) \
+                                   / result[authorEmail]['passRates'].length
+    result[authorEmail]['weightedAverage'] = result[authorEmail]['passRates'].values.zip(result[authorEmail]['passRateWeights'].values).map{|a,b| a * b}.inject(:+)\
+                                           / result[authorEmail]['passRateWeights'].values.inject(:+)
+  end
 end
 
 puts JSON.pretty_generate(result)

### 2015-08-25 analyzer.rb
Restructure the code a little

@@ -22,16 +22,24 @@ def getAuthorPassRateWeights(resultTriples)
 end
 
 result = Hash.new
+result['authors'] = Hash.new
 Dir.glob('samples/*.json') do |sample|
   authors = JSON.parse(File.read(sample))
   authors.each do |authorEmail, resultTriples|
-    result[authorEmail] = Hash.new
-    result[authorEmail]['passRates'] = getAuthorPassRates(resultTriples)
-    result[authorEmail]['passRateWeights'] = getAuthorPassRateWeights(resultTriples)
-    result[authorEmail]['average'] = result[authorEmail]['passRates'].values.inject(:+) \
-                                   / result[authorEmail]['passRates'].length
-    result[authorEmail]['weightedAverage'] = result[authorEmail]['passRates'].values.zip(result[authorEmail]['passRateWeights'].values).map{|a,b| a * b}.inject(:+)\
-                                           / result[authorEmail]['passRateWeights'].values.inject(:+)
+    result['authors'][authorEmail] = Hash.new
+
+    passRates = getAuthorPassRates(resultTriples)
+    result['authors'][authorEmail]['passRates'] = passRates
+
+    passRateWeights = getAuthorPassRateWeights(resultTriples)
+    result['authors'][authorEmail]['passRateWeights'] = passRateWeights
+
+    average = passRates.values.inject(:+) / passRates.length
+    result['authors'][authorEmail]['average'] = average
+
+    weightedAverage = passRates.values.zip(passRateWeights.values).map{|a,b| a * b}.inject(:+)\
+                    / passRateWeights.values.inject(:+)
+    result['authors'][authorEmail]['weightedAverage'] = weightedAverage
   end
 end
 

### 2015-08-25 analyzer.rb
Calculate averages of ratings and weighted ratings

@@ -43,4 +43,7 @@ Dir.glob('samples/*.json') do |sample|
   end
 end
 
+result['averageRating'] = result['authors'].values.inject(0){|acc, a| acc + a['average']} / result['authors'].length
+result['averageWeightedRating'] = result['authors'].values.inject(0){|acc, a| acc + a['weightedAverage']} / result['authors'].length
+
 puts JSON.pretty_generate(result)

### 2015-08-25 analyzer.rb
Calculate averages of criteria across all authors

@@ -21,6 +21,22 @@ def getAuthorPassRateWeights(resultTriples)
   return passRateWeights
 end
 
+criteria = [
+  "body_limit",
+  "body_used",
+  "capitalize_subject",
+  "empty_second_line",
+  "imperative_subject",
+  "no_bulk_change",
+  "no_duplicate",
+  "no_long_message",
+  "no_misspelling",
+  "no_period_subject",
+  "no_short_message",
+  "no_vulgarity",
+  "subject_limit"
+]
+
 result = Hash.new
 result['authors'] = Hash.new
 Dir.glob('samples/*.json') do |sample|
@@ -45,5 +61,11 @@ end
 
 result['averageRating'] = result['authors'].values.inject(0){|acc, a| acc + a['average']} / result['authors'].length
 result['averageWeightedRating'] = result['authors'].values.inject(0){|acc, a| acc + a['weightedAverage']} / result['authors'].length
+criteria.each do |criterion|
+
+  criterionAverage = result['authors'].values.inject(0){|acc, a| acc + a['passRates'][criterion]} \
+                   / result['authors'].length
+  result["average_#{criterion}"] = criterionAverage
+end
 
 puts JSON.pretty_generate(result)

### 2015-08-25 analyzer.rb
Limit analysis to authors with more 10 or more commits

@@ -21,6 +21,10 @@ def getAuthorPassRateWeights(resultTriples)
   return passRateWeights
 end
 
+def countCommits(resultTriples)
+  return resultTriples['subject_limit']['pass'] + resultTriples['subject_limit']['fail']
+end
+
 criteria = [
   "body_limit",
   "body_used",
@@ -42,6 +46,8 @@ result['authors'] = Hash.new
 Dir.glob('samples/*.json') do |sample|
   authors = JSON.parse(File.read(sample))
   authors.each do |authorEmail, resultTriples|
+    next if countCommits(resultTriples) < 10
+
     result['authors'][authorEmail] = Hash.new
 
     passRates = getAuthorPassRates(resultTriples)

### 2015-08-25 presentations/paper/conclusion.tex
Comment out instructions in Conclusion

@@
 \section{Conclusion}
+\label{sec:conclusion}
 
-This is essentially a redundant section. Try to summarize your
-research from a more informed point of view. (We assume that the
-reader has read the paper and is ready for some deeper conclusion.)
-You could very well add some perspectives for future work, without
-repeating smaller scale weakness of research, as they were already
-identified in the threats to validity section.
+%This is essentially a redundant section. Try to summarize your
+%research from a more informed point of view. (We assume that the
+%reader has read the paper and is ready for some deeper conclusion.)
+%You could very well add some perspectives for future work, without
+%repeating smaller scale weakness of research, as they were already
+%identified in the threats to validity section.

### 2015-08-25 presentations/paper/research_question.tex

@@
 \label{sec:related-work}
+
+The original inspiration for this work was the project \emph{Commit} \emph{Logs} \emph{From} \emph{Last} \emph{Night}\cite{LastNight}, especially its presentation resulting from it\footnote{\url{https://www.youtube.com/watch?v=V44kscaJe3M}}.
+Now defunct and only a static site, it used to regularly extract the latest commit messages from GitHub for vulgarity and published them on the website.
+As seen in the presentation, the vulgarity rate can be correlated with various software languages, time of day et cetera.
+However, in the end it is merely a fun website and does not give any useful information to developers.
+
+Similarly, the paper \emph{Sentiment} \emph{Analysis} \emph{of} \emph{Commit} \emph{Comments} \emph{in} \emph{GitHub:} \emph{An} \emph{Empirical} \emph{Study}\cite{Sentiment} from the MSR conference 2014 analyzes commit messages from Git repositories for their emotional impact and their correlation to software languages, time of day, geographical distribution and project approval.
+Again, however, the result is merely reflective not useful for developers in the process of developing something, which was our primary goal in this research.
 

### 2015-08-25 presentations/paper/methodology.tex
Add proper labels to subsections in Methodology
Remove stray slash in badgekit link

@@
 \subsection{Data Extraction}
+\label{sec:data-extraction}
 
@@
 Most of the commits in this repository do not adhere to the commit guidelines.
-    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit/}}: % TODO why?
+    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit}}: % TODO why?
     \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60000$ commits, partially adhering the commit guidelines.
@@
 \subsection{Data Synthesis}
+\label{sec:data-synthesis}
 
@@
 
-The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author. These triples will be used as a metric for the analysis in \ref{sub:analysis}.
+The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author. These triples will be used as a metric for the analysis in \ref{sec:data-analysis}.
 
@@
 \subsection{Data Analysis}
-\label{sub:analysis}
+\label{sec:data-analysis}
 

### 2015-08-26 presentations/paper/threats.tex
Add threats to validity

@@
-\section{Threats to validity}
+\section{Threats to Validity}
 \label{sec:threats-to-validity}
+%
+% There are external and internal threats to validity. See the softlang
+% papers and MSR papers for examples. See this resource~\cite{Michael04}
+% for an explanation. Be concise and systematic about answering
+% questions.
 
-There are external and internal threats to validity. See the softlang
-papers and MSR papers for examples. See this resource~\cite{Michael04}
-for an explanation. Be concise and systematic about answering
-questions.
+Based on our two research questions, our main conclusions are:
+\begin{itemize}
+  \item We can recognize a ``good'' commit by a high rating from the Commit Rater since the rating reflects how much the author adhered to certain criteria
+  \item Our personally chosen criteria are valid because they show statistical ralations to the criteria taken from official sources
+\end{itemize}
+
+\TODO{Revisit this section after drawing real conclusions}
+
+\subsection{Internal Threats to Validity}
+The relation between our criteria and the official criteria may not solely arise from the fact that both are valid criteria.
+There may be other causes, such as with the relation between the subject line character limit and the subject line word limit, which almost test the same thing.
+
+Furthermore, our tests for the criteria may be flawed.
+The prime example for such a test is the one for the spelling criterion.
+As already mentioned in \label{subs:no_misspelling}, spell-checking highly technical texts is very problematic and the results of this test may not be trustworthy.
+
+\subsection{External Threats to Validity}
+One basic assumption of our rater is, that the criteria from the official sources define ``good'' commits.
+This definition may be reasonable in most cases, but some developers might prefer different guidelines.
+Thus, our rater is only applicable to repositories where these guidelines are agreed upon.
+Other repositories meight receive significantly worse ratings although the authors may simply have adhered to different guidelines.
+
+Since there is no Ground Truth for if the rated commits are ``good'', we cannot evaluate if our rating method really recognizes such commits. Thus, this assumption may or may not be valid.

### 2015-08-26 analyzer.rb
%w

@@ -25,21 +25,7 @@ def countCommits(resultTriples)
   return resultTriples['subject_limit']['pass'] + resultTriples['subject_limit']['fail']
 end
 
-criteria = [
-  "body_limit",
-  "body_used",
-  "capitalize_subject",
-  "empty_second_line",
-  "imperative_subject",
-  "no_bulk_change",
-  "no_duplicate",
-  "no_long_message",
-  "no_misspelling",
-  "no_period_subject",
-  "no_short_message",
-  "no_vulgarity",
-  "subject_limit"
-]
+criteria = %w[body_limit body_used capitalize_subject empty_second_line imperative_subject no_bulk_change no_duplicate no_long_message no_misspelling no_period_subject no_short_message no_vulgarity subject_limit]
 
 result = Hash.new
 result['authors'] = Hash.new

### 2015-08-26 presentations/paper/threats.tex
Add labels to Treats to Validity

@@
 \subsection{Internal Threats to Validity}
+\label{sec:internal-threats}
+
 The relation between our criteria and the official criteria may not solely arise from the fact that both are valid criteria.
@@
 \subsection{External Threats to Validity}
+\label{sec:external-threats}
+
 One basic assumption of our rater is, that the criteria from the official sources define ``good'' commits.

### 2015-08-26 presentations/paper/conclusion.tex
Add Future Work section

@@
 \label{sec:conclusion}
+
+In this paper, we presented an application used to rate commit messages of Git repositories.
+Data extraction is done by cloning the repositories.
+Data synthesis is based on several separate criteria -- some official, some set by us personally.
+Finally, data analysis is done by comparing the various authors and repositories against each other\TODO{is that true?}.
+
+Both research questions were successfully answered: commits were recognized by the aformentioned criteria and by using machine learning, we successfully validated our personal criteria by correlating it with the criteria from reputable sources\TODO{maybe fix when it's done}.
+
+A prototype web application has been developed and is available for public testing, allowing us to use the resulting data for further research and development.
+
+\subsection{Future Work}
+\label{sec:future-work}
 

### 2015-08-26 presentations/paper/conclusion.tex
Add Future Work

@@
 
+The implementation and concepts presented in this paper are, due to the scope of the MSR course they were made in, largely prototypical and could be improved upon in several way.
+
+Firstly, the internal threats to validity presented in section \ref{sec:internal-threats} could largely be resolved by replacing the criteria used to synthesize data, or by improving their implementation to more accurately represent their abstract idea.
+
+Furthermore, a nicer interface could be provided to users of the web application.
+Comparisons could be drawn to other authors or repositories, better suggestions for improvement could be implemented and graphs could be used to visualize the results.
+
+Finally, language-specific criteria could be implemented as well.
+This would make the Commit Rater much more powerful, as it would be able to also analyze the contents of each commit.
+For example, it could recognize bad practices such as commented-out code or mixed whitespace and non-whitespace changes.
+
 %This is essentially a redundant section. Try to summarize your

### 2015-08-26 presentations/paper/threats.tex
Fix Marco's threats and remove double conclusion

@@
 
-Based on our two research questions, our main conclusions are:
-\begin{itemize}
-  \item We can recognize a ``good'' commit by a high rating from the Commit Rater since the rating reflects how much the author adhered to certain criteria
-  \item Our personally chosen criteria are valid because they show statistical ralations to the criteria taken from official sources
-\end{itemize}
-
-\TODO{Revisit this section after drawing real conclusions}
+\TODO{introduce without concluding}
 
@@
 The prime example for such a test is the one for the spelling criterion.
-As already mentioned in \label{subs:no_misspelling}, spell-checking highly technical texts is very problematic and the results of this test may not be trustworthy.
+As already mentioned in section \ref{subs:no_misspelling}, spell-checking highly technical texts is very problematic and the results of this test may not be trustworthy.
 

### 2015-08-26 presentations/paper/methodology.tex
Fix references in Methodology

@@
 
-Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:TODO}.
+Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:data-analysis}.
 Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings accross them.
@@
 However, there is a heavy rate limit on calls to the API\footnote{\url{https://developer.github.com/v3/\#rate-limiting}}, which at the time of writing was at most 5000 requests per hour.
-Such a limit is only enough to analyze small repositories and is not suitable for a web application performing the rating of commits (see section \ref{sec:TODO}).
+Such a limit is only enough to analyze small repositories and is not suitable for our web application performing the rating of commits.
 

### 2015-08-26 analyzer.rb
Avoid divsion by zero

@@ -6,8 +6,8 @@ require 'pp'
 def getAuthorPassRates(resultTriples)
   passRates = Hash.new
   resultTriples.each do |criterionName, resultTriple|
-    passRates[criterionName] = resultTriple['pass'].to_f \
-                             / (resultTriple['pass'] + resultTriple['fail'])
+    attempts = (resultTriple['pass'] + resultTriple['fail'])
+    passRates[criterionName] = attempts == 0 ? 0 : resultTriple['pass'].to_f / attempts
   end
   return passRates
 end
@@ -15,8 +15,8 @@ end
 def getAuthorPassRateWeights(resultTriples)
   passRateWeights = Hash.new
   resultTriples.each do |criterionName, resultTriple|
-    passRateWeights[criterionName] = (resultTriple['pass'].to_f + resultTriple['fail']) \
-                                   / (resultTriple['pass'] + resultTriple['fail'] + resultTriple['undef'])
+    total = resultTriple['pass'] + resultTriple['fail'] + resultTriple['undef']
+    passRateWeights[criterionName] = total == 0 ? 0 : (resultTriple['pass'].to_f + resultTriple['fail']) / total
   end
   return passRateWeights
 end
@@ -54,7 +54,7 @@ end
 result['averageRating'] = result['authors'].values.inject(0){|acc, a| acc + a['average']} / result['authors'].length
 result['averageWeightedRating'] = result['authors'].values.inject(0){|acc, a| acc + a['weightedAverage']} / result['authors'].length
 criteria.each do |criterion|
-
+  puts criterion
   criterionAverage = result['authors'].values.inject(0){|acc, a| acc + a['passRates'][criterion]} \
                    / result['authors'].length
   result["average_#{criterion}"] = criterionAverage

### 2015-08-26 analyzer.rb
Remove a debug message

@@ -54,7 +54,6 @@ end
 result['averageRating'] = result['authors'].values.inject(0){|acc, a| acc + a['average']} / result['authors'].length
 result['averageWeightedRating'] = result['authors'].values.inject(0){|acc, a| acc + a['weightedAverage']} / result['authors'].length
 criteria.each do |criterion|
-  puts criterion
   criterionAverage = result['authors'].values.inject(0){|acc, a| acc + a['passRates'][criterion]} \
                    / result['authors'].length
   result["average_#{criterion}"] = criterionAverage

### 2015-08-26 analysis/boxplots.rb
Move analyzer in separate repo and use a gem for boxplots

@@ -1,0 +1,49 @@
+#!/usr/bin/ruby
+
+require 'json'
+require 'pp'
+require 'statsample'
+
+# ss_analysis(Statsample::Graph::Boxplot) do
+#   a = [0.0, 0.1, 0.3, 0.5, 0.7, 0.99].to_numeric
+#   b = [0.0, 0.1, 0.125, 0.15, 0.1, 0.2, 0.99, 0.05].to_numeric
+#   c = [0.5, 0.51, 0.52, 0.53, 0.54].to_numeric
+#   d = [1, 1].to_numeric
+#
+#   boxplot(:vectors=>[d], :width=>600, :height=>600, :groups=>[0,1,2])
+# end
+# Statsample::Analysis.run
+
+
+criteria = %w[body_limit body_used capitalize_subject empty_second_line imperative_subject no_bulk_change no_duplicate no_long_message no_misspelling no_period_subject no_short_message no_vulgarity subject_limit]
+
+repos = Hash.new
+Dir.glob('../samples/*.json') do |sample|
+  repos[sample] = JSON.parse(File.read(sample))
+end
+
+criteria.each do |criterion|
+  puts "#{criterion}"
+  File.open("boxplots/#{criterion}.txt", 'w') do |f|
+    ss_analysis(Statsample::Graph::Boxplot) do
+      boxplot_arrays = Array.new
+      repos.each do |repo, authors|
+        repo_criterion_rates = Array.new
+        authors.each do |author, triples|
+          triple = triples[criterion]
+          total = triple['pass'] + triple['fail']
+          rate = total == 0 ? 1 : triple['pass'].to_f / total
+          repo_criterion_rates.push(rate)
+        end
+        boxplot_arrays.push(repo_criterion_rates.to_numeric)
+      end
+      pp boxplot_arrays
+      boxplot(:vectors=>boxplot_arrays, :width=>1024, :height=>768)
+    end
+    begin
+      Statsample::Analysis.run
+    rescue FloatDomainError
+      puts "Invalid data for boxplot"
+    end
+  end
+end

### 2015-08-26 boxplots.rb

@@ -1,23 +1,0 @@
-#!/usr/bin/ruby
-
-require 'json'
-require 'pp'
-
-criteria = %w[body_limit body_used capitalize_subject empty_second_line imperative_subject no_bulk_change no_duplicate no_long_message no_misspelling no_period_subject no_short_message no_vulgarity subject_limit]
-
-repos = Hash.new
-
-Dir.glob('samples/*.json') do |sample|
-  repos[sample] = JSON.parse(File.read(sample))
-end
-
-criteria.each do |criterion|
-  File.open("boxplots/#{criterion}.txt", 'w') {|f|
-    repos.each do |repo|
-      repo.each do |author|
-        
-      end
-    end
-    #f.puts existing
-  }
-end

### 2015-08-26 analysis/boxplots.rb
Render boxplots to svg

@@ -24,26 +24,23 @@ end
 
 criteria.each do |criterion|
   puts "#{criterion}"
-  File.open("boxplots/#{criterion}.txt", 'w') do |f|
-    ss_analysis(Statsample::Graph::Boxplot) do
-      boxplot_arrays = Array.new
-      repos.each do |repo, authors|
-        repo_criterion_rates = Array.new
-        authors.each do |author, triples|
-          triple = triples[criterion]
-          total = triple['pass'] + triple['fail']
-          rate = total == 0 ? 1 : triple['pass'].to_f / total
-          repo_criterion_rates.push(rate)
-        end
-        boxplot_arrays.push(repo_criterion_rates.to_numeric)
+  File.open("boxplots/#{criterion}.svg", 'w') do |f|
+    boxplot_arrays = Array.new
+    repos.each do |repo, authors|
+      repo_criterion_rates = Array.new
+      authors.each do |author, triples|
+        triple = triples[criterion]
+        total = triple['pass'] + triple['fail']
+        rate = total == 0 ? 1 : triple['pass'].to_f / total
+        repo_criterion_rates.push(rate)
       end
-      pp boxplot_arrays
-      boxplot(:vectors=>boxplot_arrays, :width=>1024, :height=>768)
+      boxplot_arrays.push(repo_criterion_rates.to_numeric)
     end
-    begin
-      Statsample::Analysis.run
-    rescue FloatDomainError
-      puts "Invalid data for boxplot"
-    end
+    f.puts Statsample::Graph::Boxplot.new(
+      :vectors => boxplot_arrays,
+      :width => 1024,
+      :height => 768,
+      :groups => (0..boxplot_arrays.length).to_a
+    ).to_svg
   end
 end

### 2015-08-26 analysis/boxplots.rb
Label boxplots after their repo

@@ -19,9 +19,10 @@ criteria = %w[body_limit body_used capitalize_subject empty_second_line imperati
 
 repos = Hash.new
 Dir.glob('../samples/*.json') do |sample|
-  repos[sample] = JSON.parse(File.read(sample))
+  repos[File.basename(sample, ".json")] = JSON.parse(File.read(sample))
 end
 
+boxcount = 1
 criteria.each do |criterion|
   puts "#{criterion}"
   File.open("boxplots/#{criterion}.svg", 'w') do |f|
@@ -36,11 +37,16 @@ criteria.each do |criterion|
       end
       boxplot_arrays.push(repo_criterion_rates.to_numeric)
     end
-    f.puts Statsample::Graph::Boxplot.new(
+    svg = Statsample::Graph::Boxplot.new(
       :vectors => boxplot_arrays,
       :width => 1024,
       :height => 768,
       :groups => (0..boxplot_arrays.length).to_a
     ).to_svg
+    repos.length.times do
+      svg.sub! ">Vector #{boxcount}<", ">#{repos.keys[boxcount % repos.length]}<"
+      boxcount += 1
+    end
+    f.puts svg
   end
 end

### 2015-08-26 analysis/boxplots.rb
Add number of authors to labels

@@ -44,7 +44,8 @@ criteria.each do |criterion|
       :groups => (0..boxplot_arrays.length).to_a
     ).to_svg
     repos.length.times do
-      svg.sub! ">Vector #{boxcount}<", ">#{repos.keys[boxcount % repos.length]}<"
+      repo_index = boxcount % repos.length
+      svg.sub! ">Vector #{boxcount}<", ">#{repos.keys[repo_index]} (#{repos.values[repo_index].length})<"
       boxcount += 1
     end
     f.puts svg

### 2015-08-26 presentations/paper/methodology.tex
Add analysis header in paper

@@
 \subsubsection{no\_vulgarity}
-\footnote{This criterion may or may not have been inspired by \url{http://www.commitlogsfromlastnight.com/}}
 \label{subs:no_vulgarity}
@@
 % TODO: Introduce the analysis tools we used
+
+Under the assumption that our synthesis results are metrics for the ``goodness'' of commits, we need to analyse them in order to aggregate a measure of ``goodness''.
+This analysis can be performed on three levels:
+
+\begin{itemize}
+  \item Per commit-level: Analysis could be done on the results of checking an individual commit against our criteria.
+  \item Per author-level: This level would aggregate the metrics for all commits of an author in a repository and create a rating of the authors commit behaviour.
+  \item Per repository-level: This level would aggregate the metrics of all authors in a repository and create a ranking for the whole team.
+\end{itemize}
+
+On each level, it is furthermore possible to analyse either the results of all criteria-checks or only the check/checks for one criterion. These six possibilities will be discussed below.
+
+% 1. Level: No use
+% 2. Level: Commit Rater Web
+% 3: Level: Boxplots

### 2015-08-26 presentations/paper/methodology.tex
ÂDescribe commit-level analysis

@@
 
+\subsubsection{Commit-level}
+\label{subs:Commit-level}
+Although looking at the results of a single commit might be interesting for debugging the criteria tests, there are not many options for analysis.
+The percentage of passed tests could serve as a rating for the commit, where 100\% means having passed all tests, but no further conclusions could be drawn from this level.
+Therefore, we did not concern ourselves with this level.
+
 % 1. Level: No use

### 2015-08-26 presentations/paper/methodology.tex
Describe author level analysis

@@
 
-% 1. Level: No use
-% 2. Level: Commit Rater Web
-% 3: Level: Boxplots
+\subsubsection{Author-level}
+\label{subs:Author-level}
+Analysis on this level evaluates the metrics-triples that were described in \ref{sec:data-synthesis}, where each author has a triple $(pass, fail, undef)$ for each criterion with $pass$ the number of commits that \emph{pass} the test for the criterion, $fail$ the number of commits that \emph{fail} the test for the criterion and $undef$ the number of commits that could not be tested against the criterion.
+
+The rate of how many of the commits pass a certain criterion may be interpreted as the rate with wich the author adheres the corresponding rule. The rate is calculated with the following formula:
+
+\begin{equation}
+  \label{eq:rate}
+  rate(triple) = \frac{triple_{pass}}{triple_{pass} + triple_{fail}}
+\end{equation}
+
+The important thing to note about this formula is, that it excludes $undef$.
+This means, that for instance authors who rarely use the body (see \ref{subs:body_used}) still have a useful refelction on how many of their commits with body were limited to 72 characters per line (\ref{subs:body_limit}).
+
+An example: A author with the triple $(190, 10, 0)$ for the subject limit (\ref{subs:subject_limit}) successfully limits his subject lines to 50 characters in 95\% of his commits.
+It could therefore furthermore be concluded that he is aware of the guideline, but has no tool in place that would prevent accidentally writing more than 50 characters.
+
+An average of these rates over all criteria can be seen as a general rating of an author's commit behaviour.
+Because of the $undef$s, two averages have to be considered: The standard average, which is just the average over the rates described above.
+And an average over the rates where each rate is weighted according to how many of all commits constituted to the rate.
+An author with a triple $(5, 5, 90)$ has a rate of 50\% according to equation \ref{eq:rate}, but should factor less into the average since only 10\% of all commits could be evaluated.
+Thus, the weighted average is calculated as follows:
+
+\begin{equation}
+  wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
+\end{equation}
+
+Where triples is the collection of triples of an author and a weight is calculated as follows:
+
+\begin{equation}
+  weight(triple) = \frac{triple_{pass} + triple_{fail}}{triple_{pass} + triple_{fail} + triple_{undef}}
+\end{equation}
+
+When working on this level, it turned out to be useful to exclude authors with few commits (maybe 10 or less), since the analysis results for these authors are not representative enough to infer any interpretations.
+
+This kind of analysis may be helpful for individual developers who seek to improve their Git etiquette.
+Because of this, we developed a web-frontend to our commit rater with integrated analysis.
+The source-code can be found on GitHub: \url{https://github.com/hartenfels/Commit-Rater-Web}
+
+\TODO{Insert Screenshot of Commit Rater Web, maybe describe a little bit more}
+
+\TODO{Level 3: Boxplots}

### 2015-08-26 presentations/paper/methodology.tex
Describe repository level analysis and add a threat to internal validity

@@
 \begin{equation}
+  \label{eq:weightedAverage}
   wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
@@
 
-\TODO{Level 3: Boxplots}
+\subsubsection{Repository-level}
+The analysis on this level is very similar to the analyis on the author-level.
+It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to reiceive an average for the whole repository.
+But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be infered from the results.
+
+Instead, on this level we opted to create boxplots with the rates for each criterion for all authors.
+Since each author has one triple per ciriterion, this means that for example a repository with 100 authors has 100 datapoints (rates) for a boxplot.
+The boxplots will be shown and discussed in \ref{sec:results}.

### 2015-08-26 presentations/paper/threats.tex
Describe repository level analysis and add a threat to internal validity

@@
 
+Generating boxplots on the author-level assumes equal significance for each author.
+This means, that an author with just 20 commits and a success-rate of 100\% for a criterion is counted equally as an author with 1000 commits and a rate of 100\%, although always adhering to a guideline for 1000 commits is a way greater feat as doing the same for 20 commits.
+Maybe this should somehow be reflected in the results, but we estimate that the changes to the result would be insignificant, as long as we exclude authors with very few commits (which we do).
+
 \subsection{External Threats to Validity}

### 2015-08-26 presentations/paper/introduction.tex
Finish Introduction

@@
 Revision control systems are a tool most software developers use every day, and of course performing commits is a frequent task in these systems.
-Each of these commits is associated with a message, so that the reasons for specific changes can be ascertained in the future\TODO{cite that this is true}.
+Each of these commits is associated with a message, so that the reasons for specific changes can be ascertained in the future\cite{CB}.
 To achieve consistent and useful commit messages, best practices have been established\cite{OffGuide,CB,TP,SR}.
@@
 We have built an application called ``Commit Rater''\footnote{\url{https://github.com/hartenfels/Commit-Rater}}, which extracts commit message data of any Git repository (see section \ref{sec:data-extraction}) and synthesizes the quantitative adherance to commit criteria (see section \ref{sec:data-synthesis}).
-For the sake of easy use and graphical visualization of the ratings, we have also built a web application\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}} around the tool, which, at the time of writing, is available for public use at \TODO{trollarena.de, really?}.
+For the sake of easy use and graphical visualization of the ratings, we have also built a web application\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}} around the tool, which, at the time of writing, is available for public use at \url{http://trollarena.de:8080/}.
 
-Finally, we also performed machine learning \TODO{actually do machine learning and finish this}
+Finally, we also performed machine learning using the Weka data mining software\cite{Weka} to perform association of our commit rating criteria for the sake of improving criteria selection in future versions of the Commit Rater.

### 2015-08-26 presentations/paper/methodology.tex

@@
 The boxplots will be shown and discussed in \ref{sec:results}.
+
+\subsubsection{Above repository-level}
+It may be of further interest to look at the averages of adherance to guidelines across multiple repos and thereby extrapolate some general statistics about ueage of the guidelines in the Git community.
+But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.

### 2015-08-26 analysis/boxplots.rb
Fix an error that assigned wrong labels in boxplots

@@ -24,7 +24,7 @@ end
 
 boxcount = 1
 criteria.each do |criterion|
-  puts "#{criterion}"
+  puts "----#{criterion}"
   File.open("boxplots/#{criterion}.svg", 'w') do |f|
     boxplot_arrays = Array.new
     repos.each do |repo, authors|
@@ -35,6 +35,8 @@ criteria.each do |criterion|
         rate = total == 0 ? 1 : triple['pass'].to_f / total
         repo_criterion_rates.push(rate)
       end
+      puts repo
+      puts repo_criterion_rates.inject{|sum, el| sum + el}.to_f / repo_criterion_rates.size
       boxplot_arrays.push(repo_criterion_rates.to_numeric)
     end
     svg = Statsample::Graph::Boxplot.new(
@@ -44,7 +46,7 @@ criteria.each do |criterion|
       :groups => (0..boxplot_arrays.length).to_a
     ).to_svg
     repos.length.times do
-      repo_index = boxcount % repos.length
+      repo_index = boxcount % repos.length - 1
       svg.sub! ">Vector #{boxcount}<", ">#{repos.keys[repo_index]} (#{repos.values[repo_index].length})<"
       boxcount += 1
     end

### 2015-08-26 analysis/boxplots.rb
Add manual median calculation to boxplot script for testing

@@ -4,16 +4,11 @@ require 'json'
 require 'pp'
 require 'statsample'
 
-# ss_analysis(Statsample::Graph::Boxplot) do
-#   a = [0.0, 0.1, 0.3, 0.5, 0.7, 0.99].to_numeric
-#   b = [0.0, 0.1, 0.125, 0.15, 0.1, 0.2, 0.99, 0.05].to_numeric
-#   c = [0.5, 0.51, 0.52, 0.53, 0.54].to_numeric
-#   d = [1, 1].to_numeric
-#
-#   boxplot(:vectors=>[d], :width=>600, :height=>600, :groups=>[0,1,2])
-# end
-# Statsample::Analysis.run
-
+def median(array)
+  sorted = array.sort
+  len = sorted.length
+  return (sorted[(len - 1) / 2] + sorted[len / 2]) / 2.0
+end
 
 criteria = %w[body_limit body_used capitalize_subject empty_second_line imperative_subject no_bulk_change no_duplicate no_long_message no_misspelling no_period_subject no_short_message no_vulgarity subject_limit]
 
@@ -36,7 +31,8 @@ criteria.each do |criterion|
         repo_criterion_rates.push(rate)
       end
       puts repo
-      puts repo_criterion_rates.inject{|sum, el| sum + el}.to_f / repo_criterion_rates.size
+      puts median(repo_criterion_rates)
+      #puts repo_criterion_rates.inject{|sum, el| sum + el}.to_f / repo_criterion_rates.size
       boxplot_arrays.push(repo_criterion_rates.to_numeric)
     end
     svg = Statsample::Graph::Boxplot.new(

### 2015-08-26 analysis/boxplots.rb
Remove authors with less than 10 commits from boxplots

@@ -25,6 +25,7 @@ criteria.each do |criterion|
     repos.each do |repo, authors|
       repo_criterion_rates = Array.new
       authors.each do |author, triples|
+        next if triples['subject_limit']['pass'] + triples['subject_limit']['fail'] < 10
         triple = triples[criterion]
         total = triple['pass'] + triple['fail']
         rate = total == 0 ? 1 : triple['pass'].to_f / total

### 2015-08-26 analysis/boxplots.rb
Update author count in boxplots for 10 commit limit

@@ -44,7 +44,8 @@ criteria.each do |criterion|
     ).to_svg
     repos.length.times do
       repo_index = boxcount % repos.length - 1
-      svg.sub! ">Vector #{boxcount}<", ">#{repos.keys[repo_index]} (#{repos.values[repo_index].length})<"
+      num_authors = repos.values[repo_index].select{|a, t| t['subject_limit']['pass'] + t['subject_limit']['fail'] < 10}.length
+      svg.sub! ">Vector #{boxcount}<", ">#{repos.keys[repo_index]} (#{num_authors})<"
       boxcount += 1
     end
     f.puts svg

### 2015-08-26 presentations/paper/methodology.tex
Remove lowbobiness
Make sum over elements readable
Add machine learning info in Commit-level section

@@
 \label{subs:Commit-level}
-Although looking at the results of a single commit might be interesting for debugging the criteria tests, there are not many options for analysis.
-The percentage of passed tests could serve as a rating for the commit, where 100\% means having passed all tests, but no further conclusions could be drawn from this level.
-Therefore, we did not concern ourselves with this level.
+Commit-level results, i.e.
+which criteria a single commit does or does not fulfill, is used for the machine learning aspect of this paper.
+Each commit represents a data set of boolean values.
+Due to the ways each criterion is formulated, true values are always good.
+For simplicity's sake, undefined values are considered bad and result in a false value.
+
+See section \ref{sec:results2} for a detailed explanation of our machine learning process.
 
@@
   \label{eq:weightedAverage}
-  wa(triples) = \frac{1}{|triples|} \times \sum{t \element triples} rate(t) \times weight(t)
+  wa(triples) = \frac{1}{|triples|} \times \sum\nolimits_{t \in triples} rate(t) \times weight(t)
 \end{equation}

### 2015-08-26 presentations/paper/methodology.tex

@@
 The subject line should have no trailing period.
-It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{empty_second_line}) and omitting it helps with the 50 character limit.
+It servers no purpose, since the body of a commit message should be separated by a blank line (see \ref{subs:empty_second_line}) and omitting it helps with the 50 character limit.
 Again, the only explicit mention of this rule is \cite{CB}, however the Git manual \cite{OffGuide} and Linus Torvalds \cite{SR} both implicitly adhere to it.

### 2015-08-26 presentations/paper/results.tex
Comment out instructions in Results

@@
 \section{Results}
+\label{sec:results}
 
-\noindent
-Summarize results in terms of tables, charts, and other kinds of
-figures.
+\TODO{Introduce}
 
-Explain and interpret the results.
+\subsection{Repo-level analysis}
+\label{sec:results1}
+This subsection focuses solely on repository-level analysis of our metrics, since comparison between individual commits and or individual authors would be tedious.
+Also, author-level analysis is open to everyone through the web interface.
 
-Get back to the research question and make sure that it is explicitly answered.
+Figure \ref{fig:bp_subject_limit} shows the repository-level boxplots for the subject limit criterion for all 4 repositories.
+The number behind the labels denotes the number of authors that were evaluated in the graph.
+Surprisingly, the linux kernel has the worst results, followed by the badgekit and the perl5 and then the 101worker with the best results.
+
+On the other hand, \ref{fig:bp_imperative_subject} shows that authors of the linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do.
+Additionally, \ref{fig:bp_no_short_message} shows that linux kernel authors do not write short commit messages, while the authors of the 101worker do.
+This observation coincides with our estimations for the worker, since that criterion was inspired by a prevalence for 1-word commits in that repo.
+
+One significant difference between the two small repos (badgekit and 101worker) and the big repos (perl and linux kernel) stands out in \ref{fig:bp_body_used}.
+The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the badgekit.
+
+Finally, \ref{fig:bp_no_period_subject} shows that generally none of the repositories put a period at the end of the subject line.
+This means, that this criterion could be disregarded, if similar behaviour can be observed in other repositories.
+
+The boxplots for the other criteria are available in our Git and were not included here in order to save space.
+
+Based on these results, it is surprisingly hard to draw justified conclusions and answer our first research question positively.
+While the linux kernel is certainly the most high-profile Git repository in our selection and one might expect a high commit quality from the contributing authors, considering the median it is outperformed in four of thirteen criteria by the other repositories.
+
+Since we lack further objective judgements on the ``goodnes'' of commits or repositories, we can not evaluate if meeting our criteria means having ``good'' commits.
+
+On the other hand, it can be argued that meeting the seven official criteria means having good commits \emph{per definition}, since they have been taken from the official guidelines, and are therefore themselves the missing objective judgement.
+
+In summary, while the analysis results are certainly interesting to look at, they offer no unambiguous answer to our first research question.
+
+\subsection{Machine Learning}
+\label{sec:results2}
+
+%\noindent
+%Summarize results in terms of tables, charts, and other kinds of
+%figures.
+%
+%Explain and interpret the results.
+%
+%Get back to the research question and make sure that it is explicitly answered.

### 2015-08-26 presentations/paper/img/svgToPdf.sh
Add boxplot images files

@@ -1,0 +1,9 @@
+#!/bin/bash
+
+(
+  echo imperative_subject.svg --export-pdf=imperative_subject.pdf;
+  echo no_period_subject.svg --export-pdf=no_period_subject.pdf;
+  echo no_short_message.svg --export-pdf=no_short_message.pdf;
+  echo subject_limit.svg --export-pdf=subject_limit.pdf;
+  echo body_used.svg --export-pdf=body_used.pdf;
+) | DISPLAY= inkscape --shell

### 2015-08-26 presentations/paper/results.tex
Add boxplot images files
Add sad weka results to Results section

@@
 
+As an attempt to validate our own criteria, we performed association analysis using the data mining and machine learning software Weka\cite{Weka}.
+The data set is a commit-level view (see section \ref{subs:Commit-level}) of all rated commits of our sample repositories (see section \ref{sec:data-extraction}).
+The raw ARFF\footnote{\url{http://www.cs.waikato.ac.nz/ml/weka/arff.html}} data can be found at \url{https://github.com/hartenfels/Commit-Rater/tree/master/samples}.
+
+\begin{table}[t]
+    \begin{tabularx}{\textwidth}{|c|X|}\hline
+        \textbf{Expected Correlation} & \textbf{Reason} \\\hline
+        empty\_second\_line $\Rightarrow$ body\_used & If there is more than one line, the body was used, per our definition.
+Note that a nonexistent empty line does not count as empty, see section \ref{subs:empty_second_line}.\\\hline
+        short\_message $\Leftrightarrow$ $\neg$ long\_message & Obviously, a message cannot have 2 or less and 10 or more words at the same time. \\\hline
+        body\_limit $\Rightarrow$ body\_used & Only if the body exists will the body limit criterion be defined. See section \ref{subs:body_limit}. \\\hline
+        short\_message $\Rightarrow$ subject\_limit & If two or less words are used in the subject line, it is unlikely that it will be longer than 50 characters. \\\hline
+        long\_message $\Rightarrow$ $\neg$ subject\_limit & As the inverse of the above, it is unlikely that 10 or more words can be crammed in a 50 character subject line. \\\hline
+    \end{tabularx}
+    \caption{Expected correlations, ordered by obviousness}
+    \label{tab:expect}
+\end{table}
+
+To find an appropriate algorithm, we chose a set of obvious correlations, listed in table \ref{tab:expect}.
+An algorithm detecting these correctly should also be suitable to detect other non-obvious correlations in our data set.
+
+While almost all attributers built into Weka provided useful output regarding above criteria, we eventuall chose to use the ``Apriori'' attributer\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified.
+No special parameters are used to call the attributer, only the number of output results has been increased from 10 to 300\footnote{The code to call the attributer can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/runweka\#L9}}.
+The results have been ordered by confidence of their correctness and can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/samples/sample\_repos.arff.weka}.
+
+However, only one of our expected criteria can be found in the result set.
+Two thirds of all results also relate to the no\_misspelling criterion, which, as predicted in section \ref{subs:no_misspelling}, has proven problematic.
+The same occurs with the no\_vulgarity predictate, which is simply too often true and therefore not a useful criterion.
+Additionally, some criteria, such as no\_bulk\_changes, cannot be correlated with any other criteria, as they have no connection with any of them.
+
+Due to this sobering result, the research question ``Is Our Personally Chosen Criteria Valid?'' from section \ref{sec:rq2} can clearly be answered by ``no''.
+The implementation of spell checking does not provide correct results and the vulgarity checking is not actually useful, as there aren't enough commits that fail the check.
+On the upside, the process of performing this attribution has revealed these issues very clearly, allowing us to correct them and test our corrections by another round of attributions.
+
+Additionally, this machine learning process is not useful for all criteria, as not all of them have a relation to at least one other criterion.
+Therefore, either more criteria is needed to fill these gaps, or a different way of validiation needs to be used.
+
 %\noindent

### 2015-08-26 presentations/paper/conclusion.tex
Add sad weka results to Conclusion

@@
 
-Both research questions were successfully answered: commits were recognized by the aformentioned criteria and by using machine learning, we successfully validated our personal criteria by correlating it with the criteria from reputable sources\TODO{maybe fix when it's done}.
+Only one of our research question has been answered positively: ``good'' commits were recognized by the aformentioned criteria.
+However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.
 

### 2015-08-26 presentations/paper/results.tex
Include graphics in paper

--- 2015-08-26 presentations/paper/results.tex
@@
 \label{sec:results1}
+
+\TODO{Graphics placement}
+
 This subsection focuses solely on repository-level analysis of our metrics, since comparison between individual commits and or individual authors would be tedious.
 Also, author-level analysis is open to everyone through the web interface.
+
+\begin{figure}[p]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/subject_limit.pdf}
+    \caption{Subject Limit Boxplot}
+    \label{fig:bp_subject_limit}
+\end{figure}
 
@@
 
-On the other hand, \ref{fig:bp_imperative_subject} shows that authors of the linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do.
-Additionally, \ref{fig:bp_no_short_message} shows that linux kernel authors do not write short commit messages, while the authors of the 101worker do.
+\begin{figure}[p]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/imperative_subject.pdf}
+    \caption{Imperative Subject Boxplot}
+    \label{fig:bp_imperative_subject}
+\end{figure}
+
+\begin{figure}[p]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/no_short_message.pdf}
+    \caption{No Short Message Boxplot}
+    \label{fig:bp_no_short_message}
+\end{figure}
+
+On the other hand, figure \ref{fig:bp_imperative_subject} shows that authors of the linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do.
+Additionally, figure \ref{fig:bp_no_short_message} shows that linux kernel authors do not write short commit messages, while the authors of the 101worker do.
 This observation coincides with our estimations for the worker, since that criterion was inspired by a prevalence for 1-word commits in that repo.
 
-One significant difference between the two small repos (badgekit and 101worker) and the big repos (perl and linux kernel) stands out in \ref{fig:bp_body_used}.
+\begin{figure}[p]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/body_used.pdf}
+    \caption{Body Used Boxplot}
+    \label{fig:bp_body_used}
+\end{figure}
+
+One significant difference between the two small repos (badgekit and 101worker) and the big repos (perl and linux kernel) stands out in figure \ref{fig:bp_body_used}.
 The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the badgekit.
 
-Finally, \ref{fig:bp_no_period_subject} shows that generally none of the repositories put a period at the end of the subject line.
+\begin{figure}[p]
+    \centering
+    \includegraphics[width=0.8\textwidth]{img/no_period_subject.pdf}
+    \caption{No Period Subject Boxplot}
+    \label{fig:bp_no_period_subject}
+\end{figure}
+
+Finally, figure \ref{fig:bp_no_period_subject} shows that generally none of the repositories put a period at the end of the subject line.
 This means, that this criterion could be disregarded, if similar behaviour can be observed in other repositories.

### 2015-08-26 presentations/paper/methodology.tex
Reference machine learning in Methodology properly
Fix Marco's style in Methodology

@@
 Each commit of an author is tested against the criteria below.
-While most tests either \emph{fail} or \emph{pass}, some criteria may not be appliccable in certain situations, e.g.
+While most tests either \emph{fail} or \emph{pass}, some criteria may not be applicable in certain situations, e.g.
 a commit message's body cannot be tested for a per-line character limit if there is no body at all.
-In those cases, the criterion-test will count as \emph{undefined}.
+In those cases, the criterion test will count as \emph{undefined}.
 
@@
 Since there are no other sources to back our claim that failing to meet them makes a commit ``worse'', we will explain our reasoning behind the choices.
-Additionally, our criteria can be validated if there is a correlation between them and the criteria taken from credible sources (see section \ref{sec:TODO}).
-%TODO: THIS IS A WILD FUCKING GUESS AND WE BETTER FINALLY USE WEKA AND GET SOME RESULTS
+Additionally, we will attempt to validate our criteria by correlating it with the official criteria as seen in section \ref{sec:results2}.
 
@@
 \label{subs:body_used}
-In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does (\cite{OffGuide}).
+In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does\cite{OffGuide}.
 The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines.
@@
 \label{subs:empty_second_line}
-The subject line and the body should be separated by an empty line (\cite{TP}).
+The subject line and the body should be separated by an empty line\cite{TP}.
 This is how programs (including git itself) parsing the commit message know, which part is the subject line and which the body, so if a body is used, meeting this criterion is crucial.
@@
 
-On each level, it is furthermore possible to analyse either the results of all criteria-checks or only the check/checks for one criterion. These six possibilities will be discussed below.
+On each level, it is furthermore possible to analyse either the results of all criteria checks or only the check/checks for one criterion. These six possibilities will be discussed below.
 

### 2015-08-26 presentations/paper/methodology.tex
Describe badgekit

--- 2015-08-26 presentations/paper/methodology.tex
@@
 Most of the commits in this repository do not adhere to the commit guidelines.
-    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit}}: % TODO why?
+    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit}}: The smallest repository in our selection, it was chosen because it is a Mozilla project and we therefore expect that most commits adhere at least partially to the commit guidelines.
     \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60000$ commits, partially adhering the commit guidelines.

### 2015-08-26 presentations/paper/methodology.tex
Transition smoothly from data processing to data synthesis
Remove some already finished todos
Fix spelling, mostly Marco's

--- 2015-08-26 presentations/paper/methodology.tex
@@
 Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:data-analysis}.
-Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings accross them.
+Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings across them.
 
@@
 Almost all of the criteria below relate to the commit message, only one of them states a very superficial rule about the changes in the commit.
-None of them process the code itself, neither inside the changes nor in the the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language.
+None of them process the code itself, neither inside the changes nor in the code-base before or after applying the commit, as such criteria would require very language-specific knowledge that would have to be manually implemented for each desired language.
 By keeping our criteria language-independent, they remain applicable to all Git repositories.
@@
 Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message.
-Omitting this rule, we still infered one additional criterium (\ref{subs:body_used}) that we found missing in the list.
+Omitting this rule, we still inferred one additional criterion (\ref{subs:body_used}) that we found missing in the list.
 
@@
 Additionally, large subject lines might hint at having done more than one thing in a commit, since the author needs more space to explain what the commit does.
-Logically separating changesets is another rule from \cite{OffGuide}, which of course cannot be evaluated without great language-specific effort.
+Logically separating change sets is another rule from \cite{OffGuide}, which of course cannot be evaluated without great language-specific effort.
 
@@
 This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words.
-The reasoning behind this criterion is agein, that many words hint at more than one logical changeset in one commit.
+The reasoning behind this criterion is again, that many words hint at more than one logical change set in one commit.
 Also, concision should help making a message more easily understandable and scanning a log for a particular commit takes less effort.
@@
 \label{subs:no_bulk_change}
-Large changesets hint at a commit with more than one logical changeset.
+Large change sets hint at a commit with more than one logical change set.
 If 10 or more files are changed by a commit, chances are that that commit should have been divided into multiple commits.
-Furthermore, even a commit with 10 or more changes only contains one logical changeset, this hints at bad software architecture, altough this should maybe not be reflected in the evaluation of commits.
+Furthermore, even a commit with 10 or more changes only contains one logical change set, this hints at bad software architecture, although this should maybe not be reflected in the evaluation of commits.
 
@@
 This criterion is hugely problematic.
-In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manualy whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2.
+In principle, spell checking is easily done with one of many libraries \footnote{We use GNU Aspell, via \url{https://metacpan.org/pod/Text::Aspell}}, but such libraries will report technical terms as errors and since we cannot manually whitelist all of those, we need to allow a certain number of ``errors'' per message, which we have set to 2.
 This will of course sometimes hide real errors.
@@
 
-The rate of how many of the commits pass a certain criterion may be interpreted as the rate with wich the author adheres the corresponding rule. The rate is calculated with the following formula:
+The rate of how many of the commits pass a certain criterion may be interpreted as the rate with which the author adheres the corresponding rule. The rate is calculated with the following formula:
 
@@
 The important thing to note about this formula is, that it excludes $undef$.
-This means, that for instance authors who rarely use the body (see \ref{subs:body_used}) still have a useful refelction on how many of their commits with body were limited to 72 characters per line (\ref{subs:body_limit}).
+This means, that for instance authors who rarely use the body (see \ref{subs:body_used}) still have a useful reflection on how many of their commits with body were limited to 72 characters per line (\ref{subs:body_limit}).
 
@@
 \subsubsection{Repository-level}
-The analysis on this level is very similar to the analyis on the author-level.
-It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to reiceive an average for the whole repository.
-But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be infered from the results.
+The analysis on this level is very similar to the analysis on the author-level.
+It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to receive an average for the whole repository.
+But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be inferred from the results.
 
 Instead, on this level we opted to create boxplots with the rates for each criterion for all authors.
-Since each author has one triple per ciriterion, this means that for example a repository with 100 authors has 100 datapoints (rates) for a boxplot.
+Since each author has one triple per criterion, this means that for example a repository with 100 authors has 100 data points (rates) for a boxplot.
 The boxplots will be shown and discussed in \ref{sec:results}.
@@
 \subsubsection{Above repository-level}
-It may be of further interest to look at the averages of adherance to guidelines across multiple repos and thereby extrapolate some general statistics about ueage of the guidelines in the Git community.
+It may be of further interest to look at the averages of adherence to guidelines across multiple repos and thereby extrapolate some general statistics about usage of the guidelines in the Git community.
 But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.

### 2015-08-26 presentations/paper/results.tex

@@
 The number behind the labels denotes the number of authors that were evaluated in the graph.
-Surprisingly, the linux kernel has the worst results, followed by the badgekit and the perl5 and then the 101worker with the best results.
+Surprisingly, the Linux kernel has the worst results, followed by the BadgeKit, perl and then the 101worker with the best results.
 
@@
 
-On the other hand, figure \ref{fig:bp_imperative_subject} shows that authors of the linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do.
+On the other hand, figure \ref{fig:bp_imperative_subject} shows that authors of the Linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do.
 Additionally, figure \ref{fig:bp_no_short_message} shows that linux kernel authors do not write short commit messages, while the authors of the 101worker do.
@@
 
-One significant difference between the two small repos (badgekit and 101worker) and the big repos (perl and linux kernel) stands out in figure \ref{fig:bp_body_used}.
-The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the badgekit.
+One significant difference between the two small repos (BadgeKit and 101worker) and the big repos (perl and Linux kernel) stands out in figure \ref{fig:bp_body_used}.
+The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the BadgeKit.
 
@@
 Based on these results, it is surprisingly hard to draw justified conclusions and answer our first research question positively.
-While the linux kernel is certainly the most high-profile Git repository in our selection and one might expect a high commit quality from the contributing authors, considering the median it is outperformed in four of thirteen criteria by the other repositories.
+While the Linux kernel is certainly the most high-profile Git repository in our selection and one might expect a high commit quality from the contributing authors, considering the median it is outperformed in four of thirteen criteria by the other repositories.
 
-Since we lack further objective judgements on the ``goodnes'' of commits or repositories, we can not evaluate if meeting our criteria means having ``good'' commits.
+Since we lack further objective judgements on the ``goodness'' of commits or repositories, we can not evaluate if meeting our criteria means having ``good'' commits.
 
@@
 
-While almost all attributers built into Weka provided useful output regarding above criteria, we eventuall chose to use the ``Apriori'' attributer\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified.
+While almost all associator built into Weka provided useful output regarding above criteria, we eventually chose to use the ``Apriori'' attributer\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified.
 No special parameters are used to call the attributer, only the number of output results has been increased from 10 to 300\footnote{The code to call the attributer can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/runweka\#L9}}.
@@
 Two thirds of all results also relate to the no\_misspelling criterion, which, as predicted in section \ref{subs:no_misspelling}, has proven problematic.
-The same occurs with the no\_vulgarity predictate, which is simply too often true and therefore not a useful criterion.
+The same occurs with the no\_vulgarity predicate, which is simply too often true and therefore not a useful criterion.
 Additionally, some criteria, such as no\_bulk\_changes, cannot be correlated with any other criteria, as they have no connection with any of them.
@@
 Additionally, this machine learning process is not useful for all criteria, as not all of them have a relation to at least one other criterion.
-Therefore, either more criteria is needed to fill these gaps, or a different way of validiation needs to be used.
+Therefore, either more criteria is needed to fill these gaps, or a different way of validation needs to be used.
 

### 2015-08-26 presentations/paper/threats.tex
Add RQ1 results/answer and one more external threat

@@
 Thus, our rater is only applicable to repositories where these guidelines are agreed upon.
-Other repositories meight receive significantly worse ratings although the authors may simply have adhered to different guidelines.
+Other repositories might receive significantly worse ratings although the authors may simply have adhered to different guidelines.
 
 Since there is no Ground Truth for if the rated commits are ``good'', we cannot evaluate if our rating method really recognizes such commits. Thus, this assumption may or may not be valid.
+
+While our rater mostly operates on the metadata of a commit, there are many more factors that constitute to a good commit that have not been considered, since they for example would require interpreting/compiling or at least parsing the code.
+Therefore, our criteria are incomplete.

### 2015-08-26 presentations/paper/methodology.tex
Restate a hint to the web frontend
... Since at this point it has already been introduced.

@@
 % The typical MSR paper picks either metrics or machine learning or IR.
-
-% TODO: Maybe mention, that our synthesis contains actions that may have belonged into extraction, but we found the terms more fitting to our implementation
 
@@
 
-% TODO: Decide on analysis tools
-% * Weka
-% * Some Boxplots including averages for all metrics
-% TODO: Introduce the analysis tools we used
-
 Under the assumption that our synthesis results are metrics for the ``goodness'' of commits, we need to analyse them in order to aggregate a measure of ``goodness''.
@@
 
-This kind of analysis may be helpful for individual developers who seek to improve their Git etiquette.
-Because of this, we developed a web-frontend to our commit rater with integrated analysis.
-The source-code can be found on GitHub: \url{https://github.com/hartenfels/Commit-Rater-Web}
-
-\TODO{Insert Screenshot of Commit Rater Web, maybe describe a little bit more}
+This kind of analysis may be helpful for individual developers who seek to improve their Git etiquette. Our aforementioned Web-Frontend exposes this kind of functionality in an easily accessible way.
 

### 2015-08-26 presentations/paper/conclusion.tex
Fix spelling, mostly Marco's
Add a todo
Restate summary so that it only mentions repo-level analysis

@@
 \label{sec:conclusion}
+
+\TODO{Etwas abschwächen}
 
@@
 Data synthesis is based on several separate criteria -- some official, some set by us personally.
-Finally, data analysis is done by comparing the various authors and repositories against each other\TODO{is that true?}.
+Finally, data analysis is done by comparing a set of repositories against each other.
 
-Only one of our research question has been answered positively: ``good'' commits were recognized by the aformentioned criteria.
+Only one of our research question has been answered positively: ``good'' commits were recognized by the aforementioned criteria.
 However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.

### 2015-08-26 presentations/paper/conclusion.tex
Make conclusion a little weaker

@@
 
-Only one of our research question has been answered positively: ``good'' commits were recognized by the aforementioned criteria.
-However, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.
+Only one of our research question has been answered vaguely positively: ``good'' commits were recognized by the aforementioned criteria.
+However, we were unable to draw further conclusions from analysis on higher levels.
+Additionally, not all of our criteria could be validated by using machine learning attribution, some simply due to the criteria itself not being good, some due to the approach of machine learning not being applicable to the data set.
 

### 2015-08-26 presentations/paper/details.tex
Write something in the details section

@@
 \section{Details}
-\label{S:details}
+\label{sec:details}
 
-Any sort of interesting details such as source code, extra data (extra
-to the key results), extra procedural details supporting
-reproducibility can be listed here.
+The source code for the Commit Rater can be found on GitHub\footnote{\url{https://github.com/hartenfels/Commit-Rater}}.
+The repository includes all of the boxplots (\texttt{analysis/boxplots}), their raw data source data (\texttt{samples}) and their generation script (\texttt{analysis/boxplots.rb).
+
+\TODO{It also includes the files used for the machine learning...}
+
+Finally, the web frontend runs on a private server\footnote{\url{http://trollarena.de:8080/}}, it may go offline in the not too distant future.
+Its source code is also available on GitHub\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}}.

### 2015-08-26 presentations/paper/results.tex
Introduce results
Rename attributor to associator

@@
 
-\TODO{Introduce}
+The following section describes the results of both our repo-level analysis and our machine learning analysis. Selected results are presented and interpreted.
 
@@
 
-While almost all associator built into Weka provided useful output regarding above criteria, we eventually chose to use the ``Apriori'' attributer\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified.
+While almost all associator built into Weka provided useful output regarding above criteria, we eventually chose to use the ``Apriori'' associator\cite{FastWeka,ClassWeka}, as it correctly handled boolean values and did not require the results to be classified.
 No special parameters are used to call the attributer, only the number of output results has been increased from 10 to 300\footnote{The code to call the attributer can be found at \url{https://github.com/hartenfels/Commit-Rater/blob/master/runweka\#L9}}.

### 2015-08-26 presentations/paper/details.tex
Fill in machine learning information in Details
Add missing } in Details

@@
 The source code for the Commit Rater can be found on GitHub\footnote{\url{https://github.com/hartenfels/Commit-Rater}}.
-The repository includes all of the boxplots (\texttt{analysis/boxplots}), their raw data source data (\texttt{samples}) and their generation script (\texttt{analysis/boxplots.rb).
+The repository includes all of the boxplots (\texttt{analysis/boxplots}), their raw data source data (\texttt{samples}) and their generation script (\texttt{analysis/boxplots.rb}).
 
-\TODO{It also includes the files used for the machine learning...}
+Weka's machine learning files (ARFF) can also be found in the (\texttt{samples}) folder, including a combined source file of all sample repos and the output of the Weka associator for it.
 

### 2015-08-26 presentations/paper/results.tex
Move boxplots into appendix
Fix overfull hbox by rewording Results

@@
 
-\TODO{Graphics placement}
-
 This subsection focuses solely on repository-level analysis of our metrics, since comparison between individual commits and or individual authors would be tedious.
 Also, author-level analysis is open to everyone through the web interface.
-
-\begin{figure}[p]
-    \centering
-    \includegraphics[width=0.8\textwidth]{img/subject_limit.pdf}
-    \caption{Subject Limit Boxplot}
-    \label{fig:bp_subject_limit}
-\end{figure}
 
@@
 
-\begin{figure}[p]
-    \centering
-    \includegraphics[width=0.8\textwidth]{img/imperative_subject.pdf}
-    \caption{Imperative Subject Boxplot}
-    \label{fig:bp_imperative_subject}
-\end{figure}
-
-\begin{figure}[p]
-    \centering
-    \includegraphics[width=0.8\textwidth]{img/no_short_message.pdf}
-    \caption{No Short Message Boxplot}
-    \label{fig:bp_no_short_message}
-\end{figure}
-
 On the other hand, figure \ref{fig:bp_imperative_subject} shows that authors of the Linux kernel use the imperative mood for the subject the most, while the authors of the 101worker rarely do.
@@
 
-\begin{figure}[p]
-    \centering
-    \includegraphics[width=0.8\textwidth]{img/body_used.pdf}
-    \caption{Body Used Boxplot}
-    \label{fig:bp_body_used}
-\end{figure}
-
-One significant difference between the two small repos (BadgeKit and 101worker) and the big repos (perl and Linux kernel) stands out in figure \ref{fig:bp_body_used}.
+One significant difference between the two small (BadgeKit and 101worker) and large repos (perl and Linux kernel) stands out in figure \ref{fig:bp_body_used}.
 The big repos both make heavy use of the body, while it is almost never used by the worker and only sometimes by the BadgeKit.
-
-\begin{figure}[p]
-    \centering
-    \includegraphics[width=0.8\textwidth]{img/no_period_subject.pdf}
-    \caption{No Period Subject Boxplot}
-    \label{fig:bp_no_period_subject}
-\end{figure}
 

### 2015-08-26 presentations/paper/abstract.tex

@@
 \begin{abstract}
-  In 2014, the Git surpassed Subversion as the top code management tool
-  \cite{EComSurv14}. With so many authors colaborating comes the need for a
-  appropriate and standardized use of elemental actions like doing commits.
-  Although the official Git documentation states very clear guidelines
-  \cite{OffGuide} on how to do a commit, a lot of users are not aware of them or
-  simply ignore them.
+  In 2014, Git surpassed Subversion as the top code management tool
+  \cite{EComSurv14}. With many authors collaborating comes the need for an
+  appropriate and standardized use of elemental actions, like formulating
+  commit messages. Although the official Git documentation states very clear
+  guidelines \cite{OffGuide} on how this should be done, many users are either
+  unaware or simply ignore them.
 
-  This paper presents a tool that analyzes a set of commits regarding criteria
-  composed of the official guidelines and some common mistakes, and shows a
-  prototypical website that encourages improvements in commit-etiquette by
-  creating a competitive score-board for a given GitHub repository. We also
-  perform a machine learning powered analysis of correlations between all
-  criteria.
+  This paper presents a tool that analyzes a set of commit messages regarding
+  criteria composed of the official guidelines and some common mistakes, and
+  shows a prototypical website that encourages improvements in commit message
+  style by creating a competitive score-board for a given GitHub repository. We
+  also perform a machine-learning-powered analysis of correlations between the
+  criteria, which can help improve the selection of criteria in the future.
 \end{abstract}

### 2015-08-26 presentations/paper/introduction.tex

@@
 
-While there has been research in the field of Mining Software Repositories about emotional content of commit messages (see section \ref{sec:related-work}), none of them have dealt with the actual quality of commits and their relation to the aformentioned best practices.
+While there has been research in the field of Mining Software Repositories about emotional content of commit messages (see section \ref{sec:related-work}), none of them have dealt with the actual quality of commits and their relation to the aforementioned best practices.
 In this paper, we present our approach to this topic.
 
-We have built an application called ``Commit Rater''\footnote{\url{https://github.com/hartenfels/Commit-Rater}}, which extracts commit message data of any Git repository (see section \ref{sec:data-extraction}) and synthesizes the quantitative adherance to commit criteria (see section \ref{sec:data-synthesis}).
+We have built an application called ``Commit Rater''\footnote{\url{https://github.com/hartenfels/Commit-Rater}}, which extracts commit message data of any Git repository (see section \ref{sec:data-extraction}) and synthesizes the quantitative adherence to commit criteria (see section \ref{sec:data-synthesis}).
 For the sake of easy use and graphical visualization of the ratings, we have also built a web application\footnote{\url{https://github.com/hartenfels/Commit-Rater-Web}} around the tool, which, at the time of writing, is available for public use at \url{http://trollarena.de:8080/}.

### 2015-08-26 presentations/paper/notes.tex

\section{Introduction}

Generally, this seminar (series) is about ``software languages'' (SL)
and hence it combines elements of software engineering, modelling,
programming languages, linguistics, formal specification, and
programming theory; see a recent discussion of some relevant fields
and terminology~\cite{FavreGLP10}.

Each particular edition of the SL seminar focuses on a specific topic
within the broader area of SL. (For instance, an edition may focus on
programming-language usage \cite{HageK08} or natural language aspects
in programming \cite{HostO08}.) The present notes provide some general
advice on the reporting and presentation obligations of the seminar's
participants. These notes are meant to be generic with regard to the
particular theme of a specific seminar edition.

That is, the purpose of these notes is to help student participants
writing their reports and preparing their presentations. These notes
complement the meetings and consultations.

\subsection*{Road-map}

In \S\ref{S:report}, advice on the report part of the seminar is
provided.

\noindent
In \S\ref{S:presentation}, advice on the presentation part
is provided.

\noindent
These notes are summarized in \S\ref{S:concl}.

\pagebreak

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Advice on the report}
\label{S:report}

Much has been written and said about scientific writing.  A report for
this seminar is a small exercise in scientific writing. Hence,
seminar participants are \emph{strongly encouraged} to gain basic
understanding of scientific writing. For instance, seminar
participants may consult a resource such as
\cite{Zobel09,Day98}. Unfortunately, the syllabus of Koblenz seminars
does not plan for education on scientific writing, neither does any
other obligatory course. Hence, seminar participants are bound to
consult a designated book or online resource, and to work closely
together with the prof to get a reasonable result.\footnote{Here is
  another resource on writing and giving talks:
  \url{http://research.microsoft.com/en-us/um/people/simonpj/papers/giving-a-talk/giving-a-talk.htm}.}
The following notes try to get seminar participants off the ground.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Organization of the report}

As far as reports for the seminar are concerned, we assume a rather
simple organization. A report would be spending about 10-25 pages in
Springer's LNCS style to describe the research work carried out.

Reports should use close 10 pages if there are not any substantial
illustrations. Reports can use up to 25 pages, but \textbf{a higher
  page count does not imply a better grade}---potentially it may
negatively affect the grade. However, illustrations are strongly
encouraged, if they truly illustrate the subject at hand. So seminar
participants are welcome to exhaust a 25 pages limit with useful
illustrations included.

A report would have a title and an abstract. The purpose of an
abstract is to properly summarize the report: use 50-200 words,
typically 100-150 words.

A report consists of an introduction, several technical sections,
possibly a related work section, and a conclusion section. See below
for more details.

\subsection{The importance of the introduction}

A report should start with an \emph{introduction section} which
motivates the subject of the report, possibly states one or more
\emph{research questions}, typically provides some background material
(if such material is not placed in a subsequent, designated section or
an appendix), lists \emph{contributions} of the report, and describes
the organization of the rest of the report. Judgement of all submitted
work may be biased by the introduction.

If there is any ingredient that is critical to an excellent completion
of the seminar, then this is the formulation of a \emph{research
  question}. By default (for such a short report/paper that is meant
here), the research question should be identified in the introduction
section. The challenge is here to formulate a question that performs
well in all of the following dimensions: a) concise and clear; b)
informed and nontrivial; c) operationally intelligent and verifiable;
d) meaningful to the rest of the text.

\subsection{The technical sections}

After the introduction, there can be any number of \emph{technical
  sections}.  These sections constitute the core (``technical meat'')
of the report. The style of these technical sections very much depends
on the subject and the chosen sources as well as the assumed style of
presentation.

As there are many different styles, and we do not want to discuss them
here at length. The best advice may be to leverage the corpus of
consulted research papers and to try approximating the style of one of
them. The prof wants to help on this matter---during the consultations
and otherwise.

\subsection{The concluding section}

After the technical sections, the report should be concluded by a
final section. Typically, such a section contains bits of summary,
discussion, interpretations, open problems or future work, and
vision. This may be a good place for the student to show that he or
she has outgrown the view of one or two specific papers and can
usefully operate in a broader research context. Again, an excellent
student would make a serious effort to connect several research papers
and research directions in a comprehensible, informative, and
cross-indexing manner.

\subsection{Literature references}

One important element of scholarly writing is to make appropriate use
of citations. For instance, in the introduction section, one needs to
provide \emph{contextual citations} so that the overall context of the
research effort at hand is clarified. One may also quickly mention
some more technical sources as a means to prepare for the more
detailed parts of the report. Throughout the paper, one uses
\emph{technical citations} for two major purposes: (i) to give credit
to any reused content; (ii) to substantiate claims. In the conclusion
of the report, one uses \emph{visionary citations} to connect to
subjects that were not but cut be covered, or that are worth being
mentioned otherwise.

Seminar participants must prove that they use advanced means of
locating prior work. The \href{http://portal.acm.org/}{ACM Digital
  Library} and the
\href{http://www.informatik.uni-trier.de/~ley/db/}{DBLP} service are
particularly suited to search for scientific publications on topics of
the SL seminar.

Every edition of the SL seminar is unique, but here are some general
pointers for research on software languages; again, every edition of
the SL seminar may draw from additional sources, as it should be
evident from the seminar edition's design. Thus:

\begin{itemize}
\item SLE---Software Language Engineering
\item ASE---Automated Software Engineering
\item ICPC---International Conference on Program Comprehension
\item POPL---Principles of Programming Languages
\item OOPSLA---OO Programming, Systems, Languages, and Applications
\item MODELS--- Model Driven Engineering Languages and Systems
\item WCRE---Working Conference on Reverse Engineering
\item ICSM---International Conference on Software Maintenance
\item MSR---Mining Software Repositories
\item PLDI---Programm Language Design and Implementation
\item PPDP---Principles and Practice of Declarative Programming
\item VL/HCC---Symposium on Visual Languages and Human-Centric Computing
\end{itemize}

There are also various journals on similar themes that may provide
seminal and archival content for the seminar work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\subsection{Abstraction is king, not page count}

There is no use in reproducing or condensing one specific paper (or a
series of strongly connected papers). Any reasonable seminar report
must exercise abstraction; it must study a subject from an individual
point of view with an original research question in mind. A reasonable
seminar report involves (3+) different pieces of scholarly work and
integrates them in the presentation.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Advice on the presentation}
\label{S:presentation}

This section provides another example of what should be called a
technical section. Again, in such sections, the author works out the
technical details (say, meat) of all research work. There can be any
number of such sections. One should think hard about organization
principles to make up the appropriate number of sections and
subsections.

This section briefly talks about the presentation part of the seminar.
Just as in the case of scientific writing, there exists online or
published advice on ``how to give a good talk'', perhaps even in
seminar-like circumstances \cite{Talk,Klaeren94}. Giving good talks is
extremely difficult, but also very rewarding. Speakers should sure to
do some amount of reflection before they go into your talk. Some rules
of thumb follow:

\begin{itemize}

\item Finalizing the slides the night before is perhaps Ok, but one
  should start thinking of the talk way ahead of time. Otherwise, the
  presentation may likely to be boring or stressful and sends the
  audience to sleep. Speakers should not waste the precious cycles of
  the audience! As an aside, the available time should be perfectly
  leveraged by the talk: not more, not less.

\item One should not confuse writing with talking. One should not
  think of the talk as a way to present the paper in a condensed
  style. Instead, one should design the talk in a way that its
  structure and style maintains the attention of the audience and
  keeps up with the audience's abilities. One should use the talk to
  get people interested in the subject. One should motivate the
  audience to read more about the subject in the report that is
  advertised by the presentation.

\item One should not waste time on outlines; they are often totally
  useless at the time they are shown. One should focus on motivation
  from the first slide on. One should make good use of illustrations
  and simplify matters. One should not try to tell every detail, but
  to select some interesting details and make clear what else could
  be discussed or is included into the paper.

\item Seminar talks should be interactive. Hence, clarifying
  questions should be admitted.

\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Concluding remarks}
\label{S:concl}

These notes are supposed to be useful as is, but further efforts may
be needed to convey all witness and intentions. For the time being,
the author asks the seminar participants and other readers to work
with what is available and the quoted resources. Everyone is welcome
to suggest revisions for these notes.

### 2015-08-26 presentations/paper/research_question.tex

@@
 
-Our research and development regarding the Commit Rater was lead by the goal of providing useful data to developers, such as ourselves, regarding their commits to help them learn and improve.
+Our research and development regarding the Commit Rater was lead by the goal of providing useful data to developers, such as ourselves, regarding their commits, to help them learn and improve.
 The following two research questions (RQs) emerged from this objective.

### 2015-09-22 presentations/paper/introduction.tex
Add examples of good and bad commit messages

@@
 
+For example, commit messages like ``fixed a bug'' or even just ``bugfix'' serve no practical purpose, since they convey no useful information.
+Additionally, messages like ``The fnuction x is noww an class y'' and ``makes function x write the output to stdout and changes the format of the output of function x.'' are unpleasant to read in the Git log, because of the changing format, the typos or their verbosity.
+On the other hand, a message like ``Write output to stdout'' is succinct and tells the reader what it does.
+Coupled with similarly formatted commit messages, using tools like the Git log is a lot more pleasant.
+
 While there has been research in the field of Mining Software Repositories about emotional content of commit messages (see section \ref{sec:related-work}), none of them have dealt with the actual quality of commits and their relation to the aforementioned best practices.

### 2015-09-22 presentations/paper/methodology.tex
Fix another one of Marco's refs in Methodology
State that the sample repos were chosen arbitrarily

@@
 
-Several repositories were chosen as sample sources, for the sake of having enough data to analyze in section\ref{sec:data-analysis}.
+Several repositories were chosen arbitrarily as sample sources, for the sake of having enough data to analyze in section\ref{sec:data-analysis}.
 Additionally, the authors of these repositories have different levels of being aware of and adhering to Git's commit message guidelines\cite{OffGuide}, which leads to a large spread of ratings across them.
@@
 The subject line should be limited to less than 10 words.
-This is an extension of the subject\_limit criterion in \ref{subject_limit}, which might rarely allow 10 or more words.
+This is an extension of the subject\_limit criterion in \ref{subs:subject_limit}, which might rarely allow 10 or more words.
 The reasoning behind this criterion is again, that many words hint at more than one logical change set in one commit.

### 2015-09-22 presentations/paper/methodology.tex
Make analysis-possibilities a little clearer

@@
 
-On each level, it is furthermore possible to analyse either the results of all criteria checks or only the check/checks for one criterion. These six possibilities will be discussed below.
+These three possibilities will be discussed below.
+Additionally, on each level it is possible to analyse either the results of all criteria checks or only the check/checks for one criterion.
+This distinction will be made where applicable.
 
@@
 \subsubsection{Above repository-level}
-It may be of further interest to look at the averages of adherence to guidelines across multiple repos and thereby extrapolate some general statistics about usage of the guidelines in the Git community.
+Additionally to the analysis-possibilities stated above, it may be of further interest to look at the averages of adherence to guidelines across multiple repos and thereby extrapolate some general statistics about usage of the guidelines in the Git community.
 But we did not concern ourselves with this level, since we found it to be unrelated to our research questions.

### 2015-09-25 presentations/paper/methodology.tex
fix bug

@@
 Instead, the choice was made to simply clone the repositories and use \texttt{git log} to extract commit messages from them.
-While it requires time to clone the repository and disk space to store its data, it is much less limited and can be used for any Git repository, even outside of GitHub.
+While it requires time to clone the repository and disk space to store its data, it is much less limited and is usable for any Git repository, even outside of GitHub.
 
@@
 
-Since the entirety of repository commit messages can be listed by a single call to \texttt{git log} and commits can be extracted by a single regular expression, the commit rating process is fast and scales well.
+Since the entirety of repository commit messages is listed by a single call to \texttt{git log} and commits are extracted by a single regular expression, the commit rating process is fast and scales well.
 Repeated analysis of the same repository is also optimized by caching the cloned data on disk and only pulling recent changes on subsequent runs.
@@
 
-The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author. These triples will be used as a metric for the analysis in \ref{sec:data-analysis}.
+The results of our tests are counted in a triple $(pass, fail, undef)$ for each criterion per author.
+These triples will be used as a metric for the analysis in \ref{sec:data-analysis}.
+Using these criteria, we rate every commit with a tuple of these triples, where a tuple of just $pass$es represents an ideal commit.
+A tuple of only $fail$s and/or $undef$s on the other hand represents the worst commit possible.
 
@@
 \cite{CB} summarizes the most important guidelines very nicely, and the first seven criteria below are directly taken or inspired from the blog post.
-Note that the seventh mentioned rule could not be made into a criterion, since it would require actual understanding of the commit message.
+Note that the seventh mentioned rule is not a criterion, since it would require actual understanding of the commit message.
 Omitting this rule, we still inferred one additional criterion (\ref{subs:body_used}) that we found missing in the list.
@@
 The first letter of the subject line should be capitalized.
-Although it could be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the English language start with a capital letter.
+Although it may be argued that this is more of a convention, subject lines should be complete sentences, and sentences in the English language start with a capital letter.
 This rule is only mentioned by \cite{CB}.
@@
 In addition to the subject line, there should be a body that further explains what the commit does and why it does what it does\cite{OffGuide}.
-The body consists of multiple lines and multiple paragraphs can be used, separated by blank lines.
+The body consists of multiple lines and multiple paragraphs, separated by blank lines.
 It is also acceptable to use bullet points.
@@
 \label{subs:no_short_message}
-The subject line should consist of more than 2 words, since no useful information can be conveyed with less words, for example messages like ``Bug'', ``Fix'' and ``Add comment'' are useless.
+The subject line should consist of more than 2 words, since no useful information is conveyed with less words, for example messages like ``Bug'', ``Fix'' and ``Add comment'' are useless.
 Of course, there are situations where two words are appropriate, but we estimate that these are rare enough to be insignificant.
@@
 This will of course sometimes hide real errors.
-Maybe further research could provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.
+Maybe further research will provide an adequate solution to this problem or at least analyse the precision of applying a standard spell checker to very domain specific texts.
 
@@
 Under the assumption that our synthesis results are metrics for the ``goodness'' of commits, we need to analyse them in order to aggregate a measure of ``goodness''.
-This analysis can be performed on three levels:
+This analysis is possible on three levels:
 
 \begin{itemize}
-  \item Per commit-level: Analysis could be done on the results of checking an individual commit against our criteria.
+  \item Per commit-level: Analysis is done on the results of checking an individual commit against our criteria.
   \item Per author-level: This level would aggregate the metrics for all commits of an author in a repository and create a rating of the authors commit behaviour.
@@
 \label{subs:Author-level}
-Analysis on this level evaluates the metrics-triples that were described in \ref{sec:data-synthesis}, where each author has a triple $(pass, fail, undef)$ for each criterion with $pass$ the number of commits that \emph{pass} the test for the criterion, $fail$ the number of commits that \emph{fail} the test for the criterion and $undef$ the number of commits that could not be tested against the criterion.
+Analysis on this level evaluates the metrics-triples that were described in \ref{sec:data-synthesis}, where each author has a triple $(pass, fail, undef)$ for each criterion with $pass$ the number of commits that \emph{pass} the test for the criterion, $fail$ the number of commits that \emph{fail} the test for the criterion and $undef$ the number of commits where testing for the criterion is impossible, for example because it depends on a $fail$ed criterion.
 
@@
 
-An example: A author with the triple $(190, 10, 0)$ for the subject limit (\ref{subs:subject_limit}) successfully limits his subject lines to 50 characters in 95\% of his commits.
-It could therefore furthermore be concluded that he is aware of the guideline, but has no tool in place that would prevent accidentally writing more than 50 characters.
+An example: An author with the triple $(190, 10, 0)$ for the subject limit (\ref{subs:subject_limit}) successfully limits their subject lines to 50 characters in 95\% of their commits.
+Therefore, we conclude that they are probably aware of the guideline, but have no tool in place that would prevent accidentally entering more than 50 characters.
 
-An average of these rates over all criteria can be seen as a general rating of an author's commit behaviour.
-Because of the $undef$s, two averages have to be considered: The standard average, which is just the average over the rates described above.
-And an average over the rates where each rate is weighted according to how many of all commits constituted to the rate.
-An author with a triple $(5, 5, 90)$ has a rate of 50\% according to equation \ref{eq:rate}, but should factor less into the average since only 10\% of all commits could be evaluated.
+An average of these rates over all criteria is a general rating of an author's commit behaviour.
+Because of the $undef$s, two averages have to be considered: The standard average, which is just the average over the rates described above, and an average over the rates where each rate is weighted according to how many of all commits constituted to the rate.
+An author with a triple $(5, 5, 90)$ has a rate of 50\% according to equation \ref{eq:rate}, but should factor less into the average since only 10\% of all commits were evaluated.
 Thus, the weighted average is calculated as follows:
@@
 It would have been easy to just aggregate the triples of all authors in a repo and apply equation \ref{eq:weightedAverage} to receive an average for the whole repository.
-But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends could be inferred from the results.
+But we decided that this would serve no practical purpose, since the distribution over the behaviour of many authors across all criteria would likely have a very high variance and only very general trends are inferrable from the results.
 

### 2015-09-25 presentations/paper/results.tex
fix bug

@@
 On the other hand, it can be argued that meeting the seven official criteria means having good commits \emph{per definition}, since they have been taken from the official guidelines, and are therefore themselves the missing objective judgement.
+Additionally, our criteria is certainly incomplete and could be expanded arbitrarily large.
 
@@
 As an attempt to validate our own criteria, we performed association analysis using the data mining and machine learning software Weka\cite{Weka}.
+Using the correlations gained between official criteria and our own would help us prove or disprove the validity of each criterion.
+Furthermore, with a way to validate new criteria, we would be able to expand our Commit Rater's criteria pool.
+
 The data set is a commit-level view (see section \ref{subs:Commit-level}) of all rated commits of our sample repositories (see section \ref{sec:data-extraction}).
@@
 Additionally, this machine learning process is not useful for all criteria, as not all of them have a relation to at least one other criterion.
-Therefore, either more criteria is needed to fill these gaps, or a different way of validation needs to be used.
+Therefore, either more criteria is needed to fill these gaps, or a different way of validation needs to be used, such as an expert analysis or a comparison with another commit rating system that might appear in the future.
 

### 2015-09-25 presentations/paper/results.tex
Link to boxplots in Results

@@
 
-The boxplots for the other criteria are available in our Git and were not included here in order to save space.
+The boxplots for the other criteria are available in our Git\footnote{\url{https://github.com/hartenfels/Commit-Rater/tree/master/analysis/boxplots}} and were not included here in order to save space.
 

### 2015-09-25 presentations/paper/methodology.tex
bug.

@@
 \begin{description}
-    \item[101worker]\footnote{\url{https://github.com/101companies/101worker}}: A relatively small repository of barely over $2000$ commits, done by the Software Languages Team of the University of Koblenz-Landau.
+    \item[101worker\footnote{\url{https://github.com/101companies/101worker}}]: A relatively small repository of barely over $2000$ commits, done by the Software Languages Team of the University of Koblenz-Landau.
 Most of the commits in this repository do not adhere to the commit guidelines.
-    \item[mozilla/openbadges-badgekit]\footnote{\url{https://github.com/mozilla/openbadges-badgekit}}: The smallest repository in our selection, it was chosen because it is a Mozilla project and we therefore expect that most commits adhere at least partially to the commit guidelines.
-    \item[perl]\footnote{\url{https://github.com/Perl/perl5}}: The interpreter for Perl 5, a large repository of over $60000$ commits, partially adhering the commit guidelines.
-    \item[Linux Kernel]\footnote{\url{https://github.com/torvalds/linux}}: A massive repository of over half a million commits.
+    \item[mozilla/openbadges-badgekit\footnote{\url{https://github.com/mozilla/openbadges-badgekit}}]: The smallest repository in our selection, it was chosen because it is a Mozilla project and we therefore expect that most commits adhere at least partially to the commit guidelines.
+    \item[perl\footnote{\url{https://github.com/Perl/perl5}}]: The interpreter for Perl 5, a large repository of over $60000$ commits, partially adhering the commit guidelines.
+    \item[Linux Kernel\footnote{\url{https://github.com/torvalds/linux}}]: A massive repository of over half a million commits.
 Used for stress-testing our implementation and finding reasonable constraints on the amount of commits analyzed.
